### 2018-11-13 13191.tex
New Article!

\section{Introduction}
\label{intro} 
Nunc a aliquet sem, eget aliquet purus. Vestibulum ac placerat mauris. Proin sed dolor ac justo semper iaculis. Donec varius, nibh sit amet finibus tristique, sapien ante interdum odio, et pretium sapien libero nec massa. In hac habitasse platea dictumst. Donec vel augue ac sapien imperdiet pretium. Maecenas gravida risus id ultricies dignissim. Maecenas Eq.~\ref{eqn:drag} gravida felis quis dolor faucibus, sed maximus lorem tristique
\begin{equation}
\label{eqn:drag}
	\int_a^bu\frac{d^2v}{dx^2}\,dx
	=\left.u\frac{dv}{dx}\right|_a^b
	-\int_a^b\frac{du}{dx}\frac{dv}{dx}\,dx.
\end{equation}

### 2018-11-13 b275.tex
New Article!

\section {Section}
Mauris nec massa leo. Mauris ac diam auctor nisl imperdiet porta. Sed sit amet neque eget nisi dictum placerat. Duis sit amet pellentesque odio. Cras scelerisque sem a consectetur vehicula. Aliquam interdum luctus fringilla. Nunc sollicitudin, lorem in semper viverra, \citet{Goldreich_1990}, dui nisi sodales sem, ut condimentum erat leo eget arcu \citep{Goldreich_1990,Kumar_1994}. Donec pharetra aliquam metus, non pulvinar tellus interdum a. Mauris a ante pharetra, mollis enim in, eleifend erat. Pellentesque suscipit risus massa, non vestibulum libero euismod feugiat. In hac habitasse platea dictumst. Maecenas rutrum lobortis lobortis. Vestibulum convallis porttitor sem ac ultricies. Mauris volutpat fringilla nisl blandit semper. Proin nec iaculis sem. Aenean neque ipsum, pretium a faucibus non, tincidunt ut sapien.

### 2018-11-13 baf.tex
New Article!

\section{Section}
\label{igw}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Cras egestas auctor molestie. In hac habitasse platea dictumst. Duis turpis tellus, scelerisque sit amet lectus ut, ultricies cursus enim. Integer fringilla a elit at fringilla. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nulla congue consequat consectetur. Duis ac mi ultricies, mollis ipsum nec, porta est. Aenean augue neque, varius vitae dapibus ac, Fig.~\ref{125409} dictum ut nisl et Table \ref{tab:table}

### 2019-03-18 examples/osubenchmarks/colonialone/run-osu.sh
Add input files and script for OSU benchmarks

@@ -1,0 +1,37 @@
+#!/bin/sh
+
+#SBATCH --job-name="osu"
+#SBATCH --output=log%j.out
+#SBATCH --error=log%j.err
+#SBATCH --partition=ivygpu
+#SBATCH --nodes=2
+#SBATCH --ntasks-per-node=1
+#SBATCH --time=01:00:00
+
+module load gcc/4.9.2
+module load cuda/toolkit/8.0
+module load openmpi/1.8/gcc/4.9.2
+
+bindir="/groups/barbalab/software/osu-micro-benchmarks/5.6/mpi/pt2pt"
+export PATH=$bindir:$PATH
+
+export CUDA_VISIBLE_DEVICES=0,1
+
+# number of runs
+nruns=5
+
+outdir="output"
+mkdir -p $outdir
+cd $outdir
+
+for (( i=0; i<$nruns; i++ ))
+do
+	echo "run $i"
+			  BENCHMARK="5.3.2/mpi/pt2pt/osu_bw"
+	time mpiexec -display-map -mca btl openib,self \
+		osu_bw -d cuda -x 100 -i 1000 H H \
+		> stdout_bandwidth_run$i.txt 2> stderr_bandwidth_run$i.txt
+	time mpiexec -display-map -mca btl openib,self \
+		osu_latency -d cuda -x 100 -i 1000 H H \
+		> stdout_latency_run$i.txt 2> stderr_latency_run$i.txt
+done

### 2019-03-18 examples/snake2d2k35/run-petibm.sh
Add input files and scripts for 2D snake run

@@ -1,0 +1,44 @@
+#!/usr/bin/env bash
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+simudir=$scriptdir
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=12
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+# get number of GPUs on machine
+ngpusmax=`nvidia-smi -L | wc -l`
+echo "Number of GPU devices available on each node: $ngpusmax"
+# number of GPUs to use per node
+CUDA_VISIBLE_DEVICES=0,1
+IFS=',' read -ra GPUS <<< "$CUDA_VISIBLE_DEVICES"
+ngpus=${#GPUS[@]}
+echo "Number of GPU devices per node to use: $ngpus ($CUDA_VISIBLE_DEVICES)"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+cp $AZ_BATCH_TASK_DIR/stdout.txt $simudir
+cp $AZ_BATCH_TASK_DIR/stderr.txt $simudir
+
+mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+  -genv CUDA_VISIBLE_DEVICES=$CUDA_VISIBLE_DEVICES \
+  petibm-decoupledibpm \
+  -directory $simudir \
+  -log_view ascii:$simudir/view.log \
+  -malloc_log \
+  -memory_view \
+  -options_left >> $simudir/stdout.txt 2> $simudir/stderr.txt
+
+exit 0

### 2019-03-18 examples/snake2d2k35/scripts/create_body.py

@@ -1,0 +1,26 @@
+"""Generate the coordinates of the snake boundary."""
+
+import sys
+import pathlib
+import numpy
+from matplotlib import pyplot
+
+import petibmpy
+
+# Read the original coordinates of the section.
+rootdir = pathlib.Path(__file__).absolute().parents[1]
+datadir = rootdir / 'data'
+filepath = datadir / 'snake2d.body'
+with open(filepath, 'r') as infile:
+    x, y = numpy.loadtxt(infile, dtype=numpy.float64, skiprows=1, unpack=True)
+
+# Apply rotation and regularize the geometry to desired resolution.
+x, y = petibmpy.rotate2d(x, y, center=(0.0, 0.0), angle=-35.0)
+x, y = petibmpy.regularize2d(x, y, ds=0.004)
+
+# Write new coordinates in file located in simulation directory.
+filepath = rootdir / 'snake2d35.body'
+with open(filepath, 'w') as outfile:
+    outfile.write(f'{x.size}\n')
+with open(filepath, 'ab') as outfile:
+    numpy.savetxt(outfile, numpy.c_[x, y])

### 2019-03-18 examples/snake2d2k35/scripts/create_mesh_yaml.py

@@ -1,0 +1,47 @@
+"""Generate the YAML node "mesh" with details of the Cartesian grid."""
+
+import sys
+import pathlib
+import numpy
+from matplotlib import pyplot
+
+import petibmpy
+
+
+# Info about the 2D structured Cartesian grid.
+width = 0.004  # minimum grid spacing in the x- and y- directions
+ratio = 1.01  # stretching ratio
+info = [{'direction': 'x', 'start': -15.0,
+         'subDomains': [{'end': -0.52,
+                         'width': width,
+                         'stretchRatio': ratio,
+                         'reverse': True,
+                         'precision': 2},
+                        {'end': 3.48,
+                         'width': width,
+                         'stretchRatio': 1.0},
+                        {'end': 15.0,
+                         'width': width,
+                         'stretchRatio': ratio,
+                         'precision': 2}]},
+        {'direction': 'y', 'start': -15.0,
+         'subDomains': [{'end': -2.0,
+                         'width': width,
+                         'stretchRatio': ratio,
+                         'reverse': True,
+                         'precision': 2},
+                        {'end': 2.0,
+                         'width': width,
+                         'stretchRatio': 1.0},
+                        {'end': 15.0,
+                         'width': width,
+                         'stretchRatio': ratio,
+                         'precision': 2}]}]
+
+mesh = petibmpy.CartesianStructuredMesh()
+mesh.create(info)
+mesh.print_parameters()
+
+simudir = pathlib.Path(__file__).absolute().parents[1]
+filepath = simudir / 'mesh.yaml'
+mesh.write_yaml_file(filepath)

### 2019-03-18 examples/snake2d2k35/scripts/get_vorticity2d.py

@@ -1,0 +1,47 @@
+"""Save the vorticity field as a 2D array in HDF5 files.
+
+Create a XDMF file to visualize the 2D field with VisIt.
+"""
+
+import sys
+import pathlib
+import numpy
+import yaml
+
+import petibmpy
+
+
+name = 'wz'  # name of the field variable
+
+# Get directories.
+simudir = pathlib.Path(__file__).absolute().parents[1]
+datadir = simudir / 'output' / 'solution'
+outdir = simudir / 'output' / 'postprocessing' / name
+outdir.mkdir(parents=True, exist_ok=True)
+
+# Read 3D grid and write 2D grid.
+gridpath = simudir / 'output' / 'grid.h5'
+x, y = petibmpy.read_grid_hdf5(gridpath, name)
+gridpath = outdir / 'grid.h5'
+petibmpy.write_grid_hdf5(gridpath, name, x, y)
+
+# Get temporal parameters.
+filepath = simudir / 'config.yaml'
+with open(filepath, 'r') as infile:
+    config = yaml.load(infile)['parameters']
+nstart, nt, nsave = config['startStep'], config['nt'], config['nsave']
+dt = config['dt']
+timesteps = list(range(nstart, nstart + nt + 1, nsave))
+
+# Average the scalar field along the z-direction and write field.
+for timestep in timesteps:
+    print('[time step {}]'.format(timestep))
+    filepath = datadir / '{:0>7}.h5'.format(timestep)
+    data = petibmpy.read_field_hdf5(filepath, name)
+    filepath = outdir / '{:0>7}.h5'.format(timestep)
+    petibmpy.write_field_hdf5(filepath, name, data)
+
+# Write XDMF file to visualize field with VisIt.
+filepath = outdir / (name + '.xmf')
+petibmpy.write_xdmf(filepath, outdir, gridpath, name,
+                    nstart, nt, nsave, dt)

### 2019-03-18 examples/snake2d2k35/scripts/plot_force_coefficients.py

@@ -1,0 +1,34 @@
+"""Generate a figure of the drag and lift force coefficients over time.
+
+Save the figure in the sub-folder `figures` of the simulation directory.
+"""
+
+import sys
+import pathlib
+from matplotlib import pyplot
+
+import petibmpy
+
+
+simudir = pathlib.Path(__file__).absolute().parents[1]
+
+filepath = simudir / 'output' / 'forces-0.txt'
+t, fx, fy = petibmpy.read_forces(filepath)
+cd, cl = petibmpy.get_force_coefficients(fx, fy, coeff=2.0)
+
+pyplot.rc('font', family='serif', size=16)
+fig, ax = pyplot.subplots(figsize=(8.0, 4.0))
+ax.set_xlabel('Non-dimensional time')
+ax.set_ylabel('Force coefficients')
+ax.grid()
+ax.plot(t, cd, label='$C_D$')
+ax.plot(t, cl, label='$C_L$')
+ax.legend(ncol=2)
+ax.set_xlim(t[0], t[-1])
+ax.set_ylim(0.0, 3.0)
+fig.tight_layout()
+
+figdir = simudir / 'figures'
+figdir.mkdir(parents=True, exist_ok=True)
+filepath = figdir / 'forceCoefficients.png'
+fig.savefig(str(filepath), dpi=300)

### 2019-03-18 examples/snake2d2k35/scripts/plot_wz_wake2d.py

@@ -1,0 +1,28 @@
+"""Generate figures of the 2D pseudocolor of the 2D vorticity field."""
+
+import os
+import sys
+import pathlib
+
+root_dir = pathlib.Path(__file__).absolute().parents[3]
+scripts_dir = root_dir / 'misc'
+if root_dir not in sys.path:
+    sys.path.insert(0, str(scripts_dir))
+from visitplot import *
+
+
+simudir = pathlib.Path(__file__).absolute().parents[1]
+xdmfpath = simudir / 'output' / 'postprocessing' / 'wz' / 'wz.xmf'
+name = 'wz'
+config_view = simudir / 'scripts' / 'visit_view2d.yaml'
+curve2dpath = simudir / 'output' / 'snake2d35.curve'
+figdir = simudir / 'figures'
+prefix = 'wz_wake2d_'
+
+visit_plot_pseudocolor_2d(xdmfpath, name,
+                          value_range=(-5.0, 5.0),
+                          curve2d_paths=[curve2dpath],
+                          config_view=config_view,
+                          out_dir=figdir, out_prefix=prefix,
+                          figsize=(1024, 1024),
+                          visit_dir=os.environ.get('VISIT_DIR'))

### 2019-03-18 examples/snake3d2k35/run-petibm.sh
Add input files and scripts for 3D snake run

@@ -1,0 +1,44 @@
+#!/usr/bin/env bash
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+simudir=$scriptdir
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=24
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+# get number of GPUs on machine
+ngpusmax=`nvidia-smi -L | wc -l`
+echo "Number of GPU devices available on each node: $ngpusmax"
+# number of GPUs to use per node
+CUDA_VISIBLE_DEVICES=0,1,2,3
+IFS=',' read -ra GPUS <<< "$CUDA_VISIBLE_DEVICES"
+ngpus=${#GPUS[@]}
+echo "Number of GPU devices per node to use: $ngpus ($CUDA_VISIBLE_DEVICES)"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+cp $AZ_BATCH_TASK_DIR/stdout.txt $simudir
+cp $AZ_BATCH_TASK_DIR/stderr.txt $simudir
+
+mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+  -genv CUDA_VISIBLE_DEVICES=$CUDA_VISIBLE_DEVICES \
+  petibm-decoupledibpm \
+  -directory $simudir \
+  -log_view ascii:$simudir/view.log \
+  -malloc_log \
+  -memory_view \
+  -options_left >> $simudir/stdout.txt 2> $simudir/stderr.txt
+
+exit 0

### 2019-03-18 examples/snake3d2k35/scripts/average_wz.py

@@ -1,0 +1,46 @@
+"""Average the spanwise vorticity field along the spanwise direction.
+
+Write the 2D field values into HDF5 file.
+"""
+
+import pathlib
+import numpy
+import yaml
+
+import petibmpy
+
+name = 'wz'  # name of the field variable
+
+# Get directories.
+simudir = pathlib.Path(__file__).absolute().parents[1]
+datadir = simudir / 'output' / 'solution'
+outdir = simudir / 'output' / 'postprocessing' / (name + '_avg')
+outdir.mkdir(parents=True, exist_ok=True)
+
+# Read 3D grid and write 2D grid.
+gridpath = simudir / 'output' / 'grid.h5'
+x, y, _ = petibmpy.petibm_read_grid_hdf5(gridpath, name)
+gridpath = outdir / 'grid.h5'
+petibmpy.write_grid_hdf5(gridpath, name + '-avg', x, y)
+
+# Get temporal parameters.
+filepath = simudir / 'config.yaml'
+with open(filepath, 'r') as infile:
+    config = yaml.load(infile)['parameters']
+nstart, nt, nsave = config['startStep'], config['nt'], config['nsave']
+dt = config['dt']
+timesteps = list(range(nstart, nstart + nt + 1, nsave))
+
+# Average the scalar field along the z-direction and write field.
+for timestep in timesteps:
+    print('[time step {}]'.format(timestep))
+    filepath = datadir / '{:0>7}.h5'.format(timestep)
+    data = petibmpy.read_field_hdf5(filepath, name)
+    data_avg = numpy.mean(data, axis=0)
+    filepath = outdir / '{:0>7}.h5'.format(timestep)
+    petibmpy.write_field_hdf5(filepath, name + '-avg', data_avg)
+
+# Write XDMF file to visualize field with VisIt.
+filepath = outdir / (name + '-avg.xmf')
+petibmpy.write_xdmf(filepath, outdir, gridpath, name + '-avg',
+                    nstart, nt, nsave, dt)

### 2019-03-18 examples/snake3d2k35/scripts/create_body.py

@@ -1,0 +1,27 @@
+"""Generate the coordinates of the snake boundary."""
+
+import pathlib
+import numpy
+
+import petibmpy
+
+
+simudir = pathlib.Path(__file__).absolute().parents[1]
+
+# Read the original coordinates of the section.
+filepath = simudir / 'data/snake2d.body'
+with open(filepath, 'r') as infile:
+    x, y = numpy.loadtxt(infile, skiprows=1, unpack=True)
+
+# Apply rotation and regularize the geometry to desired resolution.
+x, y = petibmpy.rotate2d(x, y, center=(0.0, 0.0), angle=-35.0)
+x, y = petibmpy.regularize2d(x, y, ds=0.008)
+# Extrude the section along the z direction.
+x, y, z = petibmpy.extrude2d(x, y, ds=0.08, limits=(0.0, 3.2))
+
+# Write new coordinates in file located in simulation directory.
+filepath = simudir / 'snake3d35.body'
+with open(filepath, 'w') as outfile:
+    outfile.write(f'{x.size}\n')
+with open(filepath, 'ab') as outfile:
+    numpy.savetxt(outfile, numpy.c_[x, y, z])

### 2019-03-18 examples/snake3d2k35/scripts/create_mesh_yaml.py

@@ -1,0 +1,54 @@
+"""Generate the YAML node "mesh" with details of the Cartesian grid."""
+
+import pathlib
+import math
+
+import petibmpy
+
+
+# Info about the 3D structured Cartesian grid.
+width = 0.008  # minimum grid spacing in the x- and y- directions
+chord = 1.0  # chord-length of the body cross-section
+spanwise_width = 10.0 * width  # grid-spacing in the spanwise direction
+spanwise_length = 3.2 * chord  # target spanwise length
+spanwise_cells = math.ceil(spanwise_length / spanwise_width)  # cells required
+spanwise_length = spanwise_cells * spanwise_width  # actual spanwise length
+ratio = 1.01  # stretching ratio
+info = [{'direction': 'x', 'start': -15.0,
+         'subDomains': [{'end': -0.52,
+                         'width': width,
+                         'stretchRatio': ratio,
+                         'reverse': True,
+                         'precision': 2},
+                        {'end': 3.48,
+                         'width': width,
+                         'stretchRatio': 1.0},
+                        {'end': 15.0,
+                         'width': width,
+                         'stretchRatio': ratio,
+                         'precision': 2}]},
+        {'direction': 'y', 'start': -15.0,
+         'subDomains': [{'end': -2.0,
+                         'width': width,
+                         'stretchRatio': ratio,
+                         'reverse': True,
+                         'precision': 2},
+                        {'end': 2.0,
+                         'width': width,
+                         'stretchRatio': 1.0},
+                        {'end': 15.0,
+                         'width': width,
+                         'stretchRatio': ratio,
+                         'precision': 2}]},
+        {'direction': 'z', 'start': 0.0,
+         'subDomains': [{'end': spanwise_length,
+                         'width': spanwise_width,
+                         'stretchRatio': 1.0}]}]
+
+mesh = petibmpy.CartesianStructuredMesh()
+mesh.create(info)
+mesh.print_parameters()
+
+simudir = pathlib.Path(__file__).absolute().parents[1]
+filepath = simudir / 'mesh.yaml'
+mesh.write_yaml_file(filepath)

### 2019-03-18 examples/snake3d2k35/scripts/plot_force_coefficients.py

@@ -1,0 +1,39 @@
+"""Generate a figure of the force coefficients over time.
+
+Save the figure in the sub-folder `figures` of the simulation directory.
+"""
+
+import pathlib
+from matplotlib import pyplot
+
+import petibmpy
+
+
+simudir = pathlib.Path(__file__).absolute().parents[1]
+
+filepath = simudir / 'output' / 'forces-0.txt'
+t, fx, fy, fz = petibmpy.read_forces(filepath)
+rho, u_inf = 1.0, 1.0  # density and freestream speed
+dyn_pressure = 0.5 * rho * u_inf**2  # dynamic pressure
+c = 1.0  # chord length
+Lz = 3.2 * c  # spanwise length
+coeff = 1 / (dyn_pressure * c * Lz)  # scaling factor for force coefficients
+cd, cl, cz = petibmpy.get_force_coefficients(fx, fy, fz, coeff=coeff)
+
+pyplot.rc('font', family='serif', size=16)
+fig, ax = pyplot.subplots(figsize=(8.0, 4.0))
+ax.set_xlabel('Non-dimensional time')
+ax.set_ylabel('Force coefficients')
+ax.grid()
+ax.plot(t, cd, label='$C_D$')
+ax.plot(t, cl, label='$C_L$')
+ax.plot(t, cz, label='$C_z$')
+ax.legend()
+ax.set_xlim(t[0], t[-1])
+ax.set_ylim(-0.1, 3.0)
+fig.tight_layout()
+
+figdir = simudir / 'figures'
+figdir.mkdir(parents=True, exist_ok=True)
+filepath = figdir / 'forceCoefficients.png'
+fig.savefig(str(filepath), dpi=300)

### 2019-03-18 examples/snake3d2k35/scripts/plot_force_coefficients_compare_2d.py

@@ -1,0 +1,52 @@
+"""Generate a figure of the force coefficients over time.
+
+Compare the 3D force coefficients with the 2D ones.
+Save the figure in the sub-folder `figures` of the simulation directory.
+"""
+
+import pathlib
+from matplotlib import pyplot
+
+import petibmpy
+
+
+simudir = pathlib.Path(__file__).absolute().parents[1]
+
+# Read 3D forces and convert to force coefficients.
+filepath = simudir / 'output' / 'forces-0.txt'
+t, fx, fy, fz = petibmpy.read_forces(filepath)
+rho, u_inf = 1.0, 1.0  # density and freestream speed
+dyn_pressure = 0.5 * rho * u_inf**2  # dynamic pressure
+c = 1.0  # chord length
+Lz = 3.2 * c  # spanwise length
+coeff = 1 / (dyn_pressure * c * Lz)  # scaling factor for force coefficients
+cd, cl, cz = petibmpy.get_force_coefficients(fx, fy, fz, coeff=coeff)
+
+# Read 2D forces and convert to force coefficients.
+rootdir = simudir.parent
+simudir2d = rootdir / 'snake2d2k35'
+filepath = simudir2d / 'output' / 'forces-0.txt'
+t2, fx2, fy2 = petibmpy.read_forces(filepath)
+coeff = 1 / (dyn_pressure * c)
+cd2, cl2 = petibmpy.get_force_coefficients(fx2, fy2, coeff=coeff)
+
+# Plot force coefficients over time.
+pyplot.rc('font', family='serif', size=16)
+fig, ax = pyplot.subplots(figsize=(8.0, 4.0))
+ax.set_xlabel('Non-dimensional time')
+ax.set_ylabel('Force coefficients')
+ax.grid()
+ax.plot(t, cd, label='$C_D$')
+ax.plot(t, cl, label='$C_L$')
+ax.plot(t2, cd2, label='$C_D$ (2D)', color='grey', linestyle='-')
+ax.plot(t2, cl2, label='$C_L$ (2D)', color='grey', linestyle='--')
+ax.legend(ncol=2)
+ax.set_xlim(t[0], t[-1])
+ax.set_ylim(0.55, 3.5)
+fig.tight_layout()
+
+# Save figure as PNG file.
+figdir = simudir / 'figures'
+figdir.mkdir(parents=True, exist_ok=True)
+filepath = figdir / 'forceCoefficientsCompare2D.png'
+fig.savefig(str(filepath), dpi=300)

### 2019-03-18 examples/snake3d2k35/scripts/plot_wz_avg_wake2d.py

@@ -1,0 +1,27 @@
+"""Create 2D pseudocolor figures of the spanwise-averaged z-vorticity."""
+
+import os
+import sys
+import pathlib
+
+scriptdir = pathlib.Path(__file__).absolute().parents[3] / 'misc'
+if scriptdir not in sys.path:
+    sys.path.insert(0, str(scriptdir))
+from visitplot import *
+
+
+simudir = pathlib.Path(__file__).absolute().parents[1]
+xdmfpath = simudir / 'output' / 'postprocessing' / 'wz_avg' / 'wz-avg.xmf'
+name = 'wz-avg'
+config_view = simudir / 'scripts' / 'visit_view2d.yaml'
+curve2dpath = simudir / 'output' / 'snake2d35.curve'
+figdir = simudir / 'figures'
+prefix = 'wz_avg_wake2d_'
+
+visit_plot_pseudocolor_2d(xdmfpath, name,
+                          value_range=(-5.0, 5.0),
+                          curve2d_paths=[curve2dpath],
+                          config_view=config_view,
+                          out_dir=figdir, out_prefix=prefix,
+                          figsize=(1024, 1024),
+                          visit_dir=os.environ.get('VISIT_DIR'))

### 2019-03-18 examples/snake3d2k35/scripts/plot_wz_wake3d.py

@@ -1,0 +1,35 @@
+"""Create 3D contour figures of the z-component of the vorticity field."""
+
+import os
+import sys
+import numpy
+import pathlib
+
+scriptdir = pathlib.Path(__file__).absolute().parents[3] / 'misc'
+if scriptdir not in sys.path:
+    sys.path.insert(0, str(scriptdir))
+from visitplot import *
+
+
+simudir = pathlib.Path(__file__).absolute().parents[1]
+xdmfpath = simudir / 'output' / 'wz.xmf'
+name = 'wz'
+config_view = simudir / 'scripts' / 'visit_view3d.yaml'
+bodypath = simudir / 'snake3d35.body'
+p3dpath = simudir / 'output' / 'snake3d35.p3d'
+figdir = simudir / 'figures'
+prefix = 'wz_wake3d_'
+
+# Create p3d file from body file.
+with open(bodypath, 'r') as infile:
+    x, y, z = numpy.loadtxt(infile, skiprows=1, unpack=True)
+with open(p3dpath, 'wb') as outfile:
+    numpy.savetxt(outfile, numpy.c_[x, y, z])
+
+visit_plot_contour_3d(xdmfpath, name,
+                      value_range=(-5.0, 5.0),
+                      p3d_paths=[p3dpath],
+                      config_view=config_view,
+                      out_dir=figdir, out_prefix=prefix,
+                      figsize=(1024, 1024),
+                      visit_dir=os.environ.get('VISIT_DIR'))

### 2019-03-18 examples/poisson/azure/amgx/01_nc24r/run-poisson.sh
Add input files and scripts for Poisson benchmark

@@ -1,0 +1,56 @@
+#!/usr/bin/env bash
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+simudir=$scriptdir
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=12
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+# get number of GPUs on machine
+ngpusmax=`nvidia-smi -L | wc -l`
+echo "Number of GPU devices available on each node: $ngpusmax"
+# number of GPUs to use per node
+CUDA_VISIBLE_DEVICES=0,1
+IFS=',' read -ra GPUS <<< "$CUDA_VISIBLE_DEVICES"
+ngpus=${#GPUS[@]}
+echo "Number of GPU devices per node to use: $ngpus ($CUDA_VISIBLE_DEVICES)"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+cd $simudir
+
+cp $AZ_BATCH_TASK_DIR/stdout.txt .
+cp $AZ_BATCH_TASK_DIR/stderr.txt .
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	echo "Run $counter" > stdout_run$counter.txt
+	mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+		poisson \
+		-caseName poisson_amgx_nodes$nodes_run$counter \
+		-mode AmgX_GPU \
+		-cfgFileName config/poisson_solver.info \
+		-Nx 500 -Ny 500 -Nz 25 \
+		-log_view ascii:view_run$counter.log \
+		-options_left >> stdout_run$counter.txt 2> stderr_run$counter.txt
+	((counter++))
+done
+
+rm -rf data
+
+exit 0

### 2019-03-18 examples/poisson/azure/amgx/01_nc24r/scripts/az-upload-input.sh

@@ -1,0 +1,30 @@
+#!/usr/bin/env bash
+
+sharename="fileshare"
+dirname="poisson/amgx/001"
+accountname="mesnardostorage"
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+casedir="$( cd "$(dirname "$scriptdir")" ; pwd -P )"
+
+source ~/.bashrc
+
+conda activate py36-cloud
+
+az storage directory create \
+	--name $dirname \
+	--share-name $sharename \
+	--account-name $accountname
+
+cp -r $casedir/../config $casedir
+
+az storage file upload-batch \
+	--source $casedir \
+	--destination $sharename/$dirname \
+	--account-name $accountname
+
+rm -rf $casedir/config
+
+conda deactivate
+
+exit 0

### 2019-03-18 examples/poisson/azure/amgx/02_nc24r/run-poisson.sh

@@ -1,0 +1,56 @@
+#!/usr/bin/env bash
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+simudir=$scriptdir
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=12
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+# get number of GPUs on machine
+ngpusmax=`nvidia-smi -L | wc -l`
+echo "Number of GPU devices available on each node: $ngpusmax"
+# number of GPUs to use per node
+CUDA_VISIBLE_DEVICES=0,1
+IFS=',' read -ra GPUS <<< "$CUDA_VISIBLE_DEVICES"
+ngpus=${#GPUS[@]}
+echo "Number of GPU devices per node to use: $ngpus ($CUDA_VISIBLE_DEVICES)"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+cd $simudir
+
+cp $AZ_BATCH_TASK_DIR/stdout.txt .
+cp $AZ_BATCH_TASK_DIR/stderr.txt .
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	echo "Run $counter" > stdout_run$counter.txt
+	mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+		poisson \
+		-caseName poisson_amgx_nodes$nodes_run$counter \
+		-mode AmgX_GPU \
+		-cfgFileName config/poisson_solver.info \
+		-Nx 500 -Ny 500 -Nz 50 \
+		-log_view ascii:view_run$counter.log \
+		-options_left >> stdout_run$counter.txt 2> stderr_run$counter.txt
+	((counter++))
+done
+
+rm -rf data
+
+exit 0

### 2019-03-18 examples/poisson/azure/amgx/04_nc24r/run-poisson.sh

@@ -1,0 +1,56 @@
+#!/usr/bin/env bash
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+simudir=$scriptdir
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=12
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+# get number of GPUs on machine
+ngpusmax=`nvidia-smi -L | wc -l`
+echo "Number of GPU devices available on each node: $ngpusmax"
+# number of GPUs to use per node
+CUDA_VISIBLE_DEVICES=0,1
+IFS=',' read -ra GPUS <<< "$CUDA_VISIBLE_DEVICES"
+ngpus=${#GPUS[@]}
+echo "Number of GPU devices per node to use: $ngpus ($CUDA_VISIBLE_DEVICES)"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+cd $simudir
+
+cp $AZ_BATCH_TASK_DIR/stdout.txt .
+cp $AZ_BATCH_TASK_DIR/stderr.txt .
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	echo "Run $counter" > stdout_run$counter.txt
+	mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+		poisson \
+		-caseName poisson_amgx_nodes$nodes_run$counter \
+		-mode AmgX_GPU \
+		-cfgFileName config/poisson_solver.info \
+		-Nx 1000 -Ny 500 -Nz 50 \
+		-log_view ascii:view_run$counter.log \
+		-options_left >> stdout_run$counter.txt 2> stderr_run$counter.txt
+	((counter++))
+done
+
+rm -rf data
+
+exit 0

### 2019-03-18 examples/poisson/azure/amgx/08_nc24r/run-poisson.sh

@@ -1,0 +1,56 @@
+#!/usr/bin/env bash
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+simudir=$scriptdir
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=12
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+# get number of GPUs on machine
+ngpusmax=`nvidia-smi -L | wc -l`
+echo "Number of GPU devices available on each node: $ngpusmax"
+# number of GPUs to use per node
+CUDA_VISIBLE_DEVICES=0,1
+IFS=',' read -ra GPUS <<< "$CUDA_VISIBLE_DEVICES"
+ngpus=${#GPUS[@]}
+echo "Number of GPU devices per node to use: $ngpus ($CUDA_VISIBLE_DEVICES)"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+cd $simudir
+
+cp $AZ_BATCH_TASK_DIR/stdout.txt .
+cp $AZ_BATCH_TASK_DIR/stderr.txt .
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	echo "Run $counter" > stdout_run$counter.txt
+	mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+		poisson \
+		-caseName poisson_amgx_nodes$nodes_run$counter \
+		-mode AmgX_GPU \
+		-cfgFileName config/poisson_solver.info \
+		-Nx 1000 -Ny 1000 -Nz 50 \
+		-log_view ascii:view_run$counter.log \
+		-options_left >> stdout_run$counter.txt 2> stderr_run$counter.txt
+	((counter++))
+done
+
+rm -rf data
+
+exit 0

### 2019-03-18 examples/poisson/azure/petsc/01_h16r/scripts/az-upload-input.sh

@@ -1,0 +1,30 @@
+#!/usr/bin/env zsh
+
+sharename="fileshare"
+dirname="poisson/petsc/001"
+accountname="mesnardostorage"
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+casedir="$( cd "$(dirname "$scriptdir")" ; pwd -P )"
+
+source ~/.zshrc
+
+conda activate py36-az
+
+az storage directory create \
+	--name $dirname \
+	--share-name $sharename \
+	--account-name $accountname
+
+cp -r $casedir/../config $casedir
+
+az storage file upload-batch \
+	--source $casedir \
+	--destination $sharename/$dirname \
+	--account-name $accountname
+
+rm -rf $casedir/config
+
+conda deactivate
+
+exit 0

### 2019-03-18 examples/poisson/azure/petsc/02_h16r/run-poisson.sh

@@ -1,0 +1,47 @@
+#!/usr/bin/env bash
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+simudir=$scriptdir
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=16
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+cd $simudir
+
+cp $AZ_BATCH_TASK_DIR/stdout.txt .
+cp $AZ_BATCH_TASK_DIR/stderr.txt .
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	echo "Run $counter" > stdout_run$counter.txt
+	mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+		poisson \
+		-caseName poisson_petsc_nodes$nodes_run$counter \
+		-mode PETSc \
+		-cfgFileName config/poisson_solver.info \
+		-Nx 1000 -Ny 1000 -Nz 50 \
+		-log_view ascii:view_run$counter.log \
+		-options_left >> stdout_run$counter.txt 2> stderr_run$counter.txt
+	((counter++))
+done
+
+rm -rf data
+
+exit 0

### 2019-03-18 examples/poisson/colonialone/amgx/01_ivygpu/run-poisson.sh

@@ -1,0 +1,45 @@
+#!/usr/bin/env bash
+
+#SBATCH --job-name="01amgx"
+#SBATCH --output=log%j.out
+#SBATCH --error=log%j.err
+#SBATCH --partition=ivygpu
+#SBATCH --nodes=1
+#SBATCH --ntasks-per-node=12
+#SBATCH --time=01:00:00
+
+nodes=1
+
+module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
+module load cuda/toolkit/8.0
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
+
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
+
+export CUDA_VISIBLE_DEVICES=0,1
+
+configdir="../config"
+outdir="output"
+mkdir -p $outdir
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	casename="poisson_amgx_${nodes}nodes_run${counter}"
+	mpiexec poisson \
+		-caseName $casename \
+		-mode AmgX_GPU \
+		-cfgFileName $configdir/poisson_solver.info \
+		-Nx 500 -Ny 500 -Nz 25 \
+		-log_view ascii:${outdir}/view_run${counter}.log \
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+	((counter++))
+done
+
+exit 0

### 2019-03-18 examples/poisson/colonialone/amgx/02_ivygpu/run-poisson.sh

@@ -1,0 +1,45 @@
+#!/usr/bin/env bash
+
+#SBATCH --job-name="02amgx"
+#SBATCH --output=log%j.out
+#SBATCH --error=log%j.err
+#SBATCH --partition=ivygpu
+#SBATCH --nodes=2
+#SBATCH --ntasks-per-node=12
+#SBATCH --time=01:00:00
+
+nodes=2
+
+module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
+module load cuda/toolkit/8.0
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
+
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
+
+export CUDA_VISIBLE_DEVICES=0,1
+
+configdir="../config"
+outdir="output"
+mkdir -p $outdir
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	casename="poisson_amgx_${nodes}nodes_run${counter}"
+	mpiexec poisson \
+		-caseName $casename \
+		-mode AmgX_GPU \
+		-cfgFileName $configdir/poisson_solver.info \
+		-Nx 500 -Ny 500 -Nz 50 \
+		-log_view ascii:${outdir}/view_run${counter}.log \
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+	((counter++))
+done
+
+exit 0

### 2019-03-18 examples/poisson/colonialone/amgx/04_ivygpu/run-poisson.sh

@@ -1,0 +1,45 @@
+#!/usr/bin/env bash
+
+#SBATCH --job-name="04amgx"
+#SBATCH --output=log%j.out
+#SBATCH --error=log%j.err
+#SBATCH --partition=ivygpu
+#SBATCH --nodes=4
+#SBATCH --ntasks-per-node=12
+#SBATCH --time=00:30:00
+
+nodes=4
+
+module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
+module load cuda/toolkit/8.0
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
+
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
+
+export CUDA_VISIBLE_DEVICES=0,1
+
+configdir="../config"
+outdir="output"
+mkdir -p $outdir
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	casename="poisson_amgx_${nodes}nodes_run${counter}"
+	mpiexec poisson \
+		-caseName $casename \
+		-mode AmgX_GPU \
+		-cfgFileName $configdir/poisson_solver.info \
+		-Nx 1000 -Ny 500 -Nz 50 \
+		-log_view ascii:${outdir}/view_run${counter}.log \
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+	((counter++))
+done
+
+exit 0

### 2019-03-18 examples/poisson/colonialone/amgx/08_ivygpu/run-poisson.sh

@@ -1,0 +1,45 @@
+#!/usr/bin/env bash
+
+#SBATCH --job-name="08amgx"
+#SBATCH --output=log%j.out
+#SBATCH --error=log%j.err
+#SBATCH --partition=ivygpu
+#SBATCH --nodes=8
+#SBATCH --ntasks-per-node=12
+#SBATCH --time=00:30:00
+
+nodes=8
+
+module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
+module load cuda/toolkit/8.0
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
+
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
+
+export CUDA_VISIBLE_DEVICES=0,1
+
+configdir="../config"
+outdir="output"
+mkdir -p $outdir
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	casename="poisson_amgx_${nodes}nodes_run${counter}"
+	mpiexec poisson \
+		-caseName $casename \
+		-mode AmgX_GPU \
+		-cfgFileName $configdir/poisson_solver.info \
+		-Nx 1000 -Ny 1000 -Nz 50 \
+		-log_view ascii:${outdir}/view_run${counter}.log \
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+	((counter++))
+done
+
+exit 0

### 2019-03-18 examples/poisson/colonialone/petsc/01_short/run-poisson.sh

@@ -1,0 +1,43 @@
+#!/usr/bin/env bash
+
+#SBATCH --job-name="01petsc"
+#SBATCH --output=log%j.out
+#SBATCH --error=log%j.err
+#SBATCH --partition=short
+#SBATCH --nodes=1
+#SBATCH --ntasks-per-node=16
+#SBATCH --time=01:00:00
+
+nodes=1
+
+module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
+module load cuda/toolkit/8.0
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
+
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
+
+configdir="../config"
+outdir="output"
+mkdir -p $outdir
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	casename="poisson_petsc_${nodes}nodes_run${counter}"
+	mpiexec poisson \
+		-caseName $casename \
+		-mode PETSc \
+		-cfgFileName $configdir/poisson_solver.info \
+		-Nx 1000 -Ny 1000 -Nz 50 \
+		-log_view ascii:${outdir}/view_run${counter}.log \
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+	((counter++))
+done
+
+exit 0

### 2019-03-18 examples/poisson/colonialone/petsc/02_short/run-poisson.sh

@@ -1,0 +1,43 @@
+#!/usr/bin/env bash
+
+#SBATCH --job-name="02petsc"
+#SBATCH --output=log%j.out
+#SBATCH --error=log%j.err
+#SBATCH --partition=short
+#SBATCH --nodes=2
+#SBATCH --ntasks-per-node=16
+#SBATCH --time=00:20:00
+
+nodes=2
+
+module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
+module load cuda/toolkit/8.0
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
+
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
+
+configdir="../config"
+outdir="output"
+mkdir -p $outdir
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	casename="poisson_petsc_${nodes}nodes_run${counter}"
+	mpiexec poisson \
+		-caseName $casename \
+		-mode PETSc \
+		-cfgFileName $configdir/poisson_solver.info \
+		-Nx 1000 -Ny 1000 -Nz 50 \
+		-log_view ascii:${outdir}/view_run${counter}.log \
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+	((counter++))
+done
+
+exit 0

### 2019-03-18 examples/poisson/colonialone/petsc/04_short/run-poisson.sh

@@ -1,0 +1,43 @@
+#!/usr/bin/env bash
+
+#SBATCH --job-name="04petsc"
+#SBATCH --output=log%j.out
+#SBATCH --error=log%j.err
+#SBATCH --partition=short
+#SBATCH --nodes=4
+#SBATCH --ntasks-per-node=16
+#SBATCH --time=00:20:00
+
+nodes=4
+
+module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
+module load cuda/toolkit/8.0
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
+
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
+
+configdir="../config"
+outdir="output"
+mkdir -p $outdir
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	casename="poisson_petsc_${nodes}nodes_run${counter}"
+	mpiexec poisson \
+		-caseName $casename \
+		-mode PETSc \
+		-cfgFileName $configdir/poisson_solver.info \
+		-Nx 1000 -Ny 1000 -Nz 50 \
+		-log_view ascii:${outdir}/view_run${counter}.log \
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+	((counter++))
+done
+
+exit 0

### 2019-03-18 examples/poisson/colonialone/petsc/08_short/run-poisson.sh

@@ -1,0 +1,43 @@
+#!/usr/bin/env bash
+
+#SBATCH --job-name="08petsc"
+#SBATCH --output=log%j.out
+#SBATCH --error=log%j.err
+#SBATCH --partition=short
+#SBATCH --nodes=8
+#SBATCH --ntasks-per-node=16
+#SBATCH --time=00:20:00
+
+nodes=8
+
+module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
+module load cuda/toolkit/8.0
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
+
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
+
+configdir="../config"
+outdir="output"
+mkdir -p $outdir
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	casename="poisson_petsc_${nodes}nodes_run${counter}"
+	mpiexec poisson \
+		-caseName $casename \
+		-mode PETSc \
+		-cfgFileName $configdir/poisson_solver.info \
+		-Nx 1000 -Ny 1000 -Nz 50 \
+		-log_view ascii:${outdir}/view_run${counter}.log \
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+	((counter++))
+done
+
+exit 0

### 2019-03-18 examples/poisson/scripts/plot_runtimes.py

@@ -1,0 +1,264 @@
+"""Plot the time-to-solution versus the number of nodes."""
+
+import pathlib
+from matplotlib import pyplot, gridspec
+import numpy
+
+
+def get_filepaths(casedir, prefix='stdout_run', suffix='.txt', niter=5):
+    """Get the file paths with data to read.
+
+    Parameters
+    ----------
+    casedir : pathlib.Path object
+        Directory that contains the files to read.
+    prefix : string (optional)
+        Common prefix of the file names; default: 'stdout_run'.
+    suffix : string (optional)
+        Common suffix of the file names; default: '.txt'.
+    niter : integer (optional)
+        Number of repeated runs (i.e., number of files to read).
+
+    Returns
+    -------
+    filepaths : list of pathlib.Path objects
+        The file paths.
+
+    """
+    filepaths = [casedir / (prefix + str(i + 1) + suffix)
+                 for i in range(niter)]
+    return filepaths
+
+
+def amgxwrapper_poisson_read_runtimes(*filepaths):
+    """Read the runtimes to solve the system for multiple runs.
+
+    Parameters
+    ----------
+    filepaths : tuple of strings or pathlib.Path objects
+        Path of the files to read.
+
+    Returns
+    -------
+    runtimes : list of floats
+        The runtimes.
+
+    """
+    runtimes = []
+    for filepath in filepaths:
+        with open(filepath, 'r') as infile:
+            prev_line = ''
+            for line in infile:
+                if 'Solve Time:' in line:
+                    if not prev_line.startswith('Warm-up'):
+                        runtime = float(line.split(' ')[-1])
+                        runtimes.append(runtime)
+                prev_line = line
+    return runtimes
+
+
+def amgxwrapper_poisson_read_iterations(filepath):
+    """Read the number of iterations to solve the system.
+
+    Parameters
+    ----------
+    filepath : string or pathlib.Path object
+        Path of the file to read.
+
+    Returns
+    -------
+    nites : integer
+        The number of iterations.
+
+    """
[…]

### 2019-03-18 tex/MesnardoBarba2019.tex
add tex file with IEEEtran class

\documentclass[10pt,journal,compsoc]{IEEEtran}

\usepackage{algorithmic}
\usepackage{array}
 \usepackage[nocompress]{cite}
 \usepackage{color}
\usepackage{listings}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{stfloats}
\usepackage{url}

\usepackage[pdftex]{graphicx}
\graphicspath{{./figs}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}

% *** MATH PACKAGES ***
\usepackage{amsmath}
\interdisplaylinepenalty=2500

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

% title
\title{Reproducible workflow on a public cloud for computational fluid dynamics}
% author names and affiliations
\author{Olivier Mesnard, Lorena A. Barba
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem Mechanical and Aerospace Engineering,
the George Washington University, Washington, DC 20052.\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: mesnardog@gwu.edu
\IEEEcompsocthanksitem Email: labarba@gwu.edu}% <-this % stops an unwanted space
%\thanks{Manuscript submitted 2019}
}

% make the title area
\maketitle

% abstract

% start the article

% \section*{Acknowledgment}

%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
%\begin{thebibliography}{1}
%\bibitem
%\end{thebibliography}

\end{document}

### 2019-03-18 tex/MesnardoBarba2019.tex
add abstract

@@
 
+\IEEEtitleabstractindextext{%
+\begin{abstract}
+In a new effort to make our research transparent and reproducible by others, we have developed a workflow to run computational studies on a public cloud.
+It uses Docker containers to create an image of the application software stack.
+We also adopt several tools that facilitate creating and managing virtual machines with compute nodes and submitting jobs to these nodes.
+The configuration files for these tools are part of an expanded "reproducibility package" that includes workflow definitions for cloud computing, in addition to input files and instructions.
+This facilitates re-creating the cloud environment to re-un the simulations under the same conditions.
+\end{abstract}
+}
+
 % make the title area

### 2019-03-18 examples/snake2d2k35/scripts/plot_wz_wake2d.py
Review scripts to plot with VisIt

@@ -1,8 +1,9 @@
 """Generate figures of the 2D pseudocolor of the 2D vorticity field."""
 
+import numpy
 import os
-import sys
 import pathlib
+import sys
 
 root_dir = pathlib.Path(__file__).absolute().parents[3]
 scripts_dir = root_dir / 'misc'
@@ -15,9 +16,17 @@ simudir = pathlib.Path(__file__).absolute().parents[1]
 xdmfpath = simudir / 'output' / 'postprocessing' / 'wz' / 'wz.xmf'
 name = 'wz'
 config_view = simudir / 'scripts' / 'visit_view2d.yaml'
+body2dpath = simudir / 'output' / 'snake2d35.body'
 curve2dpath = simudir / 'output' / 'snake2d35.curve'
 figdir = simudir / 'figures'
 prefix = 'wz_wake2d_'
+
+# Create .curve file if not already present.
+if not curve2dpath.is_file():
+    with open(str(body2dpath), 'r') as infile:
+        x, y = numpy.loadtxt(infile, skiprows=1, unpack=True)
+    with open(str(curve2dpath), 'w') as outfile:
+        numpy.savetxt(outfile, numpy.c_[x, y])
 
 visit_plot_pseudocolor_2d(xdmfpath, name,
                           value_range=(-5.0, 5.0),
@@ -25,4 +34,4 @@ visit_plot_pseudocolor_2d(xdmfpath, name,
                           config_view=config_view,
                           out_dir=figdir, out_prefix=prefix,
                           figsize=(1024, 1024),
-                          visit_dir=os.environ.get('VISIT_DIR'))
+                          visit_dir=os.environ.get('VISIT_DIR'), state=1)

### 2019-03-18 examples/snake3d2k35/scripts/average_wz.py

@@ -19,7 +19,7 @@ outdir.mkdir(parents=True, exist_ok=True)
 
 # Read 3D grid and write 2D grid.
 gridpath = simudir / 'output' / 'grid.h5'
-x, y, _ = petibmpy.petibm_read_grid_hdf5(gridpath, name)
+x, y, _ = petibmpy.read_grid_hdf5(gridpath, name)
 gridpath = outdir / 'grid.h5'
 petibmpy.write_grid_hdf5(gridpath, name + '-avg', x, y)
 
@@ -29,6 +29,7 @@ with open(filepath, 'r') as infile:
     config = yaml.load(infile)['parameters']
 nstart, nt, nsave = config['startStep'], config['nt'], config['nsave']
 dt = config['dt']
+nstart, nt = 100000, 0
 timesteps = list(range(nstart, nstart + nt + 1, nsave))
 
 # Average the scalar field along the z-direction and write field.

### 2019-03-18 examples/snake3d2k35/scripts/plot_wz_avg_wake2d.py

@@ -1,8 +1,9 @@
 """Create 2D pseudocolor figures of the spanwise-averaged z-vorticity."""
 
+import numpy
 import os
-import sys
 import pathlib
+import sys
 
 scriptdir = pathlib.Path(__file__).absolute().parents[3] / 'misc'
 if scriptdir not in sys.path:
@@ -14,9 +15,17 @@ simudir = pathlib.Path(__file__).absolute().parents[1]
 xdmfpath = simudir / 'output' / 'postprocessing' / 'wz_avg' / 'wz-avg.xmf'
 name = 'wz-avg'
 config_view = simudir / 'scripts' / 'visit_view2d.yaml'
+body3dpath = simudir / 'output' / 'snake3d35.body'
 curve2dpath = simudir / 'output' / 'snake2d35.curve'
 figdir = simudir / 'figures'
 prefix = 'wz_avg_wake2d_'
+
+# Create curve file from body file.
+if not curve2dpath.is_file():
+    with open(str(body3dpath), 'r') as infile:
+        x, y, _ = numpy.loadtxt(infile, skiprows=1, unpack=True)
+    with open(str(curve2dpath), 'wb') as outfile:
+        numpy.savetxt(outfile, numpy.c_[x, y])
 
 visit_plot_pseudocolor_2d(xdmfpath, name,
                           value_range=(-5.0, 5.0),

### 2019-03-18 examples/snake3d2k35/scripts/plot_wz_wake3d.py

@@ -1,9 +1,9 @@
 """Create 3D contour figures of the z-component of the vorticity field."""
 
-import os
-import sys
 import numpy
+import os
 import pathlib
+import sys
 
 scriptdir = pathlib.Path(__file__).absolute().parents[3] / 'misc'
 if scriptdir not in sys.path:
@@ -21,10 +21,11 @@ figdir = simudir / 'figures'
 prefix = 'wz_wake3d_'
 
 # Create p3d file from body file.
-with open(bodypath, 'r') as infile:
-    x, y, z = numpy.loadtxt(infile, skiprows=1, unpack=True)
-with open(p3dpath, 'wb') as outfile:
-    numpy.savetxt(outfile, numpy.c_[x, y, z])
+if not p3dpath.is_file():
+    with open(bodypath, 'r') as infile:
+        x, y, z = numpy.loadtxt(infile, skiprows=1, unpack=True)
+    with open(p3dpath, 'wb') as outfile:
+        numpy.savetxt(outfile, numpy.c_[x, y, z])
 
 visit_plot_contour_3d(xdmfpath, name,
                       value_range=(-5.0, 5.0),

### 2019-03-18 misc/visitplot.py

@@ -1,6 +1,4 @@
-"""
-Functions to generate plots of the flow field with VisIt.
-"""
+"""Functions to generate plots of the flow field with VisIt."""
 
 import os
 import sys

### 2019-03-19 examples/osubenchmarks/scripts/plot_latency_bandwidth.py
Use 2 rows for OSU figure

@@ -97,7 +97,7 @@ data[label]['bandwidth'] = {'sizes': sizes, 'values': bandwidths}
 
 # Create a figure to display the latency and bandwidth results.
 pyplot.rc('font', family='serif', size=14)
-fig, (ax1, ax2) = pyplot.subplots(ncols=2, figsize=(10.0, 3.0))
+fig, (ax1, ax2) = pyplot.subplots(nrows=2, figsize=(6.0, 8.0))
 # Plot the latency.
 ax1.set_xlabel('Message size (bytes)')
 ax1.set_ylabel('Point-to-point\nlatency ($\mu$s)')
@@ -127,4 +127,4 @@ figdir.mkdir(parents=True, exist_ok=True)
 filepath = figdir / 'osu_latency_bandwidth.png'
 fig.savefig(str(filepath), dpi=300)
 
-pyplot.show()
+#pyplot.show()

### 2019-03-19 examples/snake3d2k35/scripts/plot_force_coefficients_compare_2d.py
Add code to time-average force coefficients

@@ -21,6 +21,8 @@ c = 1.0  # chord length
 Lz = 3.2 * c  # spanwise length
 coeff = 1 / (dyn_pressure * c * Lz)  # scaling factor for force coefficients
 cd, cl, cz = petibmpy.get_force_coefficients(fx, fy, fz, coeff=coeff)
+cd_avg, cl_avg = petibmpy.get_time_averaged_values(t, cd, cl,
+                                                   limits=(40.0, 80.0))
 
 # Read 2D forces and convert to force coefficients.
 rootdir = simudir.parent
@@ -29,6 +31,14 @@ filepath = simudir2d / 'output' / 'forces-0.txt'
 t2, fx2, fy2 = petibmpy.read_forces(filepath)
 coeff = 1 / (dyn_pressure * c)
 cd2, cl2 = petibmpy.get_force_coefficients(fx2, fy2, coeff=coeff)
+cd2_avg, cl2_avg = petibmpy.get_time_averaged_values(t2, cd2, cl2,
+                                                     limits=(40.0, 80.0))
+cd_reldiff = (cd2_avg - cd_avg) / cd_avg * 100.0
+cl_reldiff = (cl2_avg - cl_avg) / cl_avg * 100.0
+print('Case\t<CD>\t<CL>')
+print('3D\t{:.4f}\t{:.4f}'.format(cd_avg, cl_avg))
+print('2D\t{:.4f} ({:.1f})\t {:.4f} ({:.1f})'
+      .format(cd2_avg, cd_reldiff, cl2_avg, cl_reldiff))
 
 # Plot force coefficients over time.
 pyplot.rc('font', family='serif', size=16)

### 2019-03-19 examples/snake2d2k35/scripts/plot_wz_wake2_pyplot.py
Add Python script and figure to plot 2D vorticity at multiple time units

@@ -1,0 +1,64 @@
+"""Plot the 2D vorticity field at different time steps."""
+
+import pathlib
+import matplotlib
+matplotlib.use('TkAgg')
+from matplotlib import pyplot
+import numpy
+import yaml
+
+import petibmpy
+
+
+name = 'wz'  # name of the field variable (z-vorticity)
+
+# Get directories.
+rootdir = pathlib.Path(__file__).absolute().parents[1]
+datadir = rootdir / 'output'
+
+# Read the grid.
+gridpath = datadir / 'grid.h5'
+x, y = petibmpy.read_grid_hdf5(gridpath, name)
+X, Y = numpy.meshgrid(x, y)
+
+# Read the body coordinates.
+filepath = datadir / 'snake2d35.body'
+with open(filepath, 'r') as infile:
+    xb, yb = numpy.loadtxt(infile, skiprows=1, unpack=True)
+
+# Read the time parameters from YAML configuration file.
+filepath = rootdir / 'config.yaml'
+with open(filepath, 'r') as infile:
+    config = yaml.load(infile, Loader=yaml.FullLoader)['parameters']
+nstart, nt, nsave = config['startStep'], config['nt'], config['nsave']
+dt = config['dt']
+
+# Select time units to plot.
+times = [20.0, 44.0, 45.0, 80.0]
+timesteps = [int(t / dt) for t in times]
+
+# Plot the filled contour of the field variable at selected times.
+pyplot.rc('font', family='serif', size=12)
+fig, ax = pyplot.subplots(nrows=len(times), figsize=(5.0, 8.0), sharex=True)
+levels = numpy.linspace(-5.0, 5.0, num=51)
+for i, (time, timestep) in enumerate(zip(times, timesteps)):
+    print('[time step {}]'.format(timestep))
+    filepath = datadir / 'solution' / '{:0>7}.h5'.format(timestep)
+    data = petibmpy.read_field_hdf5(filepath, name)
+    ax[i].text(-0.5, 1.0, 't = {:.1f}'.format(time))
+    ax[i].set_ylabel('y/c')
+    ax[i].contourf(X, Y, data, levels=levels, extend='both')
+    ax[i].plot(xb, yb, color='black')
+    ax[i].axis('scaled', adjustable='box')
+    ax[i].set_xlim(-1.0, 6.0)
+    ax[i].set_ylim(-1.5, 1.5)
+ax[-1].set_xlabel('x/c')
[…]

### 2019-03-19 misc/rsyncfigures.sh
Add bash script to rsync figures to use in manuscript

@@ -1,0 +1,14 @@
+#!/usr/bin/env bash
+# Rsync figures for manuscript.
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+rootdir="$( cd "$(dirname "$scriptdir")" ; pwd -P )"
+
+listpath="$scriptdir/rsyncfigureslist.txt"
+destdir="$rootdir/tex/figures/"
+
+mkdir -p $destdir
+
+rsync -av --no-relative --files-from=$listpath $rootdir $destdir
+
+exit 0

### 2019-03-19 tex/MesnardoBarba2019.tex
add intro heading
[WIP] Add figures and captions et al.
Also

* Start paragraph to describe cloud workflow.
* Start description of the snake application.

@@
 % title
-\title{Reproducible workflow on a public cloud for computational fluid dynamics}
+\title{Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics}
 % author names and affiliations
@@
 % \\ is fragile and will error, could use \hfil\break instead.
-E-mail: mesnardog@gwu.edu
+E-mail: mesnardo@gwu.edu
 \IEEEcompsocthanksitem Email: labarba@gwu.edu}% <-this % stops an unwanted space
@@
 
-% abstract
+\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
 
-% start the article
+\section{Reproducible Workflow}\label{sec:workflow}
+
+CFD publications often lack details about external libraries used along with the main computational code.
+We have learned the hard way how different versions of the same external library can alter the numerical results and even the scientific findings of a computational study\cite{mesnard_barba_2017}.
+To overcome the so-called ``dependency hell'' and facilitate reproducibility, we use Docker to locally create an image of our computational application.
+Container technology facilitates share build images of the full software stack that is used to produce scientific results.
+The process of building an image using Docker begins with writing an ASCII file, called a Dockerfile, that contains Docker keywords and system commands for building multi-layered software stack.
+Once the image is build locally, we push it to a public registry (e.g., DockerHub).
+Everyone can now pull the application image and create a container to run the application in a faithfully reproduced local environment.
+We aim to move the final stage of this workflow (creating a container) to a public cloud provider such as Microsoft Azure.
+
+To run computational jobs on Microsoft Azure, we use several tools that facilitate creating and managing virtual machines with compute nodes and submitting jobs to those nodes.
+\ref{fig:cloud_workflow} shows a graphical representation of the workflow we adopted to run CFD simulations with an in-house software on Microsoft Azure.
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=7cm]{figures/cloud_workflow.png}
+    \caption{Reproducible workflow on the public cloud provider Microsoft Azure.}
+    \label{fig:cloud_workflow}
+\end{figure}
+
+\begin{table}[!t]
+    \caption{NC series on Microsoft Azure. (Prices as of May 13, 2018.)}
+    \label{tab:nc_series}
+    \centering
+    \begin{tabular}{cccccccc}
+        Instance & cores & RAM (GiB) & disk sizes (GiB) & GPU & pay-as-you-go (\$/hr) & 1-year reserved (\$/hr) & 3-year reserved (\$/hr) \\
+        \hline
+        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.574 & 0.40 \\
+        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 1.147 & 0.80 \\
+        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.294 & 1.599 \\
+        NC24r$^\dagger$ & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.523 & 1.758 \\
+        \hline
+    \end{tabular}
+    $\dagger$ NC24r: RDMA (Remote Direct Access Memory) capable with InfiniBand network.
+\end{table}
+
+\section{Results}\label{sec:results}
+
+\subsection{MPI Communication Benchmarks}\label{subsec:mpi_benchmarks}
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=7cm]{figures/osu_latency_bandwidth.png}
+    \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One and on NC24r instances of Microsoft Azure.}
+    \label{fig:osu_benchmarks}
+\end{figure}
+
+\subsection{Poisson Benchmarks}\label{subsec:poisson_benchmarks}
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=7cm]{figures/poisson_time_vs_nodes.png}
+    \caption{Runtimes to solve a Poisson system on Colonial One and on Microsoft Azure.}
+    \label{fig:poisson_benchmarks}
+\end{figure}
+
+\subsection{Flow Around a Flying Snake Cross-Section}\label{subsec:snake}
+
+Our research lab is interested in understanding the aerodynamics of flying animals using Computational Fluid Dynamics software.
+One of our applications deals with the aerodynamics of a snake species, \textit{Chrysopelea Paradisi}, that lives in South-East Asia.
+The arboreal reptile has the remarkable capacity to turn its entire body into a wing and glide over several meters\cite{socha_2011}.
+The so-called flying snake jumps from tree branches, undulates in the air, and is able to produce lift by expanding its ribcage to flatten its ventral surface (morphing its normally circular cross-section into a triangular shape).
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=7cm]{figures/wz_multi_contourf.png}
+    \caption{Filled contour of the vorticity field after $20$, $44$, $45$, and $80$ time units fo flow simulation with PetIBM for the snake cross-section at a $35$-degree angle of attack and Reynolds number $2000$.
+Vortex merging events are responsible for the change in the wake signature and the drop in the mean value of the lift coefficient.}
+    \label{fig:vorticity2d}
+\end{figure}
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=7cm]{figures/forceCoefficientsCompare2D.png}
+    \caption{History of the force coefficients obtained with two- and three-dimensional simulations at Reynolds number $2000$ for a snake cross-section with a $35$-degree angle of attack.}
+    \label{fig:force_coefficients}
+\end{figure}
+
+\begin{table}[!t]
+    \caption{Time-averaged force coefficients on the snake cross-section at Reynolds number 1000 and angle of attack $35^o$ for the two- and three-dimensional configurations.
+(We average the force coefficients between $40$ and $80$ time units of flow simulation.)}
+    \label{tab:force_coefficients}
+    \centering
+    \begin{tabular}{ccll}
+        \hline
+        Case & Mesh size & $<C_D>$ & $<C_L>$ \\
+        \hline
+        3D & $1071 \times 1072 \times 40$ & $0.8390$ & $1.5972$ \\
+        2D & $1704 \times 1706$ & $1.1567$ ($+37.9\%$) & $1.8279$ ($+14.4\%$) \\
+        \hline
+    \end{tabular}
+\end{table}
 
@@
 
-%\bibliographystyle{IEEEtran}
+\bibliographystyle{IEEEtran}
 % argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
+\bibliography{IEEEabrv,MesnardoBarba2019}
 %

### 2019-03-19 examples/osubenchmarks/scripts/plot_latency_bandwidth.py
Use PDF for line figures, PNG for filled contours

@@ -124,7 +124,7 @@ fig.tight_layout()
 # Save the figure.
 figdir = rootdir / 'figures'
 figdir.mkdir(parents=True, exist_ok=True)
-filepath = figdir / 'osu_latency_bandwidth.png'
+filepath = figdir / 'osu_latency_bandwidth.pdf'
 fig.savefig(str(filepath), dpi=300)
 
 #pyplot.show()

### 2019-03-19 examples/poisson/scripts/plot_runtimes.py

@@ -150,7 +150,7 @@ data = {'Colonial One': {}, 'Azure': {}}
 nodes = [1, 2, 4, 8]
 subdata = {'nodes': [], 'min': [], 'max': [], 'means': []}
 for n in nodes:
-    casedir = rootdir / f'colonialone/petsc/{n:0>2}_short'
+    casedir = rootdir / f'colonialone/petsc/{n:0>2}_short/output'
     filepaths = get_filepaths(casedir)
     runtimes = amgxwrapper_poisson_read_runtimes(*filepaths)
     store_runtime_stats(subdata, n, get_runtime_stats(runtimes))
@@ -159,7 +159,7 @@ data['Colonial One']['PETSc'] = gather_arrays(subdata)
 nodes = [1, 2, 4, 8]
 subdata = {'nodes': [], 'min': [], 'max': [], 'means': []}
 for n in nodes:
-    casedir = rootdir / f'colonialone/amgx/{n:0>2}_ivygpu'
+    casedir = rootdir / f'colonialone/amgx/{n:0>2}_ivygpu/output'
     filepaths = get_filepaths(casedir)
     runtimes = amgxwrapper_poisson_read_runtimes(*filepaths)
     nites = amgxwrapper_poisson_read_iterations(filepaths[0])
@@ -179,7 +179,7 @@ data['Azure']['PETSc'] = gather_arrays(subdata)
 nodes = [1, 2, 4, 8]
 subdata = {'nodes': [], 'min': [], 'max': [], 'means': []}
 for n in nodes:
-    casedir = rootdir / f'azure/amgx/{n:0>2}_nc24r_new/output'
+    casedir = rootdir / f'azure/amgx/{n:0>2}_nc24r/output'
     filepaths = get_filepaths(casedir)
     runtimes = amgxwrapper_poisson_read_runtimes(*filepaths)
     nites = amgxwrapper_poisson_read_iterations(filepaths[0])
@@ -257,7 +257,7 @@ ax3.set_ylim(0.0, 0.05)
 # Save the figure.
 figdir = rootdir / 'figures'
 figdir.mkdir(parents=True, exist_ok=True)
-filepath = figdir / 'poisson_time_vs_nodes.png'
+filepath = figdir / 'poisson_time_vs_nodes.pdf'
 fig.tight_layout()
 fig.savefig(str(filepath), dpi=300)
 

### 2019-03-19 examples/snake2d2k35/scripts/plot_wz_wake2d_pyplot.py

@@ -1,0 +1,64 @@
+"""Plot the 2D vorticity field at different time steps."""
+
+import pathlib
+import matplotlib
+matplotlib.use('TkAgg')
+from matplotlib import pyplot
+import numpy
+import yaml
+
+import petibmpy
+
+
+name = 'wz'  # name of the field variable (z-vorticity)
+
+# Get directories.
+rootdir = pathlib.Path(__file__).absolute().parents[1]
+datadir = rootdir / 'output'
+
+# Read the grid.
+gridpath = datadir / 'grid.h5'
+x, y = petibmpy.read_grid_hdf5(gridpath, name)
+X, Y = numpy.meshgrid(x, y)
+
+# Read the body coordinates.
+filepath = datadir / 'snake2d35.body'
+with open(filepath, 'r') as infile:
+    xb, yb = numpy.loadtxt(infile, skiprows=1, unpack=True)
+
+# Read the time parameters from YAML configuration file.
+filepath = rootdir / 'config.yaml'
+with open(filepath, 'r') as infile:
+    config = yaml.load(infile, Loader=yaml.FullLoader)['parameters']
+nstart, nt, nsave = config['startStep'], config['nt'], config['nsave']
+dt = config['dt']
+
+# Select time units to plot.
+times = [20.0, 44.0, 45.0, 80.0]
+timesteps = [int(t / dt) for t in times]
+
+# Plot the filled contour of the field variable at selected times.
+pyplot.rc('font', family='serif', size=12)
+fig, ax = pyplot.subplots(nrows=len(times), figsize=(5.0, 8.0), sharex=True)
+levels = numpy.linspace(-5.0, 5.0, num=51)
+for i, (time, timestep) in enumerate(zip(times, timesteps)):
+    print('[time step {}]'.format(timestep))
+    filepath = datadir / 'solution' / '{:0>7}.h5'.format(timestep)
+    data = petibmpy.read_field_hdf5(filepath, name)
+    ax[i].text(-0.5, 1.0, 't = {:.1f}'.format(time))
+    ax[i].set_ylabel('y/c')
+    ax[i].contourf(X, Y, data, levels=levels, extend='both')
+    ax[i].plot(xb, yb, color='black')
+    ax[i].axis('scaled', adjustable='box')
+    ax[i].set_xlim(-1.0, 6.0)
+    ax[i].set_ylim(-1.5, 1.5)
+ax[-1].set_xlabel('x/c')
[…]

### 2019-03-19 examples/snake3d2k35/scripts/average_wz.py

@@ -26,11 +26,11 @@ petibmpy.write_grid_hdf5(gridpath, name + '-avg', x, y)
 # Get temporal parameters.
 filepath = simudir / 'config.yaml'
 with open(filepath, 'r') as infile:
-    config = yaml.load(infile)['parameters']
+    config = yaml.load(infile, Loader=yaml.FullLoader)['parameters']
 nstart, nt, nsave = config['startStep'], config['nt'], config['nsave']
 dt = config['dt']
-nstart, nt = 100000, 0
 timesteps = list(range(nstart, nstart + nt + 1, nsave))
+timesteps = [80000, 100000]
 
 # Average the scalar field along the z-direction and write field.
 for timestep in timesteps:

### 2019-03-19 examples/snake3d2k35/scripts/plot_force_coefficients_compare_2d.py

@@ -58,5 +58,5 @@ fig.tight_layout()
 # Save figure as PNG file.
 figdir = simudir / 'figures'
 figdir.mkdir(parents=True, exist_ok=True)
-filepath = figdir / 'forceCoefficientsCompare2D.png'
+filepath = figdir / 'forceCoefficientsCompare2D.pdf'
 fig.savefig(str(filepath), dpi=300)

### 2019-03-19 examples/snake3d2k35/scripts/plot_wz_avg_wake2d_pyplot.py

@@ -1,4 +1,4 @@
-"""Plot the 2D vorticity field at different time steps."""
+"""Plot the spanwise-averaged vorticity field at different time steps."""
 
 import pathlib
 import matplotlib
@@ -10,11 +10,11 @@ import yaml
 import petibmpy
 
 
-name = 'wz'  # name of the field variable (z-vorticity)
+name = 'wz-avg'  # name of the field variable
 
 # Get directories.
 rootdir = pathlib.Path(__file__).absolute().parents[1]
-datadir = rootdir / 'output'
+datadir = rootdir / 'output' / 'postprocessing' / 'wz_avg'
 
 # Read the grid.
 gridpath = datadir / 'grid.h5'
@@ -22,9 +22,9 @@ x, y = petibmpy.read_grid_hdf5(gridpath, name)
 X, Y = numpy.meshgrid(x, y)
 
 # Read the body coordinates.
-filepath = datadir / 'snake2d35.body'
+filepath = rootdir / 'snake3d35.body'
 with open(filepath, 'r') as infile:
-    xb, yb = numpy.loadtxt(infile, skiprows=1, unpack=True)
+    xb, yb, _ = numpy.loadtxt(infile, skiprows=1, unpack=True)
 
 # Read the time parameters from YAML configuration file.
 filepath = rootdir / 'config.yaml'
@@ -34,16 +34,18 @@ nstart, nt, nsave = config['startStep'], config['nt'], config['nsave']
 dt = config['dt']
 
 # Select time units to plot.
-times = [20.0, 44.0, 45.0, 80.0]
+times = [80.0, 100.0]
 timesteps = [int(t / dt) for t in times]
 
 # Plot the filled contour of the field variable at selected times.
 pyplot.rc('font', family='serif', size=12)
-fig, ax = pyplot.subplots(nrows=len(times), figsize=(5.0, 8.0), sharex=True)
+fig, ax = pyplot.subplots(nrows=len(times), figsize=(5.0, 5.0), sharex=True)
+if len(times) == 1:
+    ax = [ax]
 levels = numpy.linspace(-5.0, 5.0, num=51)
 for i, (time, timestep) in enumerate(zip(times, timesteps)):
     print('[time step {}]'.format(timestep))
-    filepath = datadir / 'solution' / '{:0>7}.h5'.format(timestep)
+    filepath = datadir / '{:0>7}.h5'.format(timestep)
[…]

### 2019-03-19 tex/MesnardoBarba2019.tex
Use PDF for line figures, PNG for filled contours
Add figure of spanwise-averaged vorticity

@@
     \centering
-    \includegraphics[width=7cm]{figures/osu_latency_bandwidth.png}
+    \includegraphics[width=7cm]{figures/osu_latency_bandwidth.pdf}
     \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One and on NC24r instances of Microsoft Azure.}
@@
     \centering
-    \includegraphics[width=7cm]{figures/poisson_time_vs_nodes.png}
+    \includegraphics[width=7cm]{figures/poisson_time_vs_nodes.pdf}
     \caption{Runtimes to solve a Poisson system on Colonial One and on Microsoft Azure.}
@@
     \includegraphics[width=7cm]{figures/wz_multi_contourf.png}
-    \caption{Filled contour of the vorticity field after $20$, $44$, $45$, and $80$ time units fo flow simulation with PetIBM for the snake cross-section at a $35$-degree angle of attack and Reynolds number $2000$.
+    \caption{Filled contour of the vorticity field after $20$, $44$, $45$, and $80$ time units of flow simulation with PetIBM for the snake cross-section at a $35$-degree angle of attack and Reynolds number $2000$.
 Vortex merging events are responsible for the change in the wake signature and the drop in the mean value of the lift coefficient.}
-    \label{fig:vorticity2d}
+    \label{fig:wz_2d}
 \end{figure}
@@
     \centering
-    \includegraphics[width=7cm]{figures/forceCoefficientsCompare2D.png}
+    \includegraphics[width=7cm]{figures/forceCoefficientsCompare2D.pdf}
     \caption{History of the force coefficients obtained with two- and three-dimensional simulations at Reynolds number $2000$ for a snake cross-section with a $35$-degree angle of attack.}
     \label{fig:force_coefficients}
+\end{figure}
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=7cm]{figures/wz_avg_multi_contourf.png}
+    \caption{Filled contour of the spanwise-averaged z-component of the vorticity field after $80$ and $100$ time units of flow simulation with PetIBM for the snake cylinder with a cross-section at a $35$-degree angle of attack and Reynolds number $2000$.}
+    \label{fig:wz_avg_3d}
 \end{figure}

### 2019-03-20 tex/MesnardoBarba2019.tex
Add notes about workflow and benchmarks et al.
Also:

* Add footnotes about tools (including version and url).
* Span large figures and tables over two columns.

@@
 \ref{fig:cloud_workflow} shows a graphical representation of the workflow we adopted to run CFD simulations with an in-house software on Microsoft Azure.
+We use a Microsoft Azure platform service called Azure Batch to run our in-house CFD software.
+Azure Batch services leverages Microsoft Azure at no extra cost to relieve the user from manually creating, configuring, and managing a HPC-capable cluster of cloud nodes, including virtual machines, virtual networks, job and task scheduling infrastructure.
+Azure Batch works with both embarrassingly parallel workloads and tightly-coupled MPI jobs (the latter being the case of our CFD software).
+To use Azure Batch, the user needs to configure a workspace on Microsoft Azure by creating an Azure Batch account associated to an Azure Storage account (to upload and download simulation data).
+This can be done either via the Azure Portal in a web browser or from a local terminal user the open-source tool Azure CLI.\footnote{Azure CLI (version 2.0.57): \url{https://github.com/Azure/azure-cli}}
 
-\begin{figure}[!ht]
+To create computational nodes and submit container-based jobs to Azure Batch, we use the open-source command-line utility Batch Shipyard.\footnote{Batch Shipyard (version 3.6.1): https://github.com/Azure/batch-shipyard} Batch Shipyard reads user-written YAML configuration files to automatically create pools of compute nodes on Microsoft Azure and to submit jobs to those pools.
+The Docker image of our CFD application is pulled from the (public or private) registry to the virtual machines when the pool is created.
+Once the simulations are done (i.e., the job tasks are complete), we delete the jobs and the pool.
+The output of the computation is now stored on a fileshare in our Azure Storage account and we can download the data to our local machine to perform additional post-processing steps.
+
+Reproducible research requires authors to make their code and data available.
+Thus, the Dockerfile and YAML configuration files should be made part of an extended reproducibility package that includes workflow instructions for cloud computing, in addition to other input files.
+Such reproducibility package facilitates re-creating the cloud environment to run the simulations under the same conditions.
+
+\begin{figure*}[!h]
     \centering
-    \includegraphics[width=7cm]{figures/cloud_workflow.png}
+    \includegraphics[width=14cm]{figures/cloud_workflow.png}
     \caption{Reproducible workflow on the public cloud provider Microsoft Azure.}
     \label{fig:cloud_workflow}
-\end{figure}
+\end{figure*}
 
-\begin{table}[!t]
+\begin{table*}[!h]
     \caption{NC series on Microsoft Azure. (Prices as of May 13, 2018.)}
@@
     \begin{tabular}{cccccccc}
-        Instance & cores & RAM (GiB) & disk sizes (GiB) & GPU & pay-as-you-go (\$/hr) & 1-year reserved (\$/hr) & 3-year reserved (\$/hr) \\
+        Instance & cores & RAM & disk sizes & GPU & pay-as-you-go & 1-year reserved & 3-year reserved \\
+        && (GiB) & (Gib) && (\$/hr) & (\$/hr) & (\$/hr) \\
         \hline
@@
         NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.294 & 1.599 \\
-        NC24r$^\dagger$ & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.523 & 1.758 \\
+        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.523 & 1.758 \\
         \hline
     \end{tabular}
-    $\dagger$ NC24r: RDMA (Remote Direct Access Memory) capable with InfiniBand network.
-\end{table}
+\end{table*}
+
+\footnotetext{NC24r: RDMA (Remote Direct Access Memory) capable with InfiniBand network.}
 
@@
 
+Thanks to a sponsorship ($\$20,000$ worth of cloud credits) from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} we ran three-dimensional CFD simulations of the flow around a gliding-snake model using our in-house research software PetIBM.
+Prior to that, we ran benchmarks to confirm we would get comparable performances between a local university-managed HPC cluster (Colonial One) and a public cloud platform such as Microsoft Azure.
+
 \subsection{MPI Communication Benchmarks}\label{subsec:mpi_benchmarks}
 
-\begin{figure}[!ht]
+We compared the MPI communication performances between Microsoft Azure and Colonial One using the micro-benchmarks from the Ohio State University\footnote{OSU Micro-Benchmarks (version 5.6): \url{http://mvapich.cse.ohio-state.edu/benchmarks/}} to perform point-to-point tests and evaluate the latency and bandwidth on the two clusters.
+On Colonial One, we used two nodes (provide details of CPU) with InfiniBand network.
+On Microsoft Azure, we used two NC24r instances (provide details of CPU) with RMDA over InfiniBand.
+Figure \ref{fig:osu_benchmarks} report the latencies and bandwidths averaged over 5 repetitions.
+
+\begin{figure}[!h]
     \centering
@@
 
-\begin{figure}[!ht]
+We compare the runtimes on the two platforms (Colonial One and Microsoft Azure) to solve a three-dimensional Poisson system (central differences on a uniform mesh) on CPUs and GPUs.
+Figure \ref{fig:poisson_benchmarks} reports the runtimes (averaged over 5 repetitions) to solve the Poisson system.
+On the CPU nodes, we perform strong scaling on a mesh size of $1000 \times 1000 \times 50$ cells using up to 8 nodes to solve the system with PETSc using a Conjugate Gradient method and a classical algebraic multigrid preconditioner from the package Hypre BoomerAMG.
+On the nodes that feature GPU devices, we perform weak scaling starting with a mesh size of $500 \times 500 \times 25$ cells on a single node (using 12 CPU cores and 2 GPU devices); we double the mesh size as we double the number of nodes in the pool.
+We use the NVIDIA AmgX library to solve the system with a Conjugate Gradient method and a classical algebraic multigrid preconditioner.
+As the number of iterations to reach convergence increases with the size of the system, we normalize the runtimes by the number of iterations.
+
+\begin{figure}[!h]
     \centering
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
     \centering
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
     \centering
-    \includegraphics[width=7cm]{figures/forceCoefficientsCompare2D.pdf}
+    \includegraphics[width=8cm]{figures/forceCoefficientsCompare2D.pdf}
     \caption{History of the force coefficients obtained with two- and three-dimensional simulations at Reynolds number $2000$ for a snake cross-section with a $35$-degree angle of attack.}
@@
 
-\begin{table}[!t]
+\begin{table}[!h]
     \caption{Time-averaged force coefficients on the snake cross-section at Reynolds number 1000 and angle of attack $35^o$ for the two- and three-dimensional configurations.

### 2019-03-21 tex/MesnardoBarba2019.tex
Add PetIBM citation et al.
Also:

* Provide contour range in caption.
* Increase width of figures.

@@
 
-\footnotetext{NC24r: RDMA (Remote Direct Access Memory) capable with InfiniBand network.}
+\footnotetext{NC24r instances are RDMA (Remote Direct Access Memory) capable with InfiniBand network.}
 
@@
 
-Thanks to a sponsorship ($\$20,000$ worth of cloud credits) from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} we ran three-dimensional CFD simulations of the flow around a gliding-snake model using our in-house research software PetIBM.
+Thanks to a sponsorship ($\$20,000$ worth of cloud credits) from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} we ran three-dimensional CFD simulations of the flow around a gliding-snake model using our in-house research software PetIBM\cite{chuang_et_al_2018}.
 Prior to that, we ran benchmarks to confirm we would get comparable performances between a local university-managed HPC cluster (Colonial One) and a public cloud platform such as Microsoft Azure.
@@
     \centering
-    \includegraphics[width=7cm]{figures/osu_latency_bandwidth.pdf}
+    \includegraphics[width=8cm]{figures/osu_latency_bandwidth.pdf}
     \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One and on NC24r instances of Microsoft Azure.}
@@
     \centering
-    \includegraphics[width=7cm]{figures/poisson_time_vs_nodes.pdf}
+    \includegraphics[width=8cm]{figures/poisson_time_vs_nodes.pdf}
     \caption{Runtimes to solve a Poisson system on Colonial One and on Microsoft Azure.}
@@
     \centering
-    \includegraphics[width=7cm]{figures/wz_multi_contourf.png}
-    \caption{Filled contour of the vorticity field after $20$, $44$, $45$, and $80$ time units of flow simulation with PetIBM for the snake cross-section at a $35$-degree angle of attack and Reynolds number $2000$.
+    \includegraphics[width=8cm]{figures/wz_multi_contourf.png}
+    \caption{Filled contour of the vorticity field ($-5 \leq w_z c / U_\infty \leq 5$) after $20$, $44$, $45$, and $80$ time units of flow simulation with PetIBM for the snake cross-section at a $35$-degree angle of attack and Reynolds number $2000$.
 Vortex merging events are responsible for the change in the wake signature and the drop in the mean value of the lift coefficient.}
@@
     \centering
-    \includegraphics[width=7cm]{figures/wz_avg_multi_contourf.png}
-    \caption{Filled contour of the spanwise-averaged z-component of the vorticity field after $80$ and $100$ time units of flow simulation with PetIBM for the snake cylinder with a cross-section at a $35$-degree angle of attack and Reynolds number $2000$.}
+    \includegraphics[width=8cm]{figures/wz_avg_multi_contourf.png}
+    \caption{Filled contour of the spanwise-averaged z-component of the vorticity ($-5 \leq w_z c / U_\infty \leq 5$) field after $80$ and $100$ time units of flow simulation with PetIBM for the snake cylinder with a cross-section at a $35$-degree angle of attack and Reynolds number $2000$.}
     \label{fig:wz_avg_3d}
@@
 
+\section{Cost Analysis}\label{sec:cost}
+
 % \section*{Acknowledgment}

### 2019-03-21 tex/clean.sh
Add Bash script to delete LaTeX-generated files

@@ -1,0 +1,8 @@
+#!/usr/bin/env bash
+# Clean LaTeX-generated files.
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+cd $scriptdir
+rm -f *.aux *.blg *.fdb_latexmk *.fls *.log *.synctex.gz
+
+exit 0

### 2019-03-21 examples/poisson/azure/amgx/larger/01_nc24r/run-poisson.sh
Update figure Poisson benchmark
* Re-do y-axis limits.
* Add input files for larger runs on Azure (with AmgX).
* Add new results to plot.
* Update figure in tex folder.

@@ -1,0 +1,56 @@
+#!/usr/bin/env bash
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+simudir=$scriptdir
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=24
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+# get number of GPUs on machine
+ngpusmax=`nvidia-smi -L | wc -l`
+echo "Number of GPU devices available on each node: $ngpusmax"
+# number of GPUs to use per node
+CUDA_VISIBLE_DEVICES=0,1,2,3
+IFS=',' read -ra GPUS <<< "$CUDA_VISIBLE_DEVICES"
+ngpus=${#GPUS[@]}
+echo "Number of GPU devices per node to use: $ngpus ($CUDA_VISIBLE_DEVICES)"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+cd $simudir
+
+cp $AZ_BATCH_TASK_DIR/stdout.txt .
+cp $AZ_BATCH_TASK_DIR/stderr.txt .
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	echo "Run $counter" > stdout_run$counter.txt
+	mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+		poisson \
+		-caseName poisson_amgx_nodes$nodes_run$counter \
+		-mode AmgX_GPU \
+		-cfgFileName config/poisson_solver.info \
+		-Nx 1000 -Ny 500 -Nz 50 \
+		-log_view ascii:view_run$counter.log \
+		-options_left >> stdout_run$counter.txt 2> stderr_run$counter.txt
+	((counter++))
+done
+
+rm -rf data
+
+exit 0

### 2019-03-21 examples/poisson/azure/amgx/larger/01_nc24r/scripts/az-upload-input.sh

@@ -1,0 +1,30 @@
+#!/usr/bin/env zsh
+
+sharename="fileshare"
+dirname="poisson/amgx/001"
+accountname="mesnardostorage"
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+casedir="$( cd "$(dirname "$scriptdir")" ; pwd -P )"
+
+source ~/.zshrc
+
+conda activate py36-az
+
+az storage directory create \
+	--name $dirname \
+	--share-name $sharename \
+	--account-name $accountname
+
+cp -r $casedir/../config $casedir
+
+az storage file upload-batch \
+	--source $casedir \
+	--destination $sharename/$dirname \
+	--account-name $accountname
+
+rm -rf $casedir/config
+
+conda deactivate
+
+exit 0

### 2019-03-21 examples/poisson/azure/amgx/larger/02_nc24r/run-poisson.sh

@@ -1,0 +1,56 @@
+#!/usr/bin/env bash
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+simudir=$scriptdir
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=24
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+# get number of GPUs on machine
+ngpusmax=`nvidia-smi -L | wc -l`
+echo "Number of GPU devices available on each node: $ngpusmax"
+# number of GPUs to use per node
+CUDA_VISIBLE_DEVICES=0,1,2,3
+IFS=',' read -ra GPUS <<< "$CUDA_VISIBLE_DEVICES"
+ngpus=${#GPUS[@]}
+echo "Number of GPU devices per node to use: $ngpus ($CUDA_VISIBLE_DEVICES)"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+cd $simudir
+
+cp $AZ_BATCH_TASK_DIR/stdout.txt .
+cp $AZ_BATCH_TASK_DIR/stderr.txt .
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	echo "Run $counter" > stdout_run$counter.txt
+	mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+		poisson \
+		-caseName poisson_amgx_nodes$nodes_run$counter \
+		-mode AmgX_GPU \
+		-cfgFileName config/poisson_solver.info \
+		-Nx 1000 -Ny 1000 -Nz 50 \
+		-log_view ascii:view_run$counter.log \
+		-options_left >> stdout_run$counter.txt 2> stderr_run$counter.txt
+	((counter++))
+done
+
+rm -rf data
+
+exit 0

### 2019-03-21 examples/poisson/azure/amgx/larger/04_nc24r/run-poisson.sh

@@ -1,0 +1,56 @@
+#!/usr/bin/env bash
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+simudir=$scriptdir
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=24
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+# get number of GPUs on machine
+ngpusmax=`nvidia-smi -L | wc -l`
+echo "Number of GPU devices available on each node: $ngpusmax"
+# number of GPUs to use per node
+CUDA_VISIBLE_DEVICES=0,1,2,3
+IFS=',' read -ra GPUS <<< "$CUDA_VISIBLE_DEVICES"
+ngpus=${#GPUS[@]}
+echo "Number of GPU devices per node to use: $ngpus ($CUDA_VISIBLE_DEVICES)"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+cd $simudir
+
+cp $AZ_BATCH_TASK_DIR/stdout.txt .
+cp $AZ_BATCH_TASK_DIR/stderr.txt .
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	echo "Run $counter" > stdout_run$counter.txt
+	mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+		poisson \
+		-caseName poisson_amgx_nodes$nodes_run$counter \
+		-mode AmgX_GPU \
+		-cfgFileName config/poisson_solver.info \
+		-Nx 1000 -Ny 1000 -Nz 100 \
+		-log_view ascii:view_run$counter.log \
+		-options_left >> stdout_run$counter.txt 2> stderr_run$counter.txt
+	((counter++))
+done
+
+rm -rf data
+
+exit 0

### 2019-03-21 examples/poisson/azure/amgx/larger/08_nc24r/run-poisson.sh

@@ -1,0 +1,56 @@
+#!/usr/bin/env bash
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+simudir=$scriptdir
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=24
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+# get number of GPUs on machine
+ngpusmax=`nvidia-smi -L | wc -l`
+echo "Number of GPU devices available on each node: $ngpusmax"
+# number of GPUs to use per node
+CUDA_VISIBLE_DEVICES=0,1,2,3
+IFS=',' read -ra GPUS <<< "$CUDA_VISIBLE_DEVICES"
+ngpus=${#GPUS[@]}
+echo "Number of GPU devices per node to use: $ngpus ($CUDA_VISIBLE_DEVICES)"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+cd $simudir
+
+cp $AZ_BATCH_TASK_DIR/stdout.txt .
+cp $AZ_BATCH_TASK_DIR/stderr.txt .
+
+niters=5
+counter=1
+
+while [ $counter -le $niters ]
+do
+	echo "Run $counter" > stdout_run$counter.txt
+	mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+		poisson \
+		-caseName poisson_amgx_nodes$nodes_run$counter \
+		-mode AmgX_GPU \
+		-cfgFileName config/poisson_solver.info \
+		-Nx 1000 -Ny 1000 -Nz 200 \
+		-log_view ascii:view_run$counter.log \
+		-options_left >> stdout_run$counter.txt 2> stderr_run$counter.txt
+	((counter++))
+done
+
+rm -rf data
+
+exit 0

### 2019-03-21 examples/poisson/scripts/plot_runtimes.py

@@ -186,6 +186,17 @@ for n in nodes:
     store_runtime_stats(subdata, n, get_runtime_stats(runtimes,
                                                       scale=1.0 / nites))
 data['Azure']['AmgX'] = gather_arrays(subdata)
+# Get runtimes data for AmgX runs on Azure.
+nodes = [1, 2, 4, 8]
+subdata = {'nodes': [], 'min': [], 'max': [], 'means': []}
+for n in nodes:
+    casedir = rootdir / f'azure/amgx/larger/{n:0>2}_nc24r/output'
+    filepaths = get_filepaths(casedir)
+    runtimes = amgxwrapper_poisson_read_runtimes(*filepaths)
+    nites = amgxwrapper_poisson_read_iterations(filepaths[0])
+    store_runtime_stats(subdata, n, get_runtime_stats(runtimes,
+                                                      scale=1.0 / nites))
+data['Azure']['AmgX-larger'] = gather_arrays(subdata)
 
 # Create Matplotlib figures.
 pyplot.rc('font', family='serif', size=14)
@@ -199,16 +210,14 @@ ax1.set_xlabel('Number of nodes')
 ax1.set_ylabel('Time (s)')
 # Colonial One runs.
 nodes, mins, maxs, means = data['Colonial One']['PETSc']
-ax1.plot(numpy.log2(nodes), means, label='Colonial One',
-         color='C0', marker='x', markersize=10)
+ax1.plot(numpy.log2(nodes), means, label='Colonial One', color='C0')
 ax1.errorbar(numpy.log2(nodes), means,
              [means - mins, maxs - means],
              fmt='k', linewidth=0, ecolor='black', elinewidth=2,
              capthick=2, capsize=4, barsabove=True)
 # Azure runs.
 nodes, mins, maxs, means = data['Azure']['PETSc']
-ax1.plot(numpy.log2(nodes), means, label='Azure',
-         color='C1', marker='x', markersize=10)
+ax1.plot(numpy.log2(nodes), means, label='Azure', color='C1')
 ax1.errorbar(numpy.log2(nodes), means,
              [means - mins, maxs - means],
              fmt='k', linewidth=0, ecolor='black', elinewidth=2,
[…]

### 2019-03-22 tex/MesnardoBarba2019.tex
Move table (NC series) to cost section
Add table with hardware specs

@@
 \usepackage{url}
+\usepackage{multirow}
 
@@
 \begin{table*}[!h]
-    \caption{NC series on Microsoft Azure. (Prices as of May 13, 2018.)}
-    \label{tab:nc_series}
+    \renewcommand{\arraystretch}{1.5}
+    \caption{Hardware Specifications of Nodes Used on Microsoft Azure and Colonial One.
+On Both Platforms, MPI Applications Take Advantage of RDMA (Remote Direct Memory Access) Network with FDR InfiniBand.}
+    \label{tab:hw_specs}
     \centering
     \begin{tabular}{cccccccc}
-        Instance & cores & RAM & disk sizes & GPU & pay-as-you-go & 1-year reserved & 3-year reserved \\
-        && (GiB) & (Gib) && (\$/hr) & (\$/hr) & (\$/hr) \\
+        Platform & Node & Intel Xeon CPU & \# threads & NVIDIA GPU & RAM (GiB) & SSD Storage (GiB) \\
         \hline
-        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.574 & 0.40 \\
-        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 1.147 & 0.80 \\
-        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.294 & 1.599 \\
-        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.523 & 1.758 \\
+        \multirow{2}{*}{Azure} & NC24r & Dual 12-Core E5-2690v3 (2.60GHz) & 24 & 4 x K80 & 224 & 1440 \\
+        & H16r & Dual 8-Core E5-2667v3 (3.20GHz) & 16 & - & 112 & 2000 \\
+        \hline
+        \multirow{2}{*}{Colonial One} & Ivygpu & Dual 6-Core E5-2620v2 (2.10GHz) & 12 & 2 x K20 & 120 & 93 \\
+        & Short & Dual 8-Core E5-2650v2 (2.60GHz) & 16 & - & 120 & 93 \\
         \hline
@@
 \end{table*}
-
-\footnotetext{NC24r instances are RDMA (Remote Direct Access Memory) capable with InfiniBand network.}
 
@@
 
+\begin{table*}[!h]
+    \caption{NC series on Microsoft Azure. (Prices as of May 13, 2018.)}
+    \label{tab:nc_series}
+    \centering
+    \begin{tabular}{cccccccc}
+        Instance & cores & RAM & disk sizes & GPU & pay-as-you-go & 1-year reserved & 3-year reserved \\
+        && (GiB) & (Gib) && (\$/hr) & (\$/hr) & (\$/hr) \\
+        \hline
+        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.574 & 0.40 \\
+        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 1.147 & 0.80 \\
+        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.294 & 1.599 \\
+        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.523 & 1.758 \\
+        \hline
+    \end{tabular}
+\end{table*}
+\footnotetext{NC24r instances are RDMA (Remote Direct Access Memory) capable with InfiniBand network.}
+
 % \section*{Acknowledgment}

### 2019-03-22 tex/MesnardoBarba2019.tex
Revise captions of figures for benchmarks
Also:

* Change "Figure" to "Fig.".

@@
 On Microsoft Azure, we used two NC24r instances (provide details of CPU) with RMDA over InfiniBand.
-Figure \ref{fig:osu_benchmarks} report the latencies and bandwidths averaged over 5 repetitions.
+Fig. \ref{fig:osu_benchmarks} report the latencies and bandwidths averaged over 5 repetitions.
 
@@
     \includegraphics[width=8cm]{figures/osu_latency_bandwidth.pdf}
-    \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One and on NC24r instances of Microsoft Azure.}
+    \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One (Ivygpu nodes) and on Microsoft Azure (NC24r nodes).}
     \label{fig:osu_benchmarks}
@@
 We compare the runtimes on the two platforms (Colonial One and Microsoft Azure) to solve a three-dimensional Poisson system (central differences on a uniform mesh) on CPUs and GPUs.
-Figure \ref{fig:poisson_benchmarks} reports the runtimes (averaged over 5 repetitions) to solve the Poisson system.
+Fig. \ref{fig:poisson_benchmarks} reports the runtimes (averaged over 5 repetitions) to solve the Poisson system.
 On the CPU nodes, we perform strong scaling on a mesh size of $1000 \times 1000 \times 50$ cells using up to 8 nodes to solve the system with PETSc using a Conjugate Gradient method and a classical algebraic multigrid preconditioner from the package Hypre BoomerAMG.
@@
     \includegraphics[width=8cm]{figures/poisson_time_vs_nodes.pdf}
-    \caption{Runtimes to solve a Poisson system on Colonial One and on Microsoft Azure.}
+    \caption{Runtimes to solve a Poisson system on Colonial One and on Microsoft Azure.
+Benchmark was repeated 5 times and we report the mean runtimes as well as the extrema.
+Poisson system was solved on Azure using PETSc on H16r nodes and using AmgX on NC24r nodes.
+On Colonial One, we solved the system with PETSc on Short nodes and with AmgX on Ivygpu nodes.
+The runs with PETSc solved a Poisson system on a mesh size of 50 million cells (top).
+With AmgX (bottom left), the base mesh size contains 6.25 million cells and we scale it with the number of nodes.
+On Azure, we also ran the Poisson benchmark with a finer base mesh size of 25 million cells (bottom right).
+Runtimes obtained with AmgX were normalized by the number of iterations required to reach a absolute tolerance of $10^{-12}$.}
     \label{fig:poisson_benchmarks}

### 2019-03-22 examples/poisson/azure/amgx/larger/01_nc24r/scripts/az-upload-input.sh
Change name of conda environment

@@ -1,4 +1,4 @@
-#!/usr/bin/env zsh
+#!/usr/bin/env bash
 
 sharename="fileshare"
 dirname="poisson/amgx/001"
@@ -7,9 +7,9 @@ accountname="mesnardostorage"
 scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
 casedir="$( cd "$(dirname "$scriptdir")" ; pwd -P )"
 
-source ~/.zshrc
+source ~/.bashrc
 
-conda activate py36-az
+conda activate py36-cloud
 
 az storage directory create \
 	--name $dirname \

### 2019-03-22 examples/poisson/azure/petsc/01_h16r/scripts/az-upload-input.sh

@@ -1,4 +1,4 @@
-#!/usr/bin/env zsh
+#!/usr/bin/env bash
 
 sharename="fileshare"
 dirname="poisson/petsc/001"
@@ -7,9 +7,9 @@ accountname="mesnardostorage"
 scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
 casedir="$( cd "$(dirname "$scriptdir")" ; pwd -P )"
 
-source ~/.zshrc
+source ~/.bashrc
 
-conda activate py36-az
+conda activate py36-cloud
 
 az storage directory create \
 	--name $dirname \

### 2019-03-23 tex/MesnardoBarba2019.tex
Add listings of command lines, and others
Also:

* List the different YAML files for Batch Shipyard.
* Add comments of what to include in last sections.

@@
 \usepackage{multirow}
+
+\usepackage{listings}
+\lstset{
+    backgroundcolor=\color{white},
+    basicstyle=\footnotesize,
+    breakatwhitespace=true,
+    breaklines=true,
+    captionpos=b,
+    extendedchars=true,
+    frame=single,
+    keepspaces=true,
+    language=bash,
+    morekeywords={*,...},
+    numbers=none,
+    numbersep=5pt,
+    rulecolor=\color{black},
+    showspaces=false,
+    showstringspaces=false,
+    showtabs=false,
+    stepnumber=2,
+    tabsize=2,
+    title=\lstname,
+}
 
@@
 Once the image is build locally, we push it to a public registry (e.g., DockerHub).
+
+\begin{lstlisting}
+$ cd $CLOUDREPRO/docker/petibm
+$ docker build --tag=barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu --file=Dockerfile .
+$ docker push barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu
+\end{lstlisting}
+
 Everyone can now pull the application image and create a container to run the application in a faithfully reproduced local environment.
@@
 
+\begin{lstlisting}
+$ az account set --subscription reprosubscription
+$ az group create --name reprorg --location eastus
+$ az storage account create --name reprostorage --resource-group reprorg --sku Standard_LRS --location eastus
+$ az batch account create --name reprobatch --resource-group reprorg --location eastus --storage-account reprostorage
+$ az storage share create --name fileshare --account-name reprostorage --account-key storagekey --quota 100
+\end{lstlisting}
+
 To create computational nodes and submit container-based jobs to Azure Batch, we use the open-source command-line utility Batch Shipyard.\footnote{Batch Shipyard (version 3.6.1): https://github.com/Azure/batch-shipyard} Batch Shipyard reads user-written YAML configuration files to automatically create pools of compute nodes on Microsoft Azure and to submit jobs to those pools.
+
+\begin{itemize}
+    \item \texttt{config.yaml} contains information about the Azure Storage account and Docker images to use.
+    \item \texttt{credentials.yaml} stores the necessary credentials to use the different Microsoft Azure service platforms (e.g., Azure Batch and Azure Storage).
+    \item \texttt{pool.yaml} is where the user configures the pool of virtual machines to create.
+    \item \texttt{jobs.yaml} details the configuration of the jobs to submit to the pool.
+\end{itemize}
+
 The Docker image of our CFD application is pulled from the (public or private) registry to the virtual machines when the pool is created.
+
+\begin{lstlisting}
+$ cd $CLOUDREPRO/examples/snake2d2k35
+$ az storage directory create --name snake2d2k35 --share-name fileshare --account-name reprostorage
+$ export SHIPYARD_CONFIGDIR=config_shipyard
+$ shipyard pool add
+$ shipyard data ingress
+$ shipyard jobs add
+\end{lstlisting}
+
 Once the simulations are done (i.e., the job tasks are complete), we delete the jobs and the pool.
 The output of the computation is now stored on a fileshare in our Azure Storage account and we can download the data to our local machine to perform additional post-processing steps.
+
+\begin{lstlisting}
+$ shipyard pool del
+$ mkdir output
+$ az storage file download-batch --source fileshare/snake2d2k25 --destination output --account-name reprostorage
+\end{lstlisting}
 
@@
 
-\section{Cost Analysis}\label{sec:cost}
+\section{Cost Analysis and Lessons Learned}\label{sec:cost}
+
+% Mention the 7-day limitation for jobs with Azure Batch.
+% Mention that Batch Shipyard can pull images from public and private registries.
+% Mention that Singularity containers are also supported in Batch Shipyard.
 

### 2019-03-23 tex/MesnardoBarba2019.tex
Revise benchmarks subsections, and others
* Give more details about the OSU Micro-Benchmarks used.
* Add more details about the Poisson tests.

Also:

* Add paragraph on PetIBM.

@@
 
+\section{Results}\label{sec:results}
+
+Thanks to a sponsorship ($\$20,000$ worth of cloud credits) from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} three-dimensional CFD simulations with our in-house research software ran on the public cloud platform using the reproducible workflow described in Section \ref{sec:workflow}.
+Preliminary results from benchmarks and test-cases showed that we are able to obtain similar performance in terms of latency and bandwidth using the Azure virtual network, comparing to a traditional University-managed HPC cluster (Colonial One).
+Table \ref{tab:hw_specs} reports the hardware specifications of the nodes used on Microsoft Azure and Colonial One.
+
 \begin{table*}[!h]
@@
         \hline
-        \multirow{2}{*}{Azure} & NC24r & Dual 12-Core E5-2690v3 (2.60GHz) & 24 & 4 x K80 & 224 & 1440 \\
-        & H16r & Dual 8-Core E5-2667v3 (3.20GHz) & 16 & - & 112 & 2000 \\
+        \multirow{2}{*}{Azure} & \texttt{NC24r} & Dual 12-Core E5-2690v3 (2.60GHz) & 24 & 4 x K80 & 224 & 1440 \\
+        & \texttt{H16r} & Dual 8-Core E5-2667v3 (3.20GHz) & 16 & - & 112 & 2000 \\
         \hline
-        \multirow{2}{*}{Colonial One} & Ivygpu & Dual 6-Core E5-2620v2 (2.10GHz) & 12 & 2 x K20 & 120 & 93 \\
-        & Short & Dual 8-Core E5-2650v2 (2.60GHz) & 16 & - & 120 & 93 \\
+        \multirow{2}{*}{Colonial One} & \texttt{Ivygpu} & Dual 6-Core E5-2620v2 (2.10GHz) & 12 & 2 x K20 & 120 & 93 \\
+        & \texttt{Short} & Dual 8-Core E5-2650v2 (2.60GHz) & 16 & - & 120 & 93 \\
         \hline
@@
 
-\section{Results}\label{sec:results}
-
-Thanks to a sponsorship ($\$20,000$ worth of cloud credits) from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} we ran three-dimensional CFD simulations of the flow around a gliding-snake model using our in-house research software PetIBM\cite{chuang_et_al_2018}.
-Prior to that, we ran benchmarks to confirm we would get comparable performances between a local university-managed HPC cluster (Colonial One) and a public cloud platform such as Microsoft Azure.
-
 \subsection{MPI Communication Benchmarks}\label{subsec:mpi_benchmarks}
 
-We compared the MPI communication performances between Microsoft Azure and Colonial One using the micro-benchmarks from the Ohio State University\footnote{OSU Micro-Benchmarks (version 5.6): \url{http://mvapich.cse.ohio-state.edu/benchmarks/}} to perform point-to-point tests and evaluate the latency and bandwidth on the two clusters.
-On Colonial One, we used two nodes (provide details of CPU) with InfiniBand network.
-On Microsoft Azure, we used two NC24r instances (provide details of CPU) with RMDA over InfiniBand.
-Fig. \ref{fig:osu_benchmarks} report the latencies and bandwidths averaged over 5 repetitions.
+Point-to-point MPI benchmarks from the Ohio State University Micro-Benchmarks\footnote{OSU Micro-Benchmarks (version 5.6): \url{http://mvapich.cse.ohio-state.edu/benchmarks/}} suite ran on Microsoft Azure and Colonial One to investigate performance in terms the latency and bandwidth.
+The latency test is carried out in a ping-pong fashion and measures the time elapsed to get a response; the sender sends a message with a certain data size and wait for the receiver to send back the message with the same data size.
+The bandwidth test measures the maximum sustained rate that can be achieved on the network; it consists in having the sender sends a fixed number of messages to a receiver that replies only after receiving all of them.
+The tests ran on \texttt{NC24r} nodes on Azure and \texttt{Ivygpu} nodes on Colonial One, all them featuring a network interface for RDMA (Remote Direct Memory Access) connectivity to communicate over an InfiniBand network.
+Fig. \ref{fig:osu_benchmarks} reports the mean latencies and bandwidths obtained over $5$ repetitions on both platforms.
 
@@
     \includegraphics[width=8cm]{figures/osu_latency_bandwidth.pdf}
-    \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One (Ivygpu nodes) and on Microsoft Azure (NC24r nodes).}
+    \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One (\texttt{Ivygpu} nodes) and on Microsoft Azure (\texttt{NC24r} nodes).
+Benchmark results are averaged over $5$ repetitions.}
     \label{fig:osu_benchmarks}
@@
 
-We compare the runtimes on the two platforms (Colonial One and Microsoft Azure) to solve a three-dimensional Poisson system (central differences on a uniform mesh) on CPUs and GPUs.
-Fig. \ref{fig:poisson_benchmarks} reports the runtimes (averaged over 5 repetitions) to solve the Poisson system.
-On the CPU nodes, we perform strong scaling on a mesh size of $1000 \times 1000 \times 50$ cells using up to 8 nodes to solve the system with PETSc using a Conjugate Gradient method and a classical algebraic multigrid preconditioner from the package Hypre BoomerAMG.
-On the nodes that feature GPU devices, we perform weak scaling starting with a mesh size of $500 \times 500 \times 25$ cells on a single node (using 12 CPU cores and 2 GPU devices); we double the mesh size as we double the number of nodes in the pool.
-We use the NVIDIA AmgX library to solve the system with a Conjugate Gradient method and a classical algebraic multigrid preconditioner.
+CFD algorithms often require to solve linear systems with iterative methods.
+For example, the project method implemented in our research software solve a Poisson system every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
+Thus, we investigated the time-to-solution to solve a three-dimensional Poisson system (obtained with a 7-point stencil using central differences) on different nodes of Microsoft Azure and Colonial One.
+The system was solved using a Conjugate-Gradient (CG) method with a classical Algebraic MultiGrid (AMG) preconditioner with an exit criterion set to an absolute tolerance of $10^{-12}$.
+The iterative solver ran on CPU nodes (\texttt{H16r} instances on Azure and \texttt{Short} nodes on Colonial One) using the CG algorithm from the PETSc library and an AMG preconditioner from Hypre BoomerAMG.
+Fig.
+\ref{fig:poisson_benchmarks} (top) reports the mean runtimes (averaged over $5$ repetitions) to iteratively solve the system, on a uniform grid of $50$ million cells ($1000 \times 1000 \times 50$), as we increase the number of nodes in the pool.
+We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
+The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) is solved on a single node using $12$ MPI processes and $2$ GPU devices; we then double the mesh size as we double the number of nodes.
 As the number of iterations to reach convergence increases with the size of the system, we normalize the runtimes by the number of iterations.
+Fig. \ref{fig:poisson_benchmarks} (bottom left) shows the normalized mean runtimes ($5$ repetitions) obtained on Azure and Colonial One.
+The bottom-right panel of the figure reports the normalized mean runtimes obtained on Azure when we put more constraint on the bandwidth; the base mesh now contains $25$ millions cells ($1000 \times 500 \times 50$).
 
@@
 Benchmark was repeated 5 times and we report the mean runtimes as well as the extrema.
-Poisson system was solved on Azure using PETSc on H16r nodes and using AmgX on NC24r nodes.
-On Colonial One, we solved the system with PETSc on Short nodes and with AmgX on Ivygpu nodes.
+Poisson system was solved on Azure using PETSc on \texttt{H16r} nodes and using AmgX on \texttt{NC24r} nodes.
+On Colonial One, we solved the system with PETSc on \texttt{Short} nodes and with AmgX on \texttt{Ivygpu} nodes.
 The runs with PETSc solved a Poisson system on a mesh size of 50 million cells (top).
@@
 The so-called flying snake jumps from tree branches, undulates in the air, and is able to produce lift by expanding its ribcage to flatten its ventral surface (morphing its normally circular cross-section into a triangular shape).
+
+To study the flow around the flying snake, we develop a in-house CFD software called PetIBM\cite{chuang_et_al_2018}, a open-source toolbox that solves the two- and three-dimensional incompressible Navier-Stokes equations using a projection method (an approximate block-LU decomposition of the fully discretized equations\cite{perot_1993}) and an Immersed-Boundary Method (IBM).
+Within this framework, the fluid equations are solved on a extended grid that does not conform to the surface of the immersed body.
+To model the presence of the body, the momentum equation is augmented with a forcing term that is activated in the vicinity of the immersed boundary.
+This technique allows the use of simple fixed structured Cartesian grids to solve the equations.
+PetIBM also implements Immersed Boundary Methods (IBMs) that fit into the projection method and, in the present study, we use an implementation of the IBM proposed in \cite{li_et_al_2016}.
+To obtain reproducible computational results, the code used to run the simulations needs to be made available.
+In that regard, PetIBM is open source, version-controlled on GitHub,\footnote{PetIBM (version 0.4): \url{https://github.com/barbagroup/PetIBM}} and developed under the permissive BSD-3 clause license.
 

### 2019-03-23 tex/MesnardoBarba2019.tex
Add sentences in intro about terminologies

@@
 \IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
+
+Reproducible research and replication studies are essential components for the progress of evidence-based science, even more since science today advances via computation.
+More than ever we use computer simulations to create new knowledge.
+But how do we certify that this new knowledge is justified, that there is enough evidence to support it?
+With constant increase in the rate of submissions to journals as well as software and data getting more complex, it becomes difficult to verify and corroborate what computational scientists present in journal and conferences \cite{donoho_et_al_2009}.
+
+The literature is often swamped with confused, and sometimes contradictory, meanings for reproducible research, reproducibility, replicability, repetition, and so on \cite{barba_2018}.
+It is thus worth clarifying these terms.
+The term ``reproducible research'' in reference to computational studies that can be reproduced by other scientists was introduced by geophysics professor Jon Claerbout in the 1990s.
+He and his research group at Stanford created a reproducible-research environment\cite{schwab_et_al_2000} in which, the goal was complete documentation of scientific computations, in such way that a reader could reproduce all the results and figures in a paper using the author-provided computer programs and raw data.
+This ability requires open data and open source software and, for this reason, the reproducibility movement is closely linked with the open science movement.
+In subsequent years, the term ``replication'' was distinctly adopted to refer to an independent study that rerun experiments to generate new data which, when analyzed, lead to the same findings.
+We follow this convention, clarified more recently in a report from the National Academies of Sciences, Engineering, and Medicine.
 

### 2019-03-23 examples/snake3d2k35/scripts/plot_ux_uy_xz_plane.py
Add script to plot velocity components in xz plane and the figure as a PNG

@@ -1,0 +1,92 @@
+"""Plot the streamwise and cross-flow velocity components.
+
+Plot the filled contours of the streamwise and cross-flow velocity components
+at time-step 100000 (100 time units) in the x/z plane at y=-0.2.
+"""
+
+from matplotlib import pyplot, patches
+import numpy
+import pathlib
+import yaml
+
+import petibmpy
+
+
+def interp_xzplane(y, u, y_target=0.0):
+    """Perform linear interpolation of the 3D data at given y-location.
+
+    Parameters
+    ----------
+    y : numpy.ndarray of floats
+        The y-coordinates along a vertical gridline as a 1D array.
+    u : numpy.ndarray of floats
+        The 3D data.
+    y_target : float (optional)
+        The y-coordinate at which to interpolate the data.
+
+    Returns
+    -------
+    u_target : numpy.ndarray of floats
+        The 2D interpolated data.
+
+    """
+    idx = numpy.where(y >= y_target)[0][0]
+    y0, y1 = y[idx - 1], y[idx]
+    u0, u1 = u[:, idx - 1, :], u[:, idx, :]
+    u_target = u0 + (y_target - y0) * (u1 - u0) / (y1 - y0)
+    return u_target
+
+
+# Get simulation directory and data directory.
+simudir = pathlib.Path(__file__).absolute().parents[1]
+datadir = simudir / 'output'
+
+# Read the body file to add body location on the axes.
+filepath = simudir / 'data' / 'snake2d.body'
+with open(filepath, 'r') as infile:
+    xb, _ = numpy.loadtxt(infile, skiprows=1, unpack=True)
+xb_min, xb_max = numpy.min(xb), numpy.max(xb)
+
+# Plot the filled contours of the velocity components in the x/z plane.
+timestep = 100000  # time-step index
+y_target = -0.2  # y-location where to interpolate
+names = ['u', 'v']  # name of the velocity components to plot
+pyplot.rc ('font', family='serif', size=16)
+fig, ax = pyplot.subplots(figsize=(8.0, 4.0), nrows=len(names), sharex=True)
+for i, name in enumerate(names):
+    # Read the grid coordinates on which the velocity is located.
+    gridpath = simudir / 'output' / 'grid.h5'
+    x, y, z = petibmpy.read_grid_hdf5(gridpath, name)
+    x_min, x_max = numpy.min(x), numpy.max(x)
[…]

### 2019-03-23 examples/snake3d2k35/scripts/plot_qcrit_wx_wake3d_visit.py
Add script to plot isosurfaces of Q-criterion with VisIt
* Save figure as PNG.

@@ -1,0 +1,30 @@
+"""Plot the isosurfaces of the Q-criterion at save time steps.
+
+The isosurfaces are colored with the streamwise vorticity.
+"""
+
+import numpy
+import os
+import pathlib
+import sys
+
+scriptdir = pathlib.Path(__file__).absolute().parents[3] / 'misc'
+if scriptdir not in sys.path:
+    sys.path.insert(0, str(scriptdir))
+from visitplot import *
+
+
+simudir = pathlib.Path(__file__).absolute().parents[1]
+xdmfdir = simudir / 'output'
+config_view = simudir / 'scripts' / 'visit_view3d.yaml'
+figdir = simudir / 'figures'
+prefix = 'qcrit_wx_wake3d_'
+
+visit_plot_qcrit_wx_3d(xdmfdir,
+                       wx_range=(-5.0, 5.0),
+                       q_value=1.0,
+                       config_view=config_view,
+                       out_dir=figdir, out_prefix=prefix,
+                       figsize=(880, 372),
+                       visit_dir=os.environ.get('VISIT_DIR'),
+                       states=[1])

### 2019-03-23 misc/visitplot.py

@@ -141,7 +141,7 @@ def visit_plot_pseudocolor_2d(xdmf_path, name,
         visit.SaveWindow()
 
     os.remove('visitlog.py')
-    sys.exit(0)
+    visit.Close()
     return
 
 
@@ -274,5 +274,183 @@ def visit_plot_contour_3d(xdmf_path, name,
         visit.SaveWindow()
 
     os.remove('visitlog.py')
-    sys.exit(0)
+    visit.Close()
+    return
+
+
+def visit_plot_qcrit_wx_3d(xdmf_dir,
+                           wx_range=(-5.0, 5.0),
+                           q_value=0.1,
+                           config_view=None,
+                           out_dir=os.getcwd(), out_prefix='wake3d_',
+                           figsize=(1024, 1024),
+                           visit_dir=None, visit_arch='linux-x86_64',
+                           state=None, states=None,
+                           states_range=[0, None, 1]):
+    # Import VisIt package.
+    if visit_dir is None:
+        visit_dir = os.environ.get('VISIT_DIR')
+        if visit_dir is None:
+            raise ValueError('Provide VisIt installation path or '
+                             'set env variable VISIT_DIR')
+    sys.path.append(os.path.join(visit_dir, visit_arch,
+                    'lib', 'site-packages'))
+    import visit
+
+    visit.LaunchNowin()
+
+    # Check version of VisIt.
+    visit_check_version(visit.Version())
+
+    # Define some variables to get the q_crit and wx_cc.
+    p_xdmf_path = os.path.join(str(xdmf_dir), 'p.xmf')
+    visit.OpenDatabase(p_xdmf_path, 0)
+    visit.DefineScalarExpression("operators/ConnectedComponents/p Grid", "cell_constant(<p Grid>, 0.)")
+    visit.DefineCurveExpression("operators/DataBinning/1D/p Grid", "cell_constant(<p Grid>, 0)")
+    visit.DefineScalarExpression("operators/DataBinning/2D/p Grid", "cell_constant(<p Grid>, 0)")
+    visit.DefineScalarExpression("operators/DataBinning/3D/p Grid", "cell_constant(<p Grid>, 0)")
+    visit.DefineScalarExpression("operators/Flux/p Grid", "cell_constant(<p Grid>, 0.)")
[…]

### 2019-03-23 tex/MesnardoBarba2019.tex
Add 3D snake figures to manuscript

@@
 
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=8cm]{figures/ux_uy_xz_plane.png}
+    \caption{Filled contour of the streamwise velocity (top) and cross-flow velocity (bottom) behind the snake cylinder in the $x/z$ plane at $y/c=-0.2$ in the wake of the snake cylinder with a $35$-degree angle of attack at Reynolds number $2000$ after $100$ time-units of flow simulations.
+There are 52 contours from $-1.0$ to $1.0$.
+The grey area shows a projection of the snake cylinder in the $x/z$ plane.
+The solid black line defines the contour with $u_x = 0$ (top) and $u_y = 0$ (bottom).}
+    \label{fig:ux_uy_xz_plane_3d}
+\end{figure}
+
+\begin{figure*}[!h]
+    \centering
+    \includegraphics[width=16cm]{figures/qcrit_wx_wake3d_0001.png}
+    \caption{Lateral view of the isosurfaces of the Q-criterion ($Q = 1.0$) in the wake of the snake cylinder (with a $35$-degree angle of attack) at Reynolds number $2000$.
+The isosurfaces are colored with the streamwise vorticity ($-5 \leq w_x c / U_\infty \leq 5$).}
+    \label{fig:qcrit_wx_3d}
+\end{figure*}
+
 \section{Cost Analysis and Lessons Learned}\label{sec:cost}

### 2019-03-25 tex/MesnardoBarba2019.tex
Add description of the snake simulations

@@
 The system was solved using a Conjugate-Gradient (CG) method with a classical Algebraic MultiGrid (AMG) preconditioner with an exit criterion set to an absolute tolerance of $10^{-12}$.
-The iterative solver ran on CPU nodes (\texttt{H16r} instances on Azure and \texttt{Short} nodes on Colonial One) using the CG algorithm from the PETSc library and an AMG preconditioner from Hypre BoomerAMG.
+The iterative solver ran on CPU nodes (\texttt{H16r} instances on Azure and \texttt{Short} nodes on Colonial One) using the CG algorithm from the PETSc library\cite{balay_et_al_2018} and an AMG preconditioner from Hypre BoomerAMG.
 Fig.
@@
 PetIBM also implements Immersed Boundary Methods (IBMs) that fit into the projection method and, in the present study, we use an implementation of the IBM proposed in \cite{li_et_al_2016}.
+PetIBM runs on distributed-memory architectures and relies on the efficient data structures and parallel routines of the PETSc library.
+The software also implements the possibility to solve linear systems on multiple GPU devices distributed across the nodes with the NVIDIA AmgX and AmgXWrapper\cite{chuang_barba_2017}.
 To obtain reproducible computational results, the code used to run the simulations needs to be made available.
 In that regard, PetIBM is open source, version-controlled on GitHub,\footnote{PetIBM (version 0.4): \url{https://github.com/barbagroup/PetIBM}} and developed under the permissive BSD-3 clause license.
+
+\subsubsection{2D Flow Around a Snake Cross-Section}
+
+With Batch Shipyard, we submitted a job on Azure Batch to compute the two-dimensional flow around an anatomically accurate sectional shape of the gliding snake.
+The cross-section has a chord-length of $1$ and forms a $35$-degree angle of attack with the incoming freestream flow.
+The Reynolds number, based on the freestream speed, the body chord-length, the kinematic viscosity, is set to $Re=2000$.
+The immersed boundary is centered in a $30c \times 30c$ computational domain that contains just above $2.9$ million cells.
+The grid is kept uniform with the highest resolution in the vicinity of the body and stretched to the external boundaries with a constant ratio (see Table \ref{tab:grid_specs} for details about the grid).
+(The immersed boundary is discretized with the same resolution than the background fluid grid.)
+A convective condition was used at the outlet boundary while freestream conditions were enforced on the others.
+The job was submitted to a pool of two \texttt{NC24r} nodes, with $12$ MPI processes and $2$ GPU devices per node.
+The task completed $200,000$ time steps (i.e., $80$ time units of flow simulation with a time-step size $\Delta t = 0.0004 c / U_\infty$) in just above $7$ hours.
+
+Fig. \ref{fig:force_coefficients} shows the history of the force coefficients on the two-dimensional cross-section.
+The lift coefficient only maintains its maximum mean value during the early stage of the simulation (up to $40$ time units).
+Between $40$ and $50$ time units, the mean value starts to drop.
+The time-averaged force coefficients (between $40$ and $80$ time units) are reported in Table \ref{tab:force_coefficients}.
+Fig. \ref{fig:wz_2d} shows snapshots of the vorticity field after $20$, $44$, $45$, and $80$ time unit of flow simulation.
+After $20$ time units, the vortices shed from the snake section are almost aligned in the near wake (with a slight deflection towards the lower part of the domain).
+Snapshots of the vorticity at time units $44$ and $45$ show that the initial alignment is perturbed by vortex-merging events (same-sign vortices merging together to form a stronger one).
+Following that, the wake signature is altered for the rest of the simulation: vortices are not aligned anymore, the wake becomes wider (leading to lower aerodynamic forces) with a 1S+1P vortex signature (a single clockwise-rotating vortex on the upper part and a vortex pair on the lower part).
 
@@
 
+\subsubsection{3D Flow Around a Snake Cylinder}
+
+Although the two-dimensional simulations gave us some insights into to flow dynamics happening in the behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional will develop in the wake.
+Thus, we submitted jobs to Azure Batch to compute the three-dimensional flow around a cylinder with the same anatomically accurate cross-section.
+The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
+The grid is kept uniform in the $z$-direction and we enforce periodic conditions at the front and back boundaries.
+The simulation ran in a Docker container on Azure Batch using Batch Shipyard.
+The job was submitted to a pool of two \texttt{NC24r} nodes using $24$ MPI processes and $4$ GPU devices per node.
+The task completed $100,000$ time steps ($100$ time units with a time-step size $\Delta t = 0.01 c / U_\infty$) in about $5$ days and $16$ hours.
+
+Fig. \ref{fig:force_coefficients} compares the history of the force coefficients between the two- and three-dimensional configurations.
+The force coefficients resulting from the two-dimensional simulation of the snake are higher than those obtained for the snake cylinder; a relative difference of $+37.9\%$ and $+14.4\%$ for the time-averaged drag and lift coefficient, respectively (see Table \ref{tab:force_coefficients}).
+Two-dimensional computational simulations of fundamentally three-dimensional flows lead to incorrect estimation of the force coefficients\cite{mittal_balachandar_1995}.
+
+Fig. \ref{fig:wz_avg_3d} shows the instantaneous spanwise vorticity averaged along the $z$-direction after $80$ and $100$ time units.
+Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von Karman street exhibits a narrower wake.
+We note the presence of a recirculation region behind the snake cylinder and the deformation of the von Karman street as the spanwise vortices are convected away from the body (Fig.
+\ref{fig:ux_uy_xz_plane_3d}).
+Fig. \ref{fig:qcrit_wx_3d} shows the isosurfaces of the Q-criterion after $100$ time units and highlights the complexity of the three-dimensional wake generated by the snake model.
+
 \begin{figure}[!h]
@@
 
+\begin{table*}[!h]
+    \renewcommand{\arraystretch}{1.5}
+    \caption{Details about the computational grids used for the snake simulations with PetIBM.}
+    \label{tab:grid_specs}
+    \centering
+        \begin{tabular}{clllll}
+        Case & Domain & Uniform region & Smallest cell-width & Stretching ratio & Size \\
+        \hline
+        2D & $30 \times 30$ & $\left[ -0.52, 3.48 \right] \times \left[ -2, 2 \right]$ & $0.004 \times 0.004$ & $1.01$ & $1704 \times 1706$ \\
+        3D & $30c \times 30c \times 3.2c$ & $\left[ -0.52, 3.48 \right] \times \left[ -2, 2 \right] \times \left[ 0, 3.2 \right]$ & $0.008 \times 0.008 \times 0.08$ & $1.01$ & $1071 \times 1072 \times 40$ \\
+        \hline
+    \end{tabular}
+\end{table*}
+
+\begin{table}[!h]
+    \renewcommand{\arraystretch}{1.5}
+    \caption{Time-averaged force coefficients on the snake model at Reynolds number $2000$ and angle of attack $35^o$ for the two- and three-dimensional configurations.
+(We average the force coefficients between $40$ and $80$ time units of flow simulation and report the relatively difference of the 2D values with respect to the 3D ones.)}
+    \label{tab:force_coefficients}
+    \centering
+    \begin{tabular}{cll}
+        Case & $<C_D>$ & $<C_L>$ \\
+        \hline
+        3D & $0.8390$ & $1.5972$ \\
+        2D & $1.1567$ ($+37.9\%$) & $1.8279$ ($+14.4\%$) \\
+        \hline
+    \end{tabular}
+\end{table}
+
 \begin{figure}[!h]
@@
 \end{figure}
-
-\begin{table}[!h]
-    \caption{Time-averaged force coefficients on the snake cross-section at Reynolds number 1000 and angle of attack $35^o$ for the two- and three-dimensional configurations.
-(We average the force coefficients between $40$ and $80$ time units of flow simulation.)}
-    \label{tab:force_coefficients}
-    \centering
-    \begin{tabular}{ccll}
-        \hline
-        Case & Mesh size & $<C_D>$ & $<C_L>$ \\
-        \hline
-        3D & $1071 \times 1072 \times 40$ & $0.8390$ & $1.5972$ \\
-        2D & $1704 \times 1706$ & $1.1567$ ($+37.9\%$) & $1.8279$ ($+14.4\%$) \\
-        \hline
-    \end{tabular}
-\end{table}
 
@@
 \begin{table*}[!h]
+    \renewcommand{\arraystretch}{1.5}
     \caption{NC series on Microsoft Azure. (Prices as of May 13, 2018.)}

### 2019-03-25 tex/MesnardoBarba2019.tex
Add sentences about the cost

@@
 Although the two-dimensional simulations gave us some insights into to flow dynamics happening in the behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional will develop in the wake.
-Thus, we submitted jobs to Azure Batch to compute the three-dimensional flow around a cylinder with the same anatomically accurate cross-section.
+Thus, we submitted jobs to Azure Batch to perform direct numerical simulation of the three-dimensional flow around a cylinder with the same anatomically accurate cross-section.
 The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
@@
 
-% Mention the 7-day limitation for jobs with Azure Batch.
+% Mention the 7-day limitation for jobs with Azure Batch. (WARNING: according to the Batch Shipyard documentation, tasks can have a maximum lifetime of 180 days.)
 % Mention that Batch Shipyard can pull images from public and private registries.
@@
 
+For the year $2018$, Microsoft Azure granted our research lab a sponsorship of $20,000$ USD in cloud credits to run CFD simulations with our in-house software.
+From May to December, we spend a total of $20,614$ USD to run simulations of the gliding snake.
+During that period, we have been charged data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
+More than $99\%$ of the charges are due the usage of virtual machines.
+We had the opportunity to use different instances on Microsoft Azure and most the charges for the usage of virtual machines of the \texttt{NC24r} instance (used for the two- and three-dimensional simulations of the flying snake).
+The \texttt{NC24r} instance is part of the NC-series (Table \ref{tab:nc_series}); we copiously used as it enables RDMA capabilities for our MPI application and features NVIDIA K80 GPU devices.
+For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
+The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).
+
+\begin{table}
+    \renewcommand{\arraystretch}{1.5}
+    \caption{Charges incurred for the usage of different services on Microsoft Azure.}
+    \label{tab:azure_charges}
+    \centering
+    \begin{tabular}{cll}
+        Service name & Cost (USD) & \% of total cost \\
+        \hline
+        Bandwidth & $46.85$ & $0.23$ \\
+        Data Management & $0.56$ & $0.003$ \\
+        Networking & $1.38$ & $0.007$ \\
+        Storage & $25.93$ & $0.16$ \\
+        Virtual Machines & $20,582.64$& $99.6$ \\
+        \hline
+        Total & $20,614$ & \\
+        \hline
+    \end{tabular}
+\end{table}
+
 \begin{table*}[!h]
     \renewcommand{\arraystretch}{1.5}
-    \caption{NC series on Microsoft Azure. (Prices as of May 13, 2018.)}
+    \caption{NC series on Microsoft Azure. (Prices as of March 24, 2019, for CentOS or Ubuntu Linux Virtual Machines in the East US region.)}
     \label{tab:nc_series}
@@
         \hline
-        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.574 & 0.40 \\
-        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 1.147 & 0.80 \\
-        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.294 & 1.599 \\
-        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.523 & 1.758 \\
+        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.5733 & 0.3996 \\
+        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 1.1466 & 0.7991 \\
+        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.2932 & 1.5981 \\
+        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.5224 & 1.7578 \\
         \hline
@@
 \end{table*}
-\footnotetext{NC24r instances are RDMA (Remote Direct Access Memory) capable with InfiniBand network.}
+\footnotetext{The NC24r configuration provides a low latency, high throughput network interface optimized for tightly coupled parallel applications.}
+
+In a new effort to make our research transparent and reproducible by others, we have version-controlled all the input files, pre- and post-processing scripts, as well as the Batch Shipyard configuration files required to rerun the simulations on Microsoft Azure.
+In addition, all the scripts to reproduce the figures in the present article are made available.
+The reproducibility packages are hosted on GitHub in the repository \texttt{cloud-repro}.\footnote{\url{https://github.com/barbagroup/cloud-repro}}
 

### 2019-03-25 tex/MesnardoBarba2019.tex
Add paragraph on University cluster, and others
Also:

* Add some sentences on user experiences with Microsoft Azure (learning curve, helper tools, Intel MPI, visible costs, quotas).

@@
 We follow this convention, clarified more recently in a report from the National Academies of Sciences, Engineering, and Medicine.
+
+Universities and national laboratories can spend millions of dollars to deploy and maintain on-site high-performance computing (HPC) clusters.
+At the George Washington University, we have access to a university-managed HPC cluster called Colonial One.
+The cluster is now $6$ years old and approaching its end-of-life.
+On average, its computational resources are idle $9\%$ of the time and unavailable to users for roughly 5 days a year (due to maintenance).
+Administrators of the cluster are now considering integrating cloud-computing platforms in the landscape of HPC at the George Washington University.
+Over the past decade, cloud-computing platforms have rapidly evolved, now proposing solutions for scientific applications.
+From a user's point of view, a cloud platform offers great flexibility (hardware and virtual machines) with instantaneous availability of infinite (in appearance) computational resources.
+No more waiting time in job-submission queues!
+This promises to greatly facilitate code development, debugging, and testing. Resources allocated on the cloud are released as soon as the job is done, avoiding paying for idle time.
+On a public-cloud platform such as Microsoft Azure, with a "pay-as-you-go" type of subscription, a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters.
 
@@
 For the year $2018$, Microsoft Azure granted our research lab a sponsorship of $20,000$ USD in cloud credits to run CFD simulations with our in-house software.
+We a ``pay-as-you-go'' type of subscription, users can directly sees how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
 From May to December, we spend a total of $20,614$ USD to run simulations of the gliding snake.
@@
 
-In a new effort to make our research transparent and reproducible by others, we have version-controlled all the input files, pre- and post-processing scripts, as well as the Batch Shipyard configuration files required to rerun the simulations on Microsoft Azure.
+Running CFD simulations on Microsoft Azure was a first time for our research lab.
+As novices in cloud computing, it took us several months to become familiar with the technical vocabulary and the infrastructure of Microsoft Azure before we could submit our first simulation of the snake.
+
+Command-line tools such as Azure-CLI and Batch Shipyard were greatly helpful to create and submit everything from our local terminal.
+(In our research lab, we tend to avoid, as much as possible, interacting with graphical-user interfaces, so as to make our workflow more reproducible.)
+Azure-CLI helped us to setup the Azure Batch account and its associated Azure Storage, as well as uploading/downloading our simulation data.
+With Batch Shipyard, users do not need to have experience with the Azure Batch SDK.
+We have used Batch Shipyard to submit jobs on Azure Batch to run Docker container-based multi-tasks.
+Note that Batch Shipyard also support Singularity containers.
+
+Our in-house CFD research software makes use of the MPI library to run applications on distributed-memory architectures.
+We used Azure instances that feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over an InfiniBand network.
+As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.
+
+Moreover, Microsoft Azure implements quotas, such as the maximum number of cores that can be used in a certain region.
+To run our simulations, we had to open online customer support requests every time we wanted to increase our core quota for a subscription, with a certain service in certain region with a certain type of instances.
+We had to go through this process at least five times during our sponsorship period.
+
+In a new effort to make our research transparent and reproducible by others, we have version-controlled all the input files, pre- and post-processing scripts, as well as the Batch Shipyard configuration files and instructions required to rerun the simulations on Microsoft Azure.
 In addition, all the scripts to reproduce the figures in the present article are made available.

### 2019-03-25 tex/MesnardoBarba2019.tex
Add words about the three-dimensional wake

@@
 Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von Karman street exhibits a narrower wake.
-We note the presence of a recirculation region behind the snake cylinder and the deformation of the von Karman street as the spanwise vortices are convected away from the body (Fig.
+We note the presence of an unsteady recirculation region just behind the snake cylinder and alternating regions of positive and negative cross-flow velocity showing the presence of von Karman vortices (Fig.
 \ref{fig:ux_uy_xz_plane_3d}).
-Fig. \ref{fig:qcrit_wx_3d} shows the isosurfaces of the Q-criterion after $100$ time units and highlights the complexity of the three-dimensional wake generated by the snake model.
+Fig. \ref{fig:qcrit_wx_3d} shows the isosurfaces of the Q-criterion after $100$ time units and highlights the complexity of the three-dimensional turbulent wake generated by the snake model.
 

### 2019-03-25 tex/MesnardoBarba2019.tex
Cite NASA OSS report

@@
     extendedchars=true,
-    frame=single,
+    frame=none,
     keepspaces=true,
@@
 In subsequent years, the term ``replication'' was distinctly adopted to refer to an independent study that rerun experiments to generate new data which, when analyzed, lead to the same findings.
-We follow this convention, clarified more recently in a report from the National Academies of Sciences, Engineering, and Medicine.
+We follow this convention, clarified more recently in a report from the National Academies of Sciences, Engineering, and Medicine \cite{nap_oss_2018}.
 
@@
 Once the image is build locally, we push it to a public registry (e.g., DockerHub).
+
+\clearpage
 

### 2019-03-25 tex/MesnardoBarba2019.tex
Add VisIt citation to manuscript

@@
 In subsequent years, the term ``replication'' was distinctly adopted to refer to an independent study that rerun experiments to generate new data which, when analyzed, lead to the same findings.
-We follow this convention, clarified more recently in a report from the National Academies of Sciences, Engineering, and Medicine \cite{nap_oss_2018}.
+We follow this convention, clarified more recently in a report from the National Academies of Sciences, Engineering, and Medicine \cite{nasa_oss_2018}.
 
@@
     \caption{Lateral view of the isosurfaces of the Q-criterion ($Q = 1.0$) in the wake of the snake cylinder (with a $35$-degree angle of attack) at Reynolds number $2000$.
-The isosurfaces are colored with the streamwise vorticity ($-5 \leq w_x c / U_\infty \leq 5$).}
+The isosurfaces are colored with the streamwise vorticity ($-5 \leq w_x c / U_\infty \leq 5$).
+The figure was generated using the visualization software VisIt \cite{childs_et_al_2012}.}
     \label{fig:qcrit_wx_3d}

### 2019-03-25 tex/MesnardoBarba2019.tex
Modify listings style
* Remove listings caption.
* Use mono-spaced font for listings.
* Add more space above and below listings.

@@
 \lstset{
+    aboveskip=20pt,
+    belowskip=20pt,
+    lineskip=5pt,
     backgroundcolor=\color{white},
-    basicstyle=\footnotesize,
+    basicstyle=\footnotesize\ttfamily,
     breakatwhitespace=true,
     breaklines=true,
-    captionpos=b,
+    captionpos=none,
     extendedchars=true,
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[float]
 $ cd $CLOUDREPRO/docker/petibm

### 2019-03-26 tex/MesnardoBarba2019.tex
edit introduction

@@
 \begin{abstract}
-In a new effort to make our research transparent and reproducible by others, we have developed a workflow to run computational studies on a public cloud.
+In a new effort to make our research transparent and reproducible by others, we developed a workflow to run computational studies on a public cloud.
 It uses Docker containers to create an image of the application software stack.
@@
 
-Reproducible research and replication studies are essential components for the progress of evidence-based science, even more since science today advances via computation.
-More than ever we use computer simulations to create new knowledge.
-But how do we certify that this new knowledge is justified, that there is enough evidence to support it?
-With constant increase in the rate of submissions to journals as well as software and data getting more complex, it becomes difficult to verify and corroborate what computational scientists present in journal and conferences \cite{donoho_et_al_2009}.
+Reproducible research and replication studies are essential components for the progress of evidence-based science, even more now when nearly all fields advance via computation.
+We use computer simulations and data models to create new knowledge,
+but how do we provide evidence that this new knowledge is justified? 
+Traditional journal publications exclude software and data products from the peer-review process, yet reliance on ever more complex computational artifacts and methods is the norm.
+Lacking standards for documenting, reporting and reviewing the computational facets of research, it becomes difficult to verify and corroborate the findings presented in journals and conferences \cite{donoho_et_al_2009}.
 
-The literature is often swamped with confused, and sometimes contradictory, meanings for reproducible research, reproducibility, replicability, repetition, and so on \cite{barba_2018}.
-It is thus worth clarifying these terms.
-The term ``reproducible research'' in reference to computational studies that can be reproduced by other scientists was introduced by geophysics professor Jon Claerbout in the 1990s.
-He and his research group at Stanford created a reproducible-research environment\cite{schwab_et_al_2000} in which, the goal was complete documentation of scientific computations, in such way that a reader could reproduce all the results and figures in a paper using the author-provided computer programs and raw data.
-This ability requires open data and open source software and, for this reason, the reproducibility movement is closely linked with the open science movement.
-In subsequent years, the term ``replication'' was distinctly adopted to refer to an independent study that rerun experiments to generate new data which, when analyzed, lead to the same findings.
-We follow this convention, clarified more recently in a report from the National Academies of Sciences, Engineering, and Medicine \cite{nasa_oss_2018}.
+The literature is cluttered with confused and sometimes contradictory definitions for reproducible research, reproducibility, replicability, repetition, and so on \cite{barba_2018}.
+It is thus worth clarifying how we use these terms.
+``Reproducible research'' was introduced by geophysics professor Jon Claerbout in the 1990s to mean computational studies that can be reproduced by other scientists.
+He and his research group at Stanford created a reproducible-research environment\cite{schwab_et_al_2000} whose goal was complete documentation of scientific computations, in such a way that a reader could reproduce all the results and figures in a paper using the author-provided computer programs and raw data.
+This requires open data and open source software and, for this reason, the reproducibility movement is closely linked with the open science movement.
+The term ``replication'' has been adopted to refer to an independent study generating new data which, when analyzed, lead to the same findings \cite{peng_2011}.
+We follow this convention, adopted also recently in a report from the National Academies of Sciences, Engineering, and Medicine \cite{nasa_oss_2018}.
 
-Universities and national laboratories can spend millions of dollars to deploy and maintain on-site high-performance computing (HPC) clusters.
+Universities and national laboratories spend millions of dollars to deploy and maintain on-site high-performance computing (HPC) clusters.
 At the George Washington University, we have access to a university-managed HPC cluster called Colonial One.
@@
 On average, its computational resources are idle $9\%$ of the time and unavailable to users for roughly 5 days a year (due to maintenance).
-Administrators of the cluster are now considering integrating cloud-computing platforms in the landscape of HPC at the George Washington University.
-Over the past decade, cloud-computing platforms have rapidly evolved, now proposing solutions for scientific applications.
+Administrators of the cluster have been recently considering integrating cloud-computing platforms in the research-computing portfolio. 
+Over the past decade, cloud-computing platforms have rapidly evolved, now offering solutions for scientific applications.
 From a user's point of view, a cloud platform offers great flexibility (hardware and virtual machines) with instantaneous availability of infinite (in appearance) computational resources.
@@
 This promises to greatly facilitate code development, debugging, and testing. Resources allocated on the cloud are released as soon as the job is done, avoiding paying for idle time.
-On a public-cloud platform such as Microsoft Azure, with a "pay-as-you-go" type of subscription, a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters.
+On a public-cloud platform with a "pay-as-you-go" type of subscription---such as Microsoft Azure, Google Cloud, Amazon AWS---a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters.
+Cost models that make sense for researchers, labs, and universities are still unclear. 
+Yet, this information is key when making a decision to adopt a cloud workflow for research. 
+We report here what we have learned from nearly two years of using cloud computing for our simulation-based workflow, with the hope that it will shed some light on the costs and benefits, and help others considering using cloud computing for their research
 

### 2019-03-26 tex/MesnardoBarba2019.tex
add connecting paragraph in intro

@@
 
-The literature is cluttered with confused and sometimes contradictory definitions for reproducible research, reproducibility, replicability, repetition, and so on \cite{barba_2018}.
+The literature is cluttered with confused and sometimes contradictory definitions for reproducible research, reproducibility, replicability, repetition, etc.\cite{barba_2018}.
 It is thus worth clarifying how we use these terms.
-``Reproducible research'' was introduced by geophysics professor Jon Claerbout in the 1990s to mean computational studies that can be reproduced by other scientists.
-He and his research group at Stanford created a reproducible-research environment\cite{schwab_et_al_2000} whose goal was complete documentation of scientific computations, in such a way that a reader could reproduce all the results and figures in a paper using the author-provided computer programs and raw data.
+``Reproducible research'' was used by geophysics professor Jon Claerbout in the 1990s to mean computational studies that can be reproduced by other scientists.
+His research group at Stanford created a reproducible-research environment\cite{schwab_et_al_2000} whose goal was complete documentation of scientific computations, in such a way that a reader could reproduce all the results and figures in a paper using the author-provided computer programs and raw data.
 This requires open data and open source software and, for this reason, the reproducibility movement is closely linked with the open science movement.
@@
 We follow this convention, adopted also recently in a report from the National Academies of Sciences, Engineering, and Medicine \cite{nasa_oss_2018}.
+
+Many efforts to develop cyberinfrastructure that supports reproducible research have been launched in past years. 
+They address concerns like automatic capture of changes to software (version control systems), persistent data archival, global registration of data identifiers, workflow management, and more. 
+But capturing the whole computational environment used in a research project remains one of the most difficult problems. 
+Computational researchers often use a multi-layer stack of software applications that can be laborious to build from scratch. 
+Container technology like Docker is a recent addition to the reproducibility toolbox \cite{boettiger_2015}. 
+In this work, we develop and assess a workflow for reproducible research on a public cloud, adopting Docker containers and several other tools to automate and fully document scientific computations.
 
@@
 Once the image is build locally, we push it to a public registry (e.g., DockerHub).
-
-\clearpage
 

### 2019-03-26 tex/MesnardoBarba2019.tex
Remove listings language

@@
     keepspaces=true,
-    language=bash,
     morekeywords={*,...},
@@
 
-\begin{lstlisting}[float]
+\begin{lstlisting}
 $ cd $CLOUDREPRO/docker/petibm

### 2019-03-26 tex/MesnardoBarba2019.tex
add intro to Results section

@@
 Yet, this information is key when making a decision to adopt a cloud workflow for research. 
-We report here what we have learned from nearly two years of using cloud computing for our simulation-based workflow, with the hope that it will shed some light on the costs and benefits, and help others considering using cloud computing for their research
+We report here what we have learned from nearly two years of using cloud computing for our simulation-based workflow, with the hope that it will shed some light on the costs and benefits, and help others considering using cloud computing for their research.
 
-\section{Reproducible Workflow}\label{sec:workflow}
+\section{Reproducible cloud-based workflow}\label{sec:workflow}
 
-CFD publications often lack details about external libraries used along with the main computational code.
+Scientific publications reporting computational results often lack sufficient details to reproduce the researcher's computational environment; e.g., they may miss to mention external libraries used along with the main computational code.
 We have learned the hard way how different versions of the same external library can alter the numerical results and even the scientific findings of a computational study\cite{mesnard_barba_2017}.
@@
 
-Thanks to a sponsorship ($\$20,000$ worth of cloud credits) from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} three-dimensional CFD simulations with our in-house research software ran on the public cloud platform using the reproducible workflow described in Section \ref{sec:workflow}.
-Preliminary results from benchmarks and test-cases showed that we are able to obtain similar performance in terms of latency and bandwidth using the Azure virtual network, comparing to a traditional University-managed HPC cluster (Colonial One).
-Table \ref{tab:hw_specs} reports the hardware specifications of the nodes used on Microsoft Azure and Colonial One.
+The top concerns of researchers considering cloud computing are performance and cost. 
+Until just a few years ago, the products offered by cloud providers were unsuitable to the needs of computational scientists using HPC, due to performance overhead of virtualization and lack of support for fast networking.
+Azure only introduced nodes with GPU devices and Infiniband support in 2017. 
+Our first objective was to assess performance on cloud nodes for the type of computations in our research workflows with  tightly coupled parallel applications. 
+We present results from benchmarks and test-cases showing that we are able to obtain similar performance in terms of latency and bandwidth using the Azure virtual network, comparing to a traditional university-managed HPC cluster (Colonial One).
+Table \ref{tab:hw_specs} lists the hardware specifications of the nodes used on Microsoft Azure and Colonial One.
+ Our target research application relies on three-dimensional CFD simulations with our in-house research software.
+We include here a sample of the types of results needed to answer our research question, obtained by running on the public cloud using the reproducible workflow described in Section \ref{sec:workflow}.
+ The goal is to showcase the potential of cloud computing for CFD, share the lessons we learned in the process, as well as analyze the cost scenarios for full applications.
 
-\begin{table*}[!h]
+\begin{table*}[b]
     \renewcommand{\arraystretch}{1.5}
@@
 
-% \section*{Acknowledgment}
+ \section*{Acknowledgment}
+
+This study was possible thanks to a sponsorship ($\$20,000$ worth of cloud credits) from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}}.
 

### 2019-03-27 docker/prepost/shipyard-install.sh
Add Dockerfile to build image for post-processing
Also includes a bash script to install Batch Shipyard (3.6.1) within a conda environment.
The bash script is copied to the container upon building the image.

The Docker image has been pushed to the `barbagroup/cloud-repro` repository
on DockerHub (`docker pull barbagroup/cloud-repro:latest`).

@@ -1,0 +1,60 @@
+#!/usr/bin/env bash
+# Installs Batch Shipyard within conda environment.
+# Creates a symbolink link in $HOME/.local/bin.
+# CLI: ./shipyard-install.sh <path to Batch Shipyard directory>
+
+pkgdir="/opt/batch-shipyard/3.6.1"
+envname="py36-cloud"
+condadir="/opt/miniconda3"
+
+source $condadir/bin/activate base
+
+cd $pkgdir
+
+cat > get_shipyard_version.py <<- EOM
+from convoy import version
+
+if __name__ == "__main__":
+    print(version.__version__)
+EOM
+
+version=$((python get_shipyard_version.py) 2>&1)
+rm -f get_shipyard_version.py
+
+bindir="$HOME/.local/bin"
+mkdir -p $bindir
+execname="shipyard${version//./}"
+
+
+conda activate $envname
+pip install --upgrade setuptools
+pip install --upgrade -r requirements.txt
+pip install --upgrade --no-deps -r req_nodeps.txt
+conda deactivate
+
+cat > $bindir/$execname <<- EOM
+#!/usr/bin/env bash
+
+source $condadir/bin/activate base
+
+set -e
+set -f
+
+BATCH_SHIPYARD_ROOT_DIR=$pkgdir
+
+if [ -z \$BATCH_SHIPYARD_ROOT_DIR ]; then
+    echo Batch Shipyard root directory not set.
+    echo Please rerun the install.sh script.
+    exit 1
+fi
+
+conda activate $envname
+python3 \$BATCH_SHIPYARD_ROOT_DIR/shipyard.py \$*
+conda deactivate
+EOM
+
+chmod +x $bindir/$execname
+rm -f $bindir/shipyard
+ln -s $bindir/$execname $bindir/shipyard
+
+exit 0

### 2019-03-28 tex/MesnardoBarba2019.tex
First attempt at revising workflow section

@@
     breaklines=true,
-    captionpos=none,
+    captionpos=b,
     extendedchars=true,
@@
 Once the image is build locally, we push it to a public registry (e.g., DockerHub).
+Listing \ref{lst:docker_build_push} provides the command lines to build (\texttt{docker build}) and push (\texttt{docker push}) an image of our CFD software (\texttt{barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu}) that has been used to run some of the examples presented in this article.
+(Here, \texttt{CLOUDREPRO} is an environment variable set to path of the GitHub repository \texttt{cloud-repro}\footnote{cloud-repro: \url{https://github.com/barbargroup/cloud-repro}} cloned on a local machine.)
 
-\begin{lstlisting}
+\begin{lstlisting}[label=lst:docker_build_push,caption={Build and push a Docker image.}]
 $ cd $CLOUDREPRO/docker/petibm
@@
 
-Everyone can now pull the application image and create a container to run the application in a faithfully reproduced local environment.
+Everyone can now pull the application image and create a Docker container to run the CFD simulation in a faithfully reproduced local environment.
 We aim to move the final stage of this workflow (creating a container) to a public cloud provider such as Microsoft Azure.
+\ref{fig:cloud_workflow} shows a graphical representation of the workflow we adopted to run CFD simulations with an in-house software on Microsoft Azure.
 
 To run computational jobs on Microsoft Azure, we use several tools that facilitate creating and managing virtual machines with compute nodes and submitting jobs to those nodes.
-\ref{fig:cloud_workflow} shows a graphical representation of the workflow we adopted to run CFD simulations with an in-house software on Microsoft Azure.
 We use a Microsoft Azure platform service called Azure Batch to run our in-house CFD software.
@@
 Azure Batch works with both embarrassingly parallel workloads and tightly-coupled MPI jobs (the latter being the case of our CFD software).
-To use Azure Batch, the user needs to configure a workspace on Microsoft Azure by creating an Azure Batch account associated to an Azure Storage account (to upload and download simulation data).
+To use Azure Batch, we need to configure a workspace on Microsoft Azure.
 This can be done either via the Azure Portal in a web browser or from a local terminal user the open-source tool Azure CLI.\footnote{Azure CLI (version 2.0.57): \url{https://github.com/Azure/azure-cli}}
+We prefer to the use command-line solution (program \texttt{az}) as it allows us to keep track of the steps done to configure the Azure workspace (Listing \ref{lst:az_configure}).
+First, we set the subscription we want to use (let's call it \texttt{reprosubscription}).
+We then create a resource group, \texttt{reprorg}, located in the East US region that will contain all the Azure resources.
+We create an Azure Storage account, \texttt{reprostorage}, in the resource group.
+We also need to create an Azure Batch account, \texttt{reprobatch}, and associate it to the storage account.
+Finally, we create a fileshare (of size $100$ Gb) in the storage.
 
-\begin{lstlisting}
+\begin{lstlisting}[label=lst:az_configure,caption={Configure the workspace on Microsoft Azure.}]
 $ az account set --subscription reprosubscription
@@
 
-To create computational nodes and submit container-based jobs to Azure Batch, we use the open-source command-line utility Batch Shipyard.\footnote{Batch Shipyard (version 3.6.1): https://github.com/Azure/batch-shipyard} Batch Shipyard reads user-written YAML configuration files to automatically create pools of compute nodes on Microsoft Azure and to submit jobs to those pools.
+To create computational nodes and submit container-based jobs to Azure Batch, we use the open-source command-line utility Batch Shipyard.\footnote{Batch Shipyard (version 3.6.1): https://github.com/Azure/batch-shipyard}
+Batch Shipyard is entirely driven with configuration files: the utility parses user-written YAML file to automatically create pools of compute nodes on Azure Batch and to submit jobs to those pools.
+Typically, we need to provide four configuration files:
 
@@
 
-The Docker image of our CFD application is pulled from the (public or private) registry to the virtual machines when the pool is created.
+Once the configuration files are written, we invoke Batch Shipyard through the \texttt{shipyard} program on our local machine.
+The folder \texttt{examples/snake2d2k35/config\_shipyard} contains an example YAML files to create a pool of two compute \texttt{NC24r} nodes (that features k80 GPUs and InfiniBand network).
+Listing \ref{lst:shipyard_run} shows the commands to run from your local terminal to create a pool of compute nodes on Azure Batch and submit jobs to it.
+During the pool creation (\texttt{shipyard pool add}), the Docker image of our CFD application is pulled from the registry to the virtual machines.
+With \texttt{shipyard data ingress}, we can upload input files to the compute nodes.
+Once created, we submit jobs to the pool (\texttt{shipyard jobs add}); the tasks for a job will start automatically.
 
-\begin{lstlisting}
+\begin{lstlisting}[label=lst:shipyard_run,caption={Create a pool with Batch Shipyard and submit jobs to it.}]
 $ cd $CLOUDREPRO/examples/snake2d2k35
@@
 
-Once the simulations are done (i.e., the job tasks are complete), we delete the jobs and the pool.
-The output of the computation is now stored on a fileshare in our Azure Storage account and we can download the data to our local machine to perform additional post-processing steps.
+Once the simulations are done (i.e., the job tasks are complete), we delete the jobs and the pool (Listing \ref{lst:shipyard_del}).
+The output of the computation is now stored in the fileshare in our Azure Storage account.
+We can download the data to our local machine to perform additional post-processing steps.
 
-\begin{lstlisting}
+\begin{lstlisting}[label=lst:shipyard_del,caption={Delete the pool and jobs, and download to output to a local machine.}]
 $ shipyard pool del
+$ shipyard jobs del
 $ mkdir output
@@
 Such reproducibility package facilitates re-creating the cloud environment to run the simulations under the same conditions.
+The reproducibility packages of the examples showcased in the next section are available in the GitHub repository \texttt{cloud-repro}, which includes instructions on how to reproduce the results.
 
@@
     \includegraphics[width=14cm]{figures/cloud_workflow.png}
-    \caption{Reproducible workflow on the public cloud provider Microsoft Azure.}
+    \caption{Reproducible workflow on the public cloud provider Microsoft Azure.
+Our CFD software is version-controlled with Git and GitHub.
+We push to DockerHub a Docker image of our CFD application with all its dependencies.
+Azure-CLI is use to configure accounts on Microsof Azure and to upload/download data to/from an Azure Storage account.
+With Batch Shipyard, we can create pool on Azure Batch and run container-based simulation using our Docker image.}
     \label{fig:cloud_workflow}

### 2019-03-30 examples/poisson/azure/amgx/01_nc24r/scripts/az-upload-input.sh
Add README files for Poisson benchmarks
Also:

* Remove unused Shell scripts (command-line instructions are now in the README).
* Do not use sub-folders on Azure File Share (e.g., `poisson/amgx/001` -> `poisson_amgx_001`).

@@ -1,30 +1,0 @@
-#!/usr/bin/env bash
-
-sharename="fileshare"
-dirname="poisson/amgx/001"
-accountname="mesnardostorage"
-
-scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
-casedir="$( cd "$(dirname "$scriptdir")" ; pwd -P )"
-
-source ~/.bashrc
-
-conda activate py36-cloud
-
-az storage directory create \
-	--name $dirname \
-	--share-name $sharename \
-	--account-name $accountname
-
-cp -r $casedir/../config $casedir
-
-az storage file upload-batch \
-	--source $casedir \
-	--destination $sharename/$dirname \
-	--account-name $accountname
-
-rm -rf $casedir/config
-
-conda deactivate
-
-exit 0

### 2019-03-30 examples/poisson/azure/petsc/01_h16r/scripts/az-upload-input.sh

@@ -1,30 +1,0 @@
-#!/usr/bin/env bash
-
-sharename="fileshare"
-dirname="poisson/petsc/001"
-accountname="mesnardostorage"
-
-scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
-casedir="$( cd "$(dirname "$scriptdir")" ; pwd -P )"
-
-source ~/.bashrc
-
-conda activate py36-cloud
-
-az storage directory create \
-	--name $dirname \
-	--share-name $sharename \
-	--account-name $accountname
-
-cp -r $casedir/../config $casedir
-
-az storage file upload-batch \
-	--source $casedir \
-	--destination $sharename/$dirname \
-	--account-name $accountname
-
-rm -rf $casedir/config
-
-conda deactivate
-
-exit 0

### 2019-03-30 misc/visitplot.py
Set the pyyaml Loader argument to FullLoader

@@ -84,7 +84,8 @@ def visit_plot_pseudocolor_2d(xdmf_path, name,
     # Parse the 2D view configuration file.
     if config_view is not None:
         with open(str(config_view), 'r') as infile:
-            config_view = yaml.load(infile)['View2DAtts']
+            config_view = yaml.load(infile, Loader=yaml.FullLoader)
+            config_view = config_view['View2DAtts']
     # Set attributes of the view.
     View2DAtts = visit.View2DAttributes()
     for key, value in config_view.items():
@@ -214,7 +215,8 @@ def visit_plot_contour_3d(xdmf_path, name,
     # Parse the 3D view configuration file.
     if config_view is not None:
         with open(str(config_view), 'r') as infile:
-            config_view = yaml.load(infile)['View3DAtts']
+            config_view = yaml.load(infile, Loader=yaml.FullLoader)
+            config_view = config_view['View3DAtts']
     # Set attributes of the view.
     View3DAtts = visit.View3DAttributes()
     for key, value in config_view.items():
@@ -400,7 +402,8 @@ def visit_plot_qcrit_wx_3d(xdmf_dir,
     # Parse the 3D view configuration file.
     if config_view is not None:
         with open(str(config_view), 'r') as infile:
-            config_view = yaml.load(infile, Loader=yaml.FullLoader)['View3DAtts']
+            config_view = yaml.load(infile, Loader=yaml.FullLoader)
+            config_view = config_view['View3DAtts']
     # Set attributes of the view.
     View3DAtts = visit.View3DAttributes()
     for key, value in config_view.items():

### 2019-03-30 examples/snake3d2k35/scripts/plot_wz_avg_wake2d_pyplot.py
Do not display Matplotlib figure

@@ -62,5 +62,3 @@ figdir = rootdir / 'figures'
 figdir.mkdir(parents=True, exist_ok=True)
 filepath = figdir / 'wz_avg_multi_contourf.png'
 fig.savefig(str(filepath), dpi=300, bbox_inches='tight')
-
-pyplot.show()

### 2019-03-30 examples/snake3d2k35/scripts/plot_qcrit_wx_wake3d_visit.py
Use correct state for filename with VisIt
Also:

* Rename figure with Q-criterion with correct state.
* Update list of figures to rsync for manuscript.
* Update list of tested versions of VisIt.

@@ -27,4 +27,4 @@ visit_plot_qcrit_wx_3d(xdmfdir,
                        out_dir=figdir, out_prefix=prefix,
                        figsize=(880, 372),
                        visit_dir=os.environ.get('VISIT_DIR'),
-                       states=[1])
+                       state=20)

### 2019-03-30 misc/visitplot.py

@@ -8,7 +8,7 @@ import yaml
 def visit_check_version(version):
     # Check version of VisIt.
     script_version = '2.12.1'
-    tested_versions = [script_version, '2.13.2']
+    tested_versions = [script_version, '2.12.3']
     print('VisIt version: {}\n'.format(version))
     if version not in tested_versions:
         print('[warning] You are using VisIt-{}.'.format(version))
@@ -100,7 +100,6 @@ def visit_plot_pseudocolor_2d(xdmf_path, name,
     AnnotationAtts.timeInfoFlag = 1
     visit.SetAnnotationAttributes(AnnotationAtts)
 
-    visit.DrawPlots()
     visit.SetActiveWindow(1)
 
     visit.Source(os.path.join(visit_dir, visit_arch, 'bin', 'makemovie.py'))
@@ -120,9 +119,12 @@ def visit_plot_pseudocolor_2d(xdmf_path, name,
             states_range[1] += 1
         states = range(*states_range)
 
-    for state in states:
+    for i, state in enumerate(states):
         print('[state {}] Rendering and saving figure ...'.format(state))
         visit.SetTimeSliderState(state)
+
+        if i == 0:
+            visit.DrawPlots()
 
         RenderingAtts = visit.RenderingAttributes()
         visit.SetRenderingAttributes(RenderingAtts)
@@ -234,7 +236,6 @@ def visit_plot_contour_3d(xdmf_path, name,
     AnnotationAtts.axes3D.bboxFlag = 0
     visit.SetAnnotationAttributes(AnnotationAtts)
 
-    visit.DrawPlots()
     visit.SetActiveWindow(1)
 
     visit.Source(os.path.join(visit_dir, visit_arch, 'bin', 'makemovie.py'))
@@ -254,9 +255,12 @@ def visit_plot_contour_3d(xdmf_path, name,
             states_range[1] += 1
         states = range(*states_range)
 
-    for state in states:
+    for i, state in enumerate(states):
         print('[state {}] Rendering and saving figure ...'.format(state))
         visit.SetTimeSliderState(state)
+
+        if i == 0:
+            visit.DrawPlots()
 
         RenderingAtts = visit.RenderingAttributes()
         visit.SetRenderingAttributes(RenderingAtts)
@@ -412,7 +416,6 @@ def visit_plot_qcrit_wx_3d(xdmf_dir,
         setattr(View3DAtts, key, value)
     visit.SetView3D(View3DAtts)
 
[…]

### 2019-04-01 tex/MesnardoBarba2019.tex
Use correct state for filename with VisIt
Also:

* Rename figure with Q-criterion with correct state.
* Update list of figures to rsync for manuscript.
* Update list of tested versions of VisIt.
Update figure with repro workflow
* Add box about pool creation.
* Add colors.
* Add Keynote file with figure (figure is exported to PNG file).
Add note about Dockerfiles in reproducibility statement

@@
     \centering
-    \includegraphics[width=14cm]{figures/cloud_workflow.png}
+    \includegraphics[width=16cm]{figures/cloud_workflow.png}
     \caption{Reproducible workflow on the public cloud provider Microsoft Azure.
@@
     \centering
-    \includegraphics[width=16cm]{figures/qcrit_wx_wake3d_0001.png}
+    \includegraphics[width=16cm]{figures/qcrit_wx_wake3d_0020.png}
     \caption{Lateral view of the isosurfaces of the Q-criterion ($Q = 1.0$) in the wake of the snake cylinder (with a $35$-degree angle of attack) at Reynolds number $2000$.
@@
 
-In a new effort to make our research transparent and reproducible by others, we have version-controlled all the input files, pre- and post-processing scripts, as well as the Batch Shipyard configuration files and instructions required to rerun the simulations on Microsoft Azure.
+In a new effort to make our research transparent and reproducible by others, we have version-controlled all the input files, pre- and post-processing scripts, as well as the Dockerfiles (used to create the Docker images), the Batch Shipyard configuration files, and command-line instructions required to rerun the simulations on Microsoft Azure.
 In addition, all the scripts to reproduce the figures in the present article are made available.

### 2019-04-02 tex/MesnardoBarba2019.tex
Add sentences about container technology

@@
 We have learned the hard way how different versions of the same external library can alter the numerical results and even the scientific findings of a computational study\cite{mesnard_barba_2017}.
-To overcome the so-called ``dependency hell'' and facilitate reproducibility, we use Docker to locally create an image of our computational application.
-Container technology facilitates share build images of the full software stack that is used to produce scientific results.
-The process of building an image using Docker begins with writing an ASCII file, called a Dockerfile, that contains Docker keywords and system commands for building multi-layered software stack.
-Once the image is build locally, we push it to a public registry (e.g., DockerHub).
-Listing \ref{lst:docker_build_push} provides the command lines to build (\texttt{docker build}) and push (\texttt{docker push}) an image of our CFD software (\texttt{barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu}) that has been used to run some of the examples presented in this article.
+To overcome the so-called ``dependency hell'' and facilitate reproducibility and portability, we use the container technology provided by the open-source project Docker.
+
+A container represents an isolated user space where application programs run directly on the operating system's kernel (with a limited access to its resources).
+As opposed to Virtual Machines, containers do not include a full operating system, making them lighter and faster.
+Containers allows to re-create the same runtime environment of the applications (that includes all its dependencies) from one machine to another.
+A container is an instance of an image.
+The developer builds the image on a local machine and pushes it to a public registry to make it available to users.
+(Users pull down the image and create containers out of it.)
+To create a Docker image, the developer writes a \texttt{Dockerfile}.
+The \texttt{Dockerfile} is an ASCII file that contains keywords to tell Docker what to do.
+We create a new image from a base image using the keyword \texttt{FROM}.
+We then write the different commands to build a multi-layered runtime environment of the application that includes all its dependencies.
+Once we have built the image on the local machine, we push it to a repository on the DockerHub registry, a place to store and retrieve Docker images.
+Listing \ref{lst:docker_build_push} provides the command lines to build (\texttt{docker build}) and push (\texttt{docker push}) an image of our CFD software (\texttt{barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu}) that we used to run some of the examples presented in the next section.
 (Here, \texttt{CLOUDREPRO} is an environment variable set to path of the GitHub repository \texttt{cloud-repro}\footnote{cloud-repro: \url{https://github.com/barbargroup/cloud-repro}} cloned on a local machine.)
@@
 Everyone can now pull the application image and create a Docker container to run the CFD simulation in a faithfully reproduced local environment.
-We aim to move the final stage of this workflow (creating a container) to a public cloud provider such as Microsoft Azure.
+The great advantage of container technology is that the same container that was built and tested on a local machine by a developer can now run at scaled in production mode on Virtual Machines, bare metal, or even cloud platforms.
+Our objective is to create and run containers on a public cloud provider such as Microsoft Azure.
 \ref{fig:cloud_workflow} shows a graphical representation of the workflow we adopted to run CFD simulations with an in-house software on Microsoft Azure.

### 2019-04-02 misc/listfiles4zenodo.py
Add scripts to rsync files to be uploaded to Zenodo

@@ -1,0 +1,36 @@
+"""Build the list of files to rsync for the Zenodo repository."""
+
+import pathlib
+
+
+scriptdir = pathlib.Path(__file__).absolute().parent
+rootdir = scriptdir.parent
+
+excludes = ['.git', '.vscode', '__pycache__',
+            '.xmf', '.pyc',
+            'credentials.yaml', 'id_rsa', 'l_mpi_2017.2.174.tgz']
+
+filepath = scriptdir / 'files4zenodo.txt'
+with open(filepath, 'w') as outfile:
+    filepaths = rootdir.rglob('*')
+    filepaths = [p for p in filepaths if not p.is_dir()]
+    filepaths = [p for p in filepaths
+                 if not any(s in p.as_posix() for s in excludes)]
+    zenodos = [p for p in filepaths if '.zenodo' in p.name]
+    for zenodo in zenodos:
+        parent = zenodo.parent
+        filepaths = [p for p in filepaths
+                     if parent.as_posix() not in p.as_posix()]
+        with open(zenodo, 'r') as infile:
+            lines = infile.readlines()
+            for line in lines:
+                path2 = parent / line.strip()
+                if path2.is_dir():
+                    filepaths.extend(path2.rglob('*'))
+                else:
+                    filepaths.append(path2)
+    filepaths = [p for p in filepaths if '/zenodo/' not in p.as_posix()]
+    filepaths = [p for p in filepaths
+                 if not any(s in p.as_posix() for s in excludes)]
+    filepaths = [str(p.relative_to(rootdir)) + '\n' for p in filepaths]
+    outfile.writelines(filepaths)

### 2019-04-02 misc/rsync4zenodo.sh

@@ -1,0 +1,18 @@
+#!/usr/bin/env bash
+# Rsync data to be uploaded to Zenodo.
+
+scriptdir="$( cd "$(dirname "$0")" ; pwd -P )"
+rootdir="$( cd "$(dirname "$scriptdir")" ; pwd -P )"
+
+python $scriptdir/listfiles4zenodo.py
+
+listpath=$scriptdir/files4zenodo.txt
+destdir=$rootdir/zenodo
+
+mkdir -p $destdir
+
+rsync -av --files-from=$listpath $rootdir $destdir
+
+rm -f $listpath
+
+exit 0

### 2019-04-04 tex/MesnardoBarba2019.tex
add intro passage in section 2

@@
 Scientific publications reporting computational results often lack sufficient details to reproduce the researcher's computational environment; e.g., they may miss to mention external libraries used along with the main computational code.
-We have learned the hard way how different versions of the same external library can alter the numerical results and even the scientific findings of a computational study\cite{mesnard_barba_2017}.
+We have learned the hard way how even different versions of the same external library can alter the numerical results and even the scientific findings of a computational study\cite{mesnard_barba_2017}.
+This section presents an overview and mini-tutorial of the workflow we developed to guarantee the highest level of reproducibility of our computational research, with the best available technology solutions.
+In the process of creating this reproducible workflow, we also evaluated the suitability of public cloud offerings by Microsoft Azure for our research computing needs. 
+The tools we adopted for computing on cloud resources are specific for this provider.
+
 To overcome the so-called ``dependency hell'' and facilitate reproducibility and portability, we use the container technology provided by the open-source project Docker.

### 2019-04-04 tex/MesnardoBarba2019.tex
edits workflow section

@@
 
+\subsection{Use of container technology}
+
 To overcome the so-called ``dependency hell'' and facilitate reproducibility and portability, we use the container technology provided by the open-source project Docker.
+A container represents an isolated user space where application programs run directly on the operating system's kernel (with limited access to its resources).
+In contrast with virtual machines, containers do not include a full operating system, making them lighter and faster.
+Containers allow re-creating the same runtime environment of an application (including all its dependencies) from one machine to another. 
+They empower researchers to share pre-built images of their software stack, ameliorating one of the biggest pain points for reproducible research: building the software in a different machine. 
+The majority of enterprise developers today are familiar with Docker container technology (first released six years ago). 
+But in academic settings, many are still unaware of its value. 
+We present this section as an overview for research software developers unfamiliar with Docker, but comfortable with scripting, version control, and distributed collaboration.
 
-A container represents an isolated user space where application programs run directly on the operating system's kernel (with a limited access to its resources).
-As opposed to Virtual Machines, containers do not include a full operating system, making them lighter and faster.
-Containers allows to re-create the same runtime environment of the applications (that includes all its dependencies) from one machine to another.
 A container is an instance of an image.
-The developer builds the image on a local machine and pushes it to a public registry to make it available to users.
-(Users pull down the image and create containers out of it.)
-To create a Docker image, the developer writes a \texttt{Dockerfile}.
-The \texttt{Dockerfile} is an ASCII file that contains keywords to tell Docker what to do.
-We create a new image from a base image using the keyword \texttt{FROM}.
+The developer builds this image on a local machine and pushes it to a public registry to share it with other users.
+Users pull the image from the public registry,---in our case, DockerHub---and create containers out of it.
+To create a Docker image, the developer writes a \texttt{Dockerfile}.: an ASCII file containing commands that tell Docker what to do.
+For example, we create a new image from a base image using the keyword \texttt{FROM}.
 We then write the different commands to build a multi-layered runtime environment of the application that includes all its dependencies.
-Once we have built the image on the local machine, we push it to a repository on the DockerHub registry, a place to store and retrieve Docker images.
-Listing \ref{lst:docker_build_push} provides the command lines to build (\texttt{docker build}) and push (\texttt{docker push}) an image of our CFD software (\texttt{barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu}) that we used to run some of the examples presented in the next section.
-(Here, \texttt{CLOUDREPRO} is an environment variable set to path of the GitHub repository \texttt{cloud-repro}\footnote{cloud-repro: \url{https://github.com/barbargroup/cloud-repro}} cloned on a local machine.)
+Once we have built the image on the local machine, we push it to a repository on the DockerHub registry: a place to store and retrieve Docker images.
+Listing \ref{lst:docker_build_push} provides the command lines to build (\texttt{docker build}) and push (\texttt{docker push}) an image of our CFD software (\texttt{barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu}) that we used to obtain some of the results presented in the next section.
+Here, \texttt{CLOUDREPRO} is an environment variable set to the local path of the GitHub repository for this paper, \texttt{cloud-repro}\footnote{\url{https://github.com/barbargroup/cloud-repro}} cloned on the user's machine.
 
@@
 
-Everyone can now pull the application image and create a Docker container to run the CFD simulation in a faithfully reproduced local environment.
-The great advantage of container technology is that the same container that was built and tested on a local machine by a developer can now run at scaled in production mode on Virtual Machines, bare metal, or even cloud platforms.
+\noindent Anyone can now pull the application image from DockerHub, and create a Docker container to run the CFD application software in a faithfully reproduced local environment.
+The great advantage of container technology is that the same container that was built and tested on the developer's local machine can now run at scale in production mode on virtual machines, bare metal, or even cloud platforms.
 Our objective is to create and run containers on a public cloud provider such as Microsoft Azure.
-\ref{fig:cloud_workflow} shows a graphical representation of the workflow we adopted to run CFD simulations with an in-house software on Microsoft Azure.
+\ref{fig:cloud_workflow} shows a graphical representation of the workflow we developed using Docker and various tools for running CFD simulations on Microsoft Azure.
+
+\subsection{Use of  public cloud resources}
 

### 2019-04-04 tex/MesnardoBarba2019.tex
more edits to workflow section

@@
 Our objective is to create and run containers on a public cloud provider such as Microsoft Azure.
-\ref{fig:cloud_workflow} shows a graphical representation of the workflow we developed using Docker and various tools for running CFD simulations on Microsoft Azure.
+Figure \ref{fig:cloud_workflow} shows a graphical representation of the workflow we developed using Docker and various tools for running CFD simulations on Microsoft Azure.
+The next section explains these tools.
 
@@
 
-To run computational jobs on Microsoft Azure, we use several tools that facilitate creating and managing virtual machines with compute nodes and submitting jobs to those nodes.
-We use a Microsoft Azure platform service called Azure Batch to run our in-house CFD software.
-Azure Batch services leverages Microsoft Azure at no extra cost to relieve the user from manually creating, configuring, and managing a HPC-capable cluster of cloud nodes, including virtual machines, virtual networks, job and task scheduling infrastructure.
+To run computational jobs on Microsoft Azure, we use several tools that facilitate creating and managing virtual machines with compute nodes, and submitting jobs to those nodes.
+We use a service called Azure Batch that leverages Microsoft Azure at no extra cost, relieving the user from manually creating, configuring, and managing an HPC-capable cluster of cloud nodes, including virtual machines, virtual networks, job and task scheduling infrastructure.
 Azure Batch works with both embarrassingly parallel workloads and tightly-coupled MPI jobs (the latter being the case of our CFD software).
-To use Azure Batch, we need to configure a workspace on Microsoft Azure.
-This can be done either via the Azure Portal in a web browser or from a local terminal user the open-source tool Azure CLI.\footnote{Azure CLI (version 2.0.57): \url{https://github.com/Azure/azure-cli}}
-We prefer to the use command-line solution (program \texttt{az}) as it allows us to keep track of the steps done to configure the Azure workspace (Listing \ref{lst:az_configure}).
+To use Azure Batch, we first need to configure a workspace on Microsoft Azure.
+This can be done either via the Azure Portal in a web browser or from a local terminal using the open-source tool Azure CLI.\footnote{Azure CLI (version 2.0.57): \url{https://github.com/Azure/azure-cli}}
+We prefer to use the command-line solution (program \texttt{az}), as it allows us to keep track of the steps done to configure the Azure workspace (see Listing \ref{lst:az_configure}).
 First, we set the subscription we want to use (let's call it \texttt{reprosubscription}).
-We then create a resource group, \texttt{reprorg}, located in the East US region that will contain all the Azure resources.
-We create an Azure Storage account, \texttt{reprostorage}, in the resource group.
-We also need to create an Azure Batch account, \texttt{reprobatch}, and associate it to the storage account.
+Next, we create a resource group, \texttt{reprorg}, located in this case in the East US region, which will contain all the Azure resources.
+We create an Azure Storage account, \texttt{reprostorage}, in the resource group,
+and we also need to create an Azure Batch account, \texttt{reprobatch} and associate it to the storage account.
 Finally, we create a fileshare (of size $100$ Gb) in the storage.
@@
 To create computational nodes and submit container-based jobs to Azure Batch, we use the open-source command-line utility Batch Shipyard.\footnote{Batch Shipyard (version 3.6.1): https://github.com/Azure/batch-shipyard}
-Batch Shipyard is entirely driven with configuration files: the utility parses user-written YAML file to automatically create pools of compute nodes on Azure Batch and to submit jobs to those pools.
+Batch Shipyard is entirely driven by configuration files: the utility parses user-written YAML files to automatically create pools of compute nodes on Azure Batch and to submit jobs to those pools.
 Typically, we need to provide four configuration files:
@@
 Once the configuration files are written, we invoke Batch Shipyard through the \texttt{shipyard} program on our local machine.
-The folder \texttt{examples/snake2d2k35/config\_shipyard} contains an example YAML files to create a pool of two compute \texttt{NC24r} nodes (that features k80 GPUs and InfiniBand network).
+The folder \texttt{examples/snake2d2k35/config\_shipyard} in the repository accompanying this paper contains an example YAML files to create a pool of two \texttt{NC24r} compute nodes (featuring K80 GPUs and InfiniBand network).
 Listing \ref{lst:shipyard_run} shows the commands to run from your local terminal to create a pool of compute nodes on Azure Batch and submit jobs to it.

### 2019-04-05 tex/MesnardoBarba2019.tex
Add a box with Docker terminologies

@@
 \usepackage{multirow}
+
+\definecolor{lightgray}{rgb}{0.95,0.95,0.95}
 
@@
 \subsection{Use of container technology}
+
+\begin{figure*}
+    \begin{center}
+        \colorbox{lightgray}{
+        \begin{minipage}[c]{14cm}
+        \bigskip
+        \small \sffamily{
+        \subsection*{Docker Terminologies:}
+{\sf \footnotesize
+\textbf{Docker}--- An open source OS-level virtualization software to create and run multiple independent, isolated, and portable containers on the same host Operating System.\\
+\vspace{0.1cm}\\
+\textbf{Docker Image}--- Union of layered filesystems stacked on top of each other.
+Each layer defines a set of differences from the previous layer.
+A user composes (builds) a Docker image using a \texttt{Dockerfile}, usually starting from a base image (such as \texttt{ubuntu:16.04}).\\
+\vspace{0.1cm}\\
+\textbf{Docker Container}--- A standardized unit created from a Docker image to deploy an application or a runtime environment.
+A Docker container can be seen as an instance of a Docker image that includes an additional writable layer at the top of the layered stack.
+When a container is deleted, so is the writable layer, while the image remains unchanged.\\
+\vspace{0.1cm}\\
+\textbf{Dockerfile}--- An ASCII file including the sequence of instructions to create a Docker image for the computational runtime environment.
+A Dockerfile contains Docker keywords such as \texttt{FROM}, \texttt{RUN}, or \texttt{COPY}.
+Each instructions in the \texttt{Dockerfile} creates a layer in the Docker image.\\
+\vspace{0.1cm}\\
+\textbf{DockerHub}--- The official registry of Docker Inc.; a cloud-based registry service to store, share, and retrieve (public or private) Docker images.\\
+}}
+        \vspace{0.2cm}
+        \end{minipage}}
+    \end{center}
+\end{figure*}
 

### 2019-04-08 tex/MesnardoBarba2019.tex
Remove amount of sponsorship

@@
 
-For the year $2018$, Microsoft Azure granted our research lab a sponsorship of $20,000$ USD in cloud credits to run CFD simulations with our in-house software.
+For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
 We a ``pay-as-you-go'' type of subscription, users can directly sees how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
@@
 
-This study was possible thanks to a sponsorship ($\$20,000$ worth of cloud credits) from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}}.
+This study was possible thanks to a sponsorship from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}}.
 

### 2019-04-09 tex/MesnardoBarba2019.tex
Add small edits to workflow section

@@
 To overcome the so-called ``dependency hell'' and facilitate reproducibility and portability, we use the container technology provided by the open-source project Docker.
-A container represents an isolated user space where application programs run directly on the operating system's kernel (with limited access to its resources).
+A container represents an isolated user space where application programs run directly on the operating system's kernel of the host (with limited access to its resources).
 In contrast with virtual machines, containers do not include a full operating system, making them lighter and faster.
@@
 Users pull the image from the public registry,---in our case, DockerHub---and create containers out of it.
-To create a Docker image, the developer writes a \texttt{Dockerfile}.: an ASCII file containing commands that tell Docker what to do.
-For example, we create a new image from a base image using the keyword \texttt{FROM}.
-We then write the different commands to build a multi-layered runtime environment of the application that includes all its dependencies.
-Once we have built the image on the local machine, we push it to a repository on the DockerHub registry: a place to store and retrieve Docker images.
+To create a Docker image, the developer writes a \texttt{Dockerfile}: an ASCII file containing instructions that tell Docker what to do.
+For example, we start building a new image from a base image using the keyword \texttt{FROM}.
+We then write the different shell instructions (with the \texttt{RUN} instruction) to build a multi-layered runtime environment of the application that includes all its dependencies.
+Once we have built and tested the image on the local machine, we push it to a repository on the DockerHub registry: a place to store and retrieve Docker images.
 Listing \ref{lst:docker_build_push} provides the command lines to build (\texttt{docker build}) and push (\texttt{docker push}) an image of our CFD software (\texttt{barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu}) that we used to obtain some of the results presented in the next section.
@@
 We prefer to use the command-line solution (program \texttt{az}), as it allows us to keep track of the steps done to configure the Azure workspace (see Listing \ref{lst:az_configure}).
-First, we set the subscription we want to use (let's call it \texttt{reprosubscription}).
+First, we set the Azure subscription we want to use (let's call it \texttt{reprosubscription}).
 Next, we create a resource group, \texttt{reprorg}, located in this case in the East US region, which will contain all the Azure resources.
-We create an Azure Storage account, \texttt{reprostorage}, in the resource group,
-and we also need to create an Azure Batch account, \texttt{reprobatch} and associate it to the storage account.
-Finally, we create a fileshare (of size $100$ Gb) in the storage.
+We create an Azure Storage account, \texttt{reprostorage}, in the resource group, as well as an Azure Batch account, \texttt{reprobatch}, associated to the storage account.
+Finally, we create a fileshare (in this case of size $100$ GB) in the storage.
 
@@
 Once the configuration files are written, we invoke Batch Shipyard through the \texttt{shipyard} program on our local machine.
-The folder \texttt{examples/snake2d2k35/config\_shipyard} in the repository accompanying this paper contains an example YAML files to create a pool of two \texttt{NC24r} compute nodes (featuring K80 GPUs and InfiniBand network).
+The folder \texttt{examples/snake2d2k35/config\_shipyard} in the repository accompanying this paper contains an example YAML files to create a pool of two \texttt{NC24r} compute nodes (featuring K80 GPUs and using InfiniBand network).
 Listing \ref{lst:shipyard_run} shows the commands to run from your local terminal to create a pool of compute nodes on Azure Batch and submit jobs to it.
@@
 The output of the computation is now stored in the fileshare in our Azure Storage account.
-We can download the data to our local machine to perform additional post-processing steps.
+We can download the data to our local machine to perform additional post-processing steps (such as flow visualizations).
 

### 2019-04-09 tex/MesnardoBarba2019.tex
Read over manuscript (see list)
* Force coefficients figure: use black lines for 2D data and show up to 80 time units.
* Use capitalized titles for sub-sections.
* GPU available late 2016, IB support for NC-series available during 2017.
* Add missing words or correct wrong usage.
* Re-phrase some sentences in Results section.
* Add small explanation about RMDA.
* Re-write paragraph on reproducibility packages.
* (WIP) Mention Zenodo repository that contains output data needed to reproduce figures.
* Add NSF grant in "Acknowledgments" section.

@@
 
-\subsection{Use of container technology}
+\subsection{Use of Container Technology}
 
@@
 
-\subsection{Use of public cloud resources}
+\subsection{Use of Public Cloud Resources}
 
@@
 Until just a few years ago, the products offered by cloud providers were unsuitable to the needs of computational scientists using HPC, due to performance overhead of virtualization and lack of support for fast networking.
-Azure only introduced nodes with GPU devices and Infiniband support in 2017. 
+Azure only introduced nodes with GPU devices during late 2016 and Infiniband support for the NC-series in 2017.
 Our first objective was to assess performance on cloud nodes for the type of computations in our research workflows with  tightly coupled parallel applications. 
@@
 The bandwidth test measures the maximum sustained rate that can be achieved on the network; it consists in having the sender sends a fixed number of messages to a receiver that replies only after receiving all of them.
-The tests ran on \texttt{NC24r} nodes on Azure and \texttt{Ivygpu} nodes on Colonial One, all them featuring a network interface for RDMA (Remote Direct Memory Access) connectivity to communicate over an InfiniBand network.
+The tests ran on \texttt{NC24r} nodes on Azure and \texttt{Ivygpu} nodes on Colonial One, all of them featuring a network interface for RDMA (Remote Direct Memory Access) connectivity to communicate over an InfiniBand network.
+(RDMA allows direct access to a remote's memory without involving the operating system of the host and remote.)
 Fig. \ref{fig:osu_benchmarks} reports the mean latencies and bandwidths obtained over $5$ repetitions on both platforms.
@@
 CFD algorithms often require to solve linear systems with iterative methods.
-For example, the project method implemented in our research software solve a Poisson system every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
-Thus, we investigated the time-to-solution to solve a three-dimensional Poisson system (obtained with a 7-point stencil using central differences) on different nodes of Microsoft Azure and Colonial One.
-The system was solved using a Conjugate-Gradient (CG) method with a classical Algebraic MultiGrid (AMG) preconditioner with an exit criterion set to an absolute tolerance of $10^{-12}$.
+For example, the projection method implemented in our software solve a Poisson system every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
+Thus, we investigated the time-to-solution to solve a three-dimensional Poisson system (obtained with a 7-point stencil central-difference scheme) on different nodes of Microsoft Azure and Colonial One.
+The system was solved using a Conjugate-Gradient (CG) method with a classical Algebraic Multi-Grid (AMG) preconditioner with an exit criterion set to an absolute tolerance of $10^{-12}$.
 The iterative solver ran on CPU nodes (\texttt{H16r} instances on Azure and \texttt{Short} nodes on Colonial One) using the CG algorithm from the PETSc library\cite{balay_et_al_2018} and an AMG preconditioner from Hypre BoomerAMG.
@@
 
-Our research lab is interested in understanding the aerodynamics of flying animals using Computational Fluid Dynamics software.
+Our research lab is interested in understanding the aerodynamics of flying animals via CFD simulations.
 One of our applications deals with the aerodynamics of a snake species, \textit{Chrysopelea Paradisi}, that lives in South-East Asia.
 The arboreal reptile has the remarkable capacity to turn its entire body into a wing and glide over several meters\cite{socha_2011}.
-The so-called flying snake jumps from tree branches, undulates in the air, and is able to produce lift by expanding its ribcage to flatten its ventral surface (morphing its normally circular cross-section into a triangular shape).
+The so-called ``flying snake'' jumps from tree branches, undulates in the air, and is able to produce lift by expanding its ribcage to flatten its ventral surface (morphing its normally circular cross-section into a triangular shape).
 
-To study the flow around the flying snake, we develop a in-house CFD software called PetIBM\cite{chuang_et_al_2018}, a open-source toolbox that solves the two- and three-dimensional incompressible Navier-Stokes equations using a projection method (an approximate block-LU decomposition of the fully discretized equations\cite{perot_1993}) and an Immersed-Boundary Method (IBM).
-Within this framework, the fluid equations are solved on a extended grid that does not conform to the surface of the immersed body.
+To study the flow around the flying snake, we develop a in-house CFD software called PetIBM\cite{chuang_et_al_2018}, a open-source toolbox that solves the two- and three-dimensional incompressible Navier-Stokes equations using a projection method (seen as an approximate block-LU decomposition of the fully discretized equations\cite{perot_1993}) and an Immersed-Boundary Method (IBM).
+Within this framework, the fluid equations are solved over a extended grid that does not conform to the surface of the immersed body.
 To model the presence of the body, the momentum equation is augmented with a forcing term that is activated in the vicinity of the immersed boundary.
@@
 PetIBM also implements Immersed Boundary Methods (IBMs) that fit into the projection method and, in the present study, we use an implementation of the IBM proposed in \cite{li_et_al_2016}.
-PetIBM runs on distributed-memory architectures and relies on the efficient data structures and parallel routines of the PETSc library.
+PetIBM runs on distributed-memory architectures using the efficient data structures and parallel routines from the PETSc library.
 The software also implements the possibility to solve linear systems on multiple GPU devices distributed across the nodes with the NVIDIA AmgX and AmgXWrapper\cite{chuang_barba_2017}.
-To obtain reproducible computational results, the code used to run the simulations needs to be made available.
+One of the requirements to produce reproducible computational results is the make the code available.
 In that regard, PetIBM is open source, version-controlled on GitHub,\footnote{PetIBM (version 0.4): \url{https://github.com/barbagroup/PetIBM}} and developed under the permissive BSD-3 clause license.
@@
 (The immersed boundary is discretized with the same resolution than the background fluid grid.)
-A convective condition was used at the outlet boundary while freestream conditions were enforced on the others.
-The job was submitted to a pool of two \texttt{NC24r} nodes, with $12$ MPI processes and $2$ GPU devices per node.
-The task completed $200,000$ time steps (i.e., $80$ time units of flow simulation with a time-step size $\Delta t = 0.0004 c / U_\infty$) in just above $7$ hours.
+A convective condition was used at the outlet boundary while freestream conditions were enforced on the three other boundaries.
+The job was submitted to a pool of two \texttt{NC24r} nodes, using $12$ MPI processes and $2$ GPU devices per node.
+The task completed $200,000$ time steps (i.e., $80$ time units of flow simulation with time-step size $\Delta t = 0.0004 c / U_\infty$) in just above $7$ hours.
 
@@
 
-Although the two-dimensional simulations gave us some insights into to flow dynamics happening in the behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional will develop in the wake.
-Thus, we submitted jobs to Azure Batch to perform direct numerical simulation of the three-dimensional flow around a cylinder with the same anatomically accurate cross-section.
-The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
+Although the two-dimensional simulations gave us some insights into to flow dynamics happening in the behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional structures will develop in the wake.
+Thus, we submitted jobs to Azure Batch to perform direct numerical simulation of the three-dimensional flow around snake model: a cylinder with the same anatomically accurate cross-section.
+The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (with a uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
 The grid is kept uniform in the $z$-direction and we enforce periodic conditions at the front and back boundaries.
@@
 Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von Karman street exhibits a narrower wake.
-We note the presence of an unsteady recirculation region just behind the snake cylinder and alternating regions of positive and negative cross-flow velocity showing the presence of von Karman vortices (Fig.
+We also note the presence of an unsteady recirculation region just behind the snake cylinder and alternating regions of positive and negative cross-flow velocity showing the presence of von Karman vortices (Fig.
 \ref{fig:ux_uy_xz_plane_3d}).
-Fig. \ref{fig:qcrit_wx_3d} shows the isosurfaces of the Q-criterion after $100$ time units and highlights the complexity of the three-dimensional turbulent wake generated by the snake model.
+Fig.
+\ref{fig:qcrit_wx_3d} shows a side-view of the isosurfaces of the Q-criterion after $100$ time units and highlights the complexity of the three-dimensional turbulent wake generated by the snake model.
 
@@
     \renewcommand{\arraystretch}{1.5}
-    \caption{Details about the computational grids used for the snake simulations with PetIBM.}
+    \caption{Details about the computational grids used for the snake simulations with PetIBM. Distances are expressed in terms of chord-length units.}
     \label{tab:grid_specs}
@@
         2D & $30 \times 30$ & $\left[ -0.52, 3.48 \right] \times \left[ -2, 2 \right]$ & $0.004 \times 0.004$ & $1.01$ & $1704 \times 1706$ \\
-        3D & $30c \times 30c \times 3.2c$ & $\left[ -0.52, 3.48 \right] \times \left[ -2, 2 \right] \times \left[ 0, 3.2 \right]$ & $0.008 \times 0.008 \times 0.08$ & $1.01$ & $1071 \times 1072 \times 40$ \\
+        3D & $30 \times 30 \times 3.2$ & $\left[ -0.52, 3.48 \right] \times \left[ -2, 2 \right] \times \left[ 0, 3.2 \right]$ & $0.008 \times 0.008 \times 0.08$ & $1.01$ & $1071 \times 1072 \times 40$ \\
         \hline
@@
 For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
-We a ``pay-as-you-go'' type of subscription, users can directly sees how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
+With a ``pay-as-you-go'' subscription, users can immediately sees how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
 From May to December, we spend a total of $20,614$ USD to run simulations of the gliding snake.
-During that period, we have been charged data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
-More than $99\%$ of the charges are due the usage of virtual machines.
-We had the opportunity to use different instances on Microsoft Azure and most the charges for the usage of virtual machines of the \texttt{NC24r} instance (used for the two- and three-dimensional simulations of the flying snake).
-The \texttt{NC24r} instance is part of the NC-series (Table \ref{tab:nc_series}); we copiously used as it enables RDMA capabilities for our MPI application and features NVIDIA K80 GPU devices.
+During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
+More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
+To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
 For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
@@
 Command-line tools such as Azure-CLI and Batch Shipyard were greatly helpful to create and submit everything from our local terminal.
-(In our research lab, we tend to avoid, as much as possible, interacting with graphical-user interfaces, so as to make our workflow more reproducible.)
-Azure-CLI helped us to setup the Azure Batch account and its associated Azure Storage, as well as uploading/downloading our simulation data.
-With Batch Shipyard, users do not need to have experience with the Azure Batch SDK.
-We have used Batch Shipyard to submit jobs on Azure Batch to run Docker container-based multi-tasks.
+(In our research lab, we tend to avoid, as much as possible, interacting with graphical-user interfaces, to make our workflow more reproducible.)
+Azure-CLI helped us to setup the Azure Batch account and its associated Azure Storage, as well as uploading/downloading simulation data.
+With Batch Shipyard, we did not need to have experience with the software development kit to use Azure Batch.
+We have used Batch Shipyard to submit jobs on Azure Batch to run Docker container-based multi-instance tasks.
 Note that Batch Shipyard also support Singularity containers.
@@
 
-In a new effort to make our research transparent and reproducible by others, we have version-controlled all the input files, pre- and post-processing scripts, as well as the Dockerfiles (used to create the Docker images), the Batch Shipyard configuration files, and command-line instructions required to rerun the simulations on Microsoft Azure.
-In addition, all the scripts to reproduce the figures in the present article are made available.
-The reproducibility packages are hosted on GitHub in the repository \texttt{cloud-repro}.\footnote{\url{https://github.com/barbagroup/cloud-repro}}
+In a new effort to make our research transparent and reproducible by others, we have version-controlled all the files necessary to re-run the examples highlighted in this paper.
+The repository \texttt{cloud-repro}\footnote{\url{https://github.com/barbagroup/cloud-repro}} is hosted on GitHub.
+The reproducibility packages contains input files, Batch Shipyard configuration files, command-line instructions to setup and submit jobs to Microsoft Azure, as well as the post-processing scripts to reproduce the figures of this paper.
+Although they are not required to reproduce the computations, the Dockerfiles to build Docker images are also made available.
+These files contain details about the all libraries installed to create the computational runtime environment.
+In addition, we have also uploaded to Zenodo all output data required to just reproduce the figures of the present paper.
 
- \section*{Acknowledgment}
+\section*{Acknowledgments}
 
-This study was possible thanks to a sponsorship from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}}.
+This study was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No.
+CCF-1747669.
 

### 2019-04-09 examples/snake3d2k35/scripts/plot_force_coefficients_compare_2d.py

@@ -48,10 +48,12 @@ ax.set_ylabel('Force coefficients')
 ax.grid()
 ax.plot(t, cd, label='$C_D$')
 ax.plot(t, cl, label='$C_L$')
-ax.plot(t2, cd2, label='$C_D$ (2D)', color='grey', linestyle='-')
-ax.plot(t2, cl2, label='$C_L$ (2D)', color='grey', linestyle='--')
-ax.legend(ncol=2)
-ax.set_xlim(t[0], t[-1])
+ax.plot(t2, cd2, label='$C_D$ (2D)', 
+        color='black', linewidth=0.75, linestyle='--')
+ax.plot(t2, cl2, label='$C_L$ (2D)',
+        color='black', linewidth=0.75, linestyle='-')
+ax.legend(ncol=4)
+ax.set_xlim(0.0, 80.0)
 ax.set_ylim(0.55, 3.5)
 fig.tight_layout()
 

### 2019-04-10 tex/MesnardoBarba2019.tex
Revise user-experience paragraphs

@@
 
-% Mention the 7-day limitation for jobs with Azure Batch. (WARNING: according to the Batch Shipyard documentation, tasks can have a maximum lifetime of 180 days.)
-% Mention that Batch Shipyard can pull images from public and private registries.
-% Mention that Singularity containers are also supported in Batch Shipyard.
-
 For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
@@
 
-Command-line tools such as Azure-CLI and Batch Shipyard were greatly helpful to create and submit everything from our local terminal.
-(In our research lab, we tend to avoid, as much as possible, interacting with graphical-user interfaces, to make our workflow more reproducible.)
-Azure-CLI helped us to setup the Azure Batch account and its associated Azure Storage, as well as uploading/downloading simulation data.
-With Batch Shipyard, we did not need to have experience with the software development kit to use Azure Batch.
-We have used Batch Shipyard to submit jobs on Azure Batch to run Docker container-based multi-instance tasks.
-Note that Batch Shipyard also support Singularity containers.
+Command-line utilities such as Azure-CLI and Batch Shipyard were greatly helpful to create and manage resources on Microsoft Azure to conduct reproducible research.
+(In our lab, we tend to avoid interacting directly with graphical-user interfaces to keep a trace of the commands run and make the workflow more reproducible.)
+Azure-CLI helped us setup the Azure Batch and Storage accounts as well as moving data between the cloud platform and our local machines.
+Thanks to Batch Shipyard, we did not have to dig into the software development kit of Azure Batch to use the service.
+Writing YAML configuration files was all we needed to create a pool of virtual machines with Batch Shipyard and to submit jobs to it.
+With Batch Shipyard, we have painlessly submitted jobs on Azure Batch to run multi-instance tasks in Docker containers; everything from the command-line terminal on a local machine.
+Note that Bach Shipyard also support Singularity containers.
 
-Our in-house CFD research software makes use of the MPI library to run applications on distributed-memory architectures.
-We used Azure instances that feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over an InfiniBand network.
+Our in-house CFD software, PetIBM, relies on MPI to run applications on distributed-memory architectures.
+The Poisson system is solved on distribute GPU devices using the NVIDIA AmgX library.
+Thus, we have used Azure instances of the NC-series that feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over InfiniBand network.
 As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.
 
-Moreover, Microsoft Azure implements quotas, such as the maximum number of cores that can be used in a certain region.
-To run our simulations, we had to open online customer support requests every time we wanted to increase our core quota for a subscription, with a certain service in certain region with a certain type of instances.
+Moreover, Microsoft Azure implements quotas and limits on resources with Azure Batch service, such as the maximum number of dedicated cores that can used in a certain region.
+To be able to run our simulations, we had to contact Azure Support through Azure Portal to request a quota increase for a given type of instances in a specific region and for a given subscription.
 We had to go through this process at least five times during our sponsorship period.
+The readers should be aware of these quotas and limits before scaling up workloads on Azure Batch.
 

### 2019-04-10 tex/MesnardoBarba2019.tex
Add comments about p2p results

@@
 Fig. \ref{fig:osu_benchmarks} reports the mean latencies and bandwidths obtained over $5$ repetitions on both platforms.
+For small message sizes, the averaged latency on Colonial One and Azure are $1.75$ and $1.95 \mu s$, respectively.
+As the message size increases, the latency becomes smaller on Azure compared to Colonial One.
+The maximum sustained bandwidth rates for Colonial One and Azure are on average $4.5$ and $5.6 GB/s$, respectively.
+For all message sizes, a higher bandwidth rates was achieved on Azure.
+Over the last few years, Microsoft Azure has improved its HPC solution to provide networking capabilities that are comparable or even better than our 6-year-old university-managed cluster.
 

### 2019-04-10 tex/MesnardoBarba2019.tex
Add comments about Poisson results

@@
 We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
-The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) is solved on a single node using $12$ MPI processes and $2$ GPU devices; we then double the mesh size as we double the number of nodes.
+The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) is solved on a single node using $12$ MPI processes and $2$ GPU devices; we then double the mesh size as we double the number of nodes (keeping the same number of MPI processes and GPUs per node).
 As the number of iterations to reach convergence increases with the size of the system, we normalize the runtimes by the number of iterations.
 Fig. \ref{fig:poisson_benchmarks} (bottom left) shows the normalized mean runtimes ($5$ repetitions) obtained on Azure and Colonial One.
+The smaller runtimes on Azure are explained by the fact the NC-series of Microsoft Azure features NVIDIA K80 GPU devices with a higher compute capability than the K20 GPUs on Colonial One.
 The bottom-right panel of the figure reports the normalized mean runtimes obtained on Azure when we put more constraint on the bandwidth; the base mesh now contains $25$ millions cells ($1000 \times 500 \times 50$).
+We observe larger variations in the time-to-solution for the Poisson system on Microsoft Azure; runtimes are more constant on Colonial One.
 

### 2019-04-10 tex/MesnardoBarba2019.tex
move fig.1 closer to where first mentioned

@@
 Listing \ref{lst:docker_build_push} provides the command lines to build (\texttt{docker build}) and push (\texttt{docker push}) an image of our CFD software (\texttt{barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu}) that we used to obtain some of the results presented in the next section.
-Here, \texttt{CLOUDREPRO} is an environment variable set to the local path of the GitHub repository for this paper, \texttt{cloud-repro}\footnote{\url{https://github.com/barbargroup/cloud-repro}} cloned on the user's machine.
+Here, \texttt{CLOUDREPRO} is an environment variable set to the local path of the GitHub repository for this paper, \texttt{cloud-repro},\footnote{\url{https://github.com/barbargroup/cloud-repro}} cloned on the user's machine.
 
@@
 The next section explains these tools.
+
+\begin{figure*}[b]
+    \centering
+    \includegraphics[width=16cm]{figures/cloud_workflow.png}
+    \caption{Reproducible workflow on the public cloud provider Microsoft Azure.
+Our CFD software is version-controlled with Git and GitHub.
+We push to DockerHub a Docker image of our CFD application with all its dependencies.
+Azure-CLI is use to configure accounts on Microsoft Azure and to upload/download data to/from an Azure Storage account.
+With Batch Shipyard, we can create pool on Azure Batch and run container-based simulation using our Docker image.}
+    \label{fig:cloud_workflow}
+\end{figure*}
 
@@
 The reproducibility packages of the examples showcased in the next section are available in the GitHub repository \texttt{cloud-repro}, which includes instructions on how to reproduce the results.
-
-\begin{figure*}[!h]
-    \centering
-    \includegraphics[width=16cm]{figures/cloud_workflow.png}
-    \caption{Reproducible workflow on the public cloud provider Microsoft Azure.
-Our CFD software is version-controlled with Git and GitHub.
-We push to DockerHub a Docker image of our CFD application with all its dependencies.
-Azure-CLI is use to configure accounts on Microsof Azure and to upload/download data to/from an Azure Storage account.
-With Batch Shipyard, we can create pool on Azure Batch and run container-based simulation using our Docker image.}
-    \label{fig:cloud_workflow}
-\end{figure*}
 

### 2019-04-10 tex/MesnardoBarba2019.tex
copy edit results sectin, up to 3.2

@@
 This can be done either via the Azure Portal in a web browser or from a local terminal using the open-source tool Azure CLI.\footnote{Azure CLI (version 2.0.57): \url{https://github.com/Azure/azure-cli}}
-We prefer to use the command-line solution (program \texttt{az}), as it allows us to keep track of the steps done to configure the Azure workspace (see Listing \ref{lst:az_configure}).
+We prefer to use the command-line solution (program \texttt{az}), as it allows us to keep track of the steps taken to configure the Azure workspace (see Listing \ref{lst:az_configure}).
 First, we set the Azure subscription we want to use (let's call it \texttt{reprosubscription}).
@@
 Thus, the Dockerfile and YAML configuration files should be made part of an extended reproducibility package that includes workflow instructions for cloud computing, in addition to other input files.
-Such reproducibility package facilitates re-creating the cloud environment to run the simulations under the same conditions.
+Such a reproducibility package facilitates re-creating the cloud environment to run the simulations under the same conditions.
 The reproducibility packages of the examples showcased in the next section are available in the GitHub repository \texttt{cloud-repro}, which includes instructions on how to reproduce the results.
@@
 
-Point-to-point MPI benchmarks from the Ohio State University Micro-Benchmarks\footnote{OSU Micro-Benchmarks (version 5.6): \url{http://mvapich.cse.ohio-state.edu/benchmarks/}} suite ran on Microsoft Azure and Colonial One to investigate performance in terms the latency and bandwidth.
-The latency test is carried out in a ping-pong fashion and measures the time elapsed to get a response; the sender sends a message with a certain data size and wait for the receiver to send back the message with the same data size.
-The bandwidth test measures the maximum sustained rate that can be achieved on the network; it consists in having the sender sends a fixed number of messages to a receiver that replies only after receiving all of them.
+We ran point-to-point MPI benchmarks from the Ohio State University Micro-Benchmarks suite\footnote{OSU Micro-Benchmarks (version 5.6): \url{http://mvapich.cse.ohio-state.edu/benchmarks/}} on Microsoft Azure and Colonial One, to investigate performance in terms the latency and bandwidth.
+The latency test is carried out in a ping-pong fashion and measures the time elapsed to get a response; the sender sends a message with a certain data size and waits for the receiver to send back the message with the same data size.
+The bandwidth test measures the maximum sustained rate that can be achieved on the network; the sender sends a fixed number of messages to a receiver that replies only after receiving all of them.
 The tests ran on \texttt{NC24r} nodes on Azure and \texttt{Ivygpu} nodes on Colonial One, all of them featuring a network interface for RDMA (Remote Direct Memory Access) connectivity to communicate over an InfiniBand network.
@@
 Fig. \ref{fig:osu_benchmarks} reports the mean latencies and bandwidths obtained over $5$ repetitions on both platforms.
-For small message sizes, the averaged latency on Colonial One and Azure are $1.75$ and $1.95 \mu s$, respectively.
+For small message sizes, the average latencies on Colonial One and Azure are $1.75$ and $1.95 \mu $s, respectively.
 As the message size increases, the latency becomes smaller on Azure compared to Colonial One.
-The maximum sustained bandwidth rates for Colonial One and Azure are on average $4.5$ and $5.6 GB/s$, respectively.
-For all message sizes, a higher bandwidth rates was achieved on Azure.
+The maximum sustained bandwidth rates for Colonial One and Azure are on average $4.5$ and $5.6$ GB/s, respectively.
+For all message sizes, a higher bandwidth rate was achieved on Azure.
 Over the last few years, Microsoft Azure has improved its HPC solution to provide networking capabilities that are comparable or even better than our 6-year-old university-managed cluster.
@@
 
-CFD algorithms often require to solve linear systems with iterative methods.
-For example, the projection method implemented in our software solve a Poisson system every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
-Thus, we investigated the time-to-solution to solve a three-dimensional Poisson system (obtained with a 7-point stencil central-difference scheme) on different nodes of Microsoft Azure and Colonial One.
-The system was solved using a Conjugate-Gradient (CG) method with a classical Algebraic Multi-Grid (AMG) preconditioner with an exit criterion set to an absolute tolerance of $10^{-12}$.
+CFD algorithms often require solving linear systems with iterative methods.
+For example, the projection Navier-Stokes solver implemented in our software requires the solution of a Poisson system on every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
+We investigated the time-to-solution for a three-dimensional Poisson system (obtained with a 7-point stencil central-difference scheme) on different nodes of Microsoft Azure and Colonial One.
+The solution method was a Conjugate-Gradient (CG) method with a classical algebraic multi-grid (AMG) preconditioner using an exit criterion set to an absolute tolerance of $10^{-12}$.
 The iterative solver ran on CPU nodes (\texttt{H16r} instances on Azure and \texttt{Short} nodes on Colonial One) using the CG algorithm from the PETSc library\cite{balay_et_al_2018} and an AMG preconditioner from Hypre BoomerAMG.
@@
 We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
-The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) is solved on a single node using $12$ MPI processes and $2$ GPU devices; we then double the mesh size as we double the number of nodes (keeping the same number of MPI processes and GPUs per node).
-As the number of iterations to reach convergence increases with the size of the system, we normalize the runtimes by the number of iterations.
+The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) iwassolved on a single compute node using $12$ MPI processes and $2$ GPU devices; we then doubled the mesh size as we doubled the number of nodes (keeping the same number of MPI processes and GPUs per node).
+The number of iterations to reach convergence increases with the size of the system, so we normalize the runtimes by the number of iterations.
 Fig. \ref{fig:poisson_benchmarks} (bottom left) shows the normalized mean runtimes ($5$ repetitions) obtained on Azure and Colonial One.
-The smaller runtimes on Azure are explained by the fact the NC-series of Microsoft Azure features NVIDIA K80 GPU devices with a higher compute capability than the K20 GPUs on Colonial One.
-The bottom-right panel of the figure reports the normalized mean runtimes obtained on Azure when we put more constraint on the bandwidth; the base mesh now contains $25$ millions cells ($1000 \times 500 \times 50$).
-We observe larger variations in the time-to-solution for the Poisson system on Microsoft Azure; runtimes are more constant on Colonial One.
+The smaller runtimes on Azure are explained by the fact that the NC-series of Microsoft Azure features NVIDIA K80 GPU devices with a higher compute capability than the K20 GPUs on Colonial One.
+The bottom-right panel of the figure reports the normalized mean runtimes obtained on Azure when we load the bandwidth with a larger problem; the base mesh now contains $25$ millions cells ($1000 \times 500 \times 50$).
+We observe larger variations in the time-to-solution for the Poisson system on Microsoft Azure; runtimes are more uniform on Colonial One.
 

### 2019-04-10 tex/MesnardoBarba2019.tex
final edits results section

@@
 One of our applications deals with the aerodynamics of a snake species, \textit{Chrysopelea Paradisi}, that lives in South-East Asia.
-The arboreal reptile has the remarkable capacity to turn its entire body into a wing and glide over several meters\cite{socha_2011}.
+This arboreal reptile has the remarkable capacity to turn its entire body into a wing and glide over several meters\cite{socha_2011}.
 The so-called ``flying snake'' jumps from tree branches, undulates in the air, and is able to produce lift by expanding its ribcage to flatten its ventral surface (morphing its normally circular cross-section into a triangular shape).
 
-To study the flow around the flying snake, we develop a in-house CFD software called PetIBM\cite{chuang_et_al_2018}, a open-source toolbox that solves the two- and three-dimensional incompressible Navier-Stokes equations using a projection method (seen as an approximate block-LU decomposition of the fully discretized equations\cite{perot_1993}) and an Immersed-Boundary Method (IBM).
+To study the flow around the flying snake, we developed a CFD software called PetIBM\cite{chuang_et_al_2018}, an open-source toolbox that solves the two- and three-dimensional incompressible Navier-Stokes equations using a projection method (seen as an approximate block-LU decomposition of the fully discretized equations\cite{perot_1993}) and an immersed-boundary method (IBM).
 Within this framework, the fluid equations are solved over a extended grid that does not conform to the surface of the immersed body.
@@
 This technique allows the use of simple fixed structured Cartesian grids to solve the equations.
-PetIBM also implements Immersed Boundary Methods (IBMs) that fit into the projection method and, in the present study, we use an implementation of the IBM proposed in \cite{li_et_al_2016}.
+PetIBM also implements immersed boundary methods (IBMs) that fit into the projection method; in the present study, we use the IBM scheme proposed in \cite{li_et_al_2016}.
 PetIBM runs on distributed-memory architectures using the efficient data structures and parallel routines from the PETSc library.
-The software also implements the possibility to solve linear systems on multiple GPU devices distributed across the nodes with the NVIDIA AmgX and AmgXWrapper\cite{chuang_barba_2017}.
-One of the requirements to produce reproducible computational results is the make the code available.
-In that regard, PetIBM is open source, version-controlled on GitHub,\footnote{PetIBM (version 0.4): \url{https://github.com/barbagroup/PetIBM}} and developed under the permissive BSD-3 clause license.
+The software also implements the possibility to solve linear systems on multiple GPU devices distributed across the nodes with the NVIDIA AmgX library and our AmgXWrapper\cite{chuang_barba_2017}.
+One of the requirements for reproducible computational results is to make the code available under a public license (allowing reuse and modification by others).
+In that regard, PetIBM is open source, version-controlled on GitHub,\footnote{PetIBM (version 0.4): \url{https://github.com/barbagroup/PetIBM}} and shared under the permissive (non copy-left) BSD-3 clause license.
 
@@
 
-With Batch Shipyard, we submitted a job on Azure Batch to compute the two-dimensional flow around an anatomically accurate sectional shape of the gliding snake.
-The cross-section has a chord-length of $1$ and forms a $35$-degree angle of attack with the incoming freestream flow.
+We submitted a job on Azure Batch (via Batch Shipyard,) to compute the two-dimensional flow around an anatomically accurate sectional shape of the gliding snake.
+The cross-section has a chord-length $c=1$ and forms a $35$-degree angle of attack with the incoming freestream flow.
 The Reynolds number, based on the freestream speed, the body chord-length, the kinematic viscosity, is set to $Re=2000$.
-The immersed boundary is centered in a $30c \times 30c$ computational domain that contains just above $2.9$ million cells.
+The immersed boundary is centered in a $30c \times 30c$ computational domain that contains just over $2.9$ million cells.
 The grid is kept uniform with the highest resolution in the vicinity of the body and stretched to the external boundaries with a constant ratio (see Table \ref{tab:grid_specs} for details about the grid).
-(The immersed boundary is discretized with the same resolution than the background fluid grid.)
+For the immersed boundary, the same grid resolution than the background fluid grid was applied.
 A convective condition was used at the outlet boundary while freestream conditions were enforced on the three other boundaries.
 The job was submitted to a pool of two \texttt{NC24r} nodes, using $12$ MPI processes and $2$ GPU devices per node.
-The task completed $200,000$ time steps (i.e., $80$ time units of flow simulation with time-step size $\Delta t = 0.0004 c / U_\infty$) in just above $7$ hours.
+It completed $200,000$ time steps (i.e., $80$ time units of flow simulation with time-step size $\Delta t = 0.0004 c / U_\infty$) in just above $7$ hours (wall-clock time).
 
@@
 The time-averaged force coefficients (between $40$ and $80$ time units) are reported in Table \ref{tab:force_coefficients}.
-Fig. \ref{fig:wz_2d} shows snapshots of the vorticity field after $20$, $44$, $45$, and $80$ time unit of flow simulation.
+Fig. \ref{fig:wz_2d} shows snapshots of the vorticity field after $20$, $44$, $45$, and $80$ time units of flow simulation.
 After $20$ time units, the vortices shed from the snake section are almost aligned in the near wake (with a slight deflection towards the lower part of the domain).
@@
 
-Although the two-dimensional simulations gave us some insights into to flow dynamics happening in the behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional structures will develop in the wake.
-Thus, we submitted jobs to Azure Batch to perform direct numerical simulation of the three-dimensional flow around snake model: a cylinder with the same anatomically accurate cross-section.
+Although the two-dimensional simulations can give us some insights into to flow dynamics happening in the wake behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional structures will develop in the wake.
+We submitted jobs on Azure Batch to perform direct numerical simulation of the three-dimensional flow around a snake model: a cylinder with the an anatomically accurate cross-section.
 The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (with a uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
@@
 Fig. \ref{fig:force_coefficients} compares the history of the force coefficients between the two- and three-dimensional configurations.
-The force coefficients resulting from the two-dimensional simulation of the snake are higher than those obtained for the snake cylinder; a relative difference of $+37.9\%$ and $+14.4\%$ for the time-averaged drag and lift coefficient, respectively (see Table \ref{tab:force_coefficients}).
-Two-dimensional computational simulations of fundamentally three-dimensional flows lead to incorrect estimation of the force coefficients\cite{mittal_balachandar_1995}.
+The force coefficients resulting from the two-dimensional simulation of the snake are higher than those obtained for the snake cylinder; we computed a relative difference of $+37.9\%$ and $+14.4\%$ for the time-averaged drag and lift coefficient, respectively (see Table \ref{tab:force_coefficients}).
+Two-dimensional computational simulations of fundamentally three-dimensional flows lead to incorrect estimation of the force coefficients, as is well known\cite{mittal_balachandar_1995}.
 
 Fig. \ref{fig:wz_avg_3d} shows the instantaneous spanwise vorticity averaged along the $z$-direction after $80$ and $100$ time units.
-Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von Karman street exhibits a narrower wake.
-We also note the presence of an unsteady recirculation region just behind the snake cylinder and alternating regions of positive and negative cross-flow velocity showing the presence of von Karman vortices (Fig.
+Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von Karman street exhibits a narrower wake than in the two-dimensional simulations.
+We also note the presence of an unsteady recirculation region just behind the snake cylinder, and alternating regions of positive and negative cross-flow velocity showing the presence of von Karman vortices (Fig.
 \ref{fig:ux_uy_xz_plane_3d}).
@@
 
-\begin{figure}[!h]
+The selection of results presented here corresponds to a typical set of experiments included in a CFD study. 
+A comprehensive study might include several similar sets, leading to additional insights about the flow dynamics, and clues to future avenues of research.
+We include this selection here to represent a typical workflow, and combine our discussion with a meaningful analysis of the costs associated with running CFD studies in a public cloud.
+
+\begin{figure}
     \centering
     \includegraphics[width=8cm]{figures/forceCoefficientsCompare2D.pdf}
-    \caption{History of the force coefficients obtained with two- and three-dimensional simulations at Reynolds number $2000$ for a snake cross-section with a $35$-degree angle of attack.}
+    \caption{History of the force coefficients obtained with two- and three-dimensional simulations at Reynolds number $2000$ for a snake cross-section with a $35$-degree angle of attack.
+As expected, the two-dimensional simulations over-estimate the force coefficients of what is essentially a three-dimensional flow problem.}
     \label{fig:force_coefficients}
@@
 
-\begin{table*}[!h]
+\begin{table*}
     \renewcommand{\arraystretch}{1.5}
@@
 
-\begin{figure}[!h]
+\begin{figure}
     \centering
     \includegraphics[width=8cm]{figures/wz_avg_multi_contourf.png}
-    \caption{Filled contour of the spanwise-averaged z-component of the vorticity ($-5 \leq w_z c / U_\infty \leq 5$) field after $80$ and $100$ time units of flow simulation with PetIBM for the snake cylinder with a cross-section at a $35$-degree angle of attack and Reynolds number $2000$.}
+    \caption{Filled contour of the spanwise-averaged z-component of the vorticity ($-5 \leq w_z c / U_\infty \leq 5$) field after $80$ and $100$ time units of three-dimensional flow simulation with PetIBM for the snake cylinder with a cross-section at a $35$-degree angle of attack and Reynolds number $2000$.}
     \label{fig:wz_avg_3d}
@@
 
-\begin{figure}[!h]
+\begin{figure}
     \centering

### 2019-04-11 tex/MesnardoBarba2019.tex
edits final section
(We still need a concluding paragraph.)

@@
     \centering
-    \includegraphics[width=16cm]{figures/qcrit_wx_wake3d_0020.png}
+    \includegraphics[width=18cm]{figures/qcrit_wx_wake3d_0020.png}
     \caption{Lateral view of the isosurfaces of the Q-criterion ($Q = 1.0$) in the wake of the snake cylinder (with a $35$-degree angle of attack) at Reynolds number $2000$.
@@
 For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
-With a ``pay-as-you-go'' subscription, users can immediately sees how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
-From May to December, we spend a total of $20,614$ USD to run simulations of the gliding snake.
+With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
+From May to December, we spent a total of $20,614$ USD to run simulations of the gliding snake.
 During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
@@
 
-Command-line utilities such as Azure-CLI and Batch Shipyard were greatly helpful to create and manage resources on Microsoft Azure to conduct reproducible research.
+Command-line utilities such as Azure-CLI and Batch Shipyard were of great help to create and manage resources on Microsoft Azure for executing our reproducible research workflow.
 (In our lab, we tend to avoid interacting directly with graphical-user interfaces to keep a trace of the commands run and make the workflow more reproducible.)
-Azure-CLI helped us setup the Azure Batch and Storage accounts as well as moving data between the cloud platform and our local machines.
+Azure-CLI helped us set up the Azure Batch and Storage accounts as well as moving data between the cloud platform and our local machines.
 Thanks to Batch Shipyard, we did not have to dig into the software development kit of Azure Batch to use the service.
-Writing YAML configuration files was all we needed to create a pool of virtual machines with Batch Shipyard and to submit jobs to it.
-With Batch Shipyard, we have painlessly submitted jobs on Azure Batch to run multi-instance tasks in Docker containers; everything from the command-line terminal on a local machine.
-Note that Bach Shipyard also support Singularity containers.
+Writing YAML configuration files was all we needed to do to create a pool of virtual machines with Batch Shipyard and to submit jobs to it.
+With Batch Shipyard, we have painlessly submitted jobs on Azure Batch to run multi-instance tasks in Docker containers, everything from the command-line terminal on a local machine.
+Note that Bach Shipyard also supports Singularity containers.
 
 Our in-house CFD software, PetIBM, relies on MPI to run applications on distributed-memory architectures.
-The Poisson system is solved on distribute GPU devices using the NVIDIA AmgX library.
-Thus, we have used Azure instances of the NC-series that feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over InfiniBand network.
+The Poisson system is solved on distributed GPU devices using the NVIDIA AmgX library.
+Thus, we used Azure instances of the NC-series, which feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over InfiniBand network.
 As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.
 
-Moreover, Microsoft Azure implements quotas and limits on resources with Azure Batch service, such as the maximum number of dedicated cores that can used in a certain region.
+Microsoft Azure implements quotas and limits on resources with Azure Batch service, such as the maximum number of dedicated cores that can used in a certain region.
 To be able to run our simulations, we had to contact Azure Support through Azure Portal to request a quota increase for a given type of instances in a specific region and for a given subscription.
@@
 
-In a new effort to make our research transparent and reproducible by others, we have version-controlled all the files necessary to re-run the examples highlighted in this paper.
-The repository \texttt{cloud-repro}\footnote{\url{https://github.com/barbagroup/cloud-repro}} is hosted on GitHub.
-The reproducibility packages contains input files, Batch Shipyard configuration files, command-line instructions to setup and submit jobs to Microsoft Azure, as well as the post-processing scripts to reproduce the figures of this paper.
+In a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
+The repository is found at \url{https://github.com/barbagroup/cloud-repro}.
+
+Our expanded reproducibility packages contain input files, Batch Shipyard configuration files, command-line instructions to set up and submit jobs to Microsoft Azure, as well as the post-processing scripts to reproduce the figures of this paper.
 Although they are not required to reproduce the computations, the Dockerfiles to build Docker images are also made available. 
-These files contain details about the all libraries installed to create the computational runtime environment.
-In addition, we have also uploaded to Zenodo all output data required to just reproduce the figures of the present paper.
+These files contain details about all the libraries needed to create the computational runtime environment.
+We even included a Dockerfile to reproduce the local environment with the visualization tools needed for post-processing.
+In addition, we have also deposited in the Zenodo service all secondary data required to reproduce the figures of the paper without running the simulations again.
 
@@
 
-This study was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No.
+This work was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No.
 CCF-1747669.

### 2019-04-11 tex/MesnardoBarba2019.tex
Minor edits (see list)
* Add "drop cap" letters.
* Mention Linux VMs for IB on NC-series.
* Drop "front" and "back" boundaries.
* Change "Lessons Learned" to "User Experience".
* Add comment about paragraph to add (university cost model).

@@
 
-Reproducible research and replication studies are essential components for the progress of evidence-based science, even more now when nearly all fields advance via computation.
+\IEEEPARstart{R}{eproducible} research and replication studies are essential components for the progress of evidence-based science, even more now when nearly all fields advance via computation.
 We use computer simulations and data models to create new knowledge,
@@
 Until just a few years ago, the products offered by cloud providers were unsuitable to the needs of computational scientists using HPC, due to performance overhead of virtualization and lack of support for fast networking.
-Azure only introduced nodes with GPU devices during late 2016 and Infiniband support for the NC-series in 2017.
+Azure only introduced nodes with GPU devices during late 2016 and Infiniband support for Linux virtual machines on the NC-series in 2017.
 Our first objective was to assess performance on cloud nodes for the type of computations in our research workflows with  tightly coupled parallel applications. 
@@
 The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (with a uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
-The grid is kept uniform in the $z$-direction and we enforce periodic conditions at the front and back boundaries.
+The grid is kept uniform in the $z$-direction with periodic boundary conditions.
 The simulation ran in a Docker container on Azure Batch using Batch Shipyard.
@@
 
-\section{Cost Analysis and Lessons Learned}\label{sec:cost}
+\section{Cost Analysis and User Experience}\label{sec:cost}
 
@@
 
+% Discuss cheaper options and university cost models (F&A).
+
 Running CFD simulations on Microsoft Azure was a first time for our research lab.
@@
 
-In a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
+\bigskip
+\IEEEPARstart{I}{n} a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
 The repository is found at \url{https://github.com/barbagroup/cloud-repro}.

### 2019-04-12 tex/MesnardoBarba2019.tex
Add snake cost with 3-yr-reserved instances
Cite Freniere et al. (2016)

@@
 The top concerns of researchers considering cloud computing are performance and cost. 
-Until just a few years ago, the products offered by cloud providers were unsuitable to the needs of computational scientists using HPC, due to performance overhead of virtualization and lack of support for fast networking.
+Until just a few years ago, the products offered by cloud providers were unsuitable to the needs of computational scientists using HPC, due to performance overhead of virtualization or lack of support for fast networking \cite{freniere_et_2016}.
 Azure only introduced nodes with GPU devices during late 2016 and Infiniband support for Linux virtual machines on the NC-series in 2017.
@@
 The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).
+(Note that with 3-year-reserved instances, the two- and three-dimensional snake simulations would have only cost $24.6$ and $478.1$ USD, respectively.)
 

### 2019-04-12 tex/MesnardoBarba2019.tex
Try to connect snake simus to overall cost

@@
 With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
-From May to December, we spent a total of $20,614$ USD to run simulations of the gliding snake.
+From May to December, we spent a total of $20,614$ USD to run CFD simulations, including a couple dozens of snake simulations.
+(The output of those simulations are now being processed to further analyze the complex flow dynamics generated behind the snake model.)
 During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).

### 2019-04-12 tex/MesnardoBarba2019.tex
Add more to conclusion

@@
 \bigskip
-\IEEEPARstart{I}{n} a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
+
+\IEEEPARstart{L}{ooking} for an alternative solution to university-managed HPC clusters to run CFD simulations with our in-house software, we leveraged the public cloud provider Microsoft Azure to generate reproducible computational results.
+Our reproducible workflow makes use of Docker containers to faithfully port the runtime environment our CFD application to Azure.
+We used the command-line utilities Azure-CLI and Batch Shipyard to run multi-instance tasks within Docker containers on the Azure Batch platform.
+Our CFD simulations ran on instances of the NC-series that feature NVDIDA K80 GPU devices and enable access to InfiniBand network.
+The benchmarks showed that we could get comparable runtimes between our university-managed HPC system and Microsoft Azure.
+Thanks to Microsoft Azure sponsorship, we have been able to run dozens of CFD simulations of a gliding snake's model.
+The study of the three-dimensional flow around a cylinder with an anatomically accurate cross-section of the flying snake is currently ongoing; output data from these runs are being analyzed and will be published in a later paper.
+
+In a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
 The repository is found at \url{https://github.com/barbagroup/cloud-repro}.
-
 Our expanded reproducibility packages contain input files, Batch Shipyard configuration files, command-line instructions to set up and submit jobs to Microsoft Azure, as well as the post-processing scripts to reproduce the figures of this paper.

### 2019-04-15 tex/MesnardoBarba2019.tex
fix typos

@@
 From May to December, we spent a total of $20,614$ USD to run CFD simulations, including a couple dozens of snake simulations.
-(The output of those simulations are now being processed to further analyze the complex flow dynamics generated behind the snake model.)
+(The output of those simulations is now being processed to further analyze the complex flow dynamics generated behind the snake model.)
 During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
@@
 Running CFD simulations on Microsoft Azure was a first time for our research lab.
-As novices in cloud computing, it took us several months to become familiar with the technical vocabulary and the infrastructure of Microsoft Azure before we could submit our first simulation of the snake.
+As novices in cloud computing, it took us several months to become familiar with the technical vocabulary and the infrastructure of Microsoft Azure before we could submit our first simulation of the flow around a snake profile.
 
@@
 With Batch Shipyard, we have painlessly submitted jobs on Azure Batch to run multi-instance tasks in Docker containers, everything from the command-line terminal on a local machine.
-Note that Bach Shipyard also supports Singularity containers.
+Note that Batch Shipyard also supports Singularity containers.
 
@@
 
-Microsoft Azure implements quotas and limits on resources with Azure Batch service, such as the maximum number of dedicated cores that can used in a certain region.
+Microsoft Azure implements quotas and limits on resources with Azure Batch service, such as the maximum number of dedicated cores that can be used in a certain region.
 To be able to run our simulations, we had to contact Azure Support through Azure Portal to request a quota increase for a given type of instances in a specific region and for a given subscription.
 We had to go through this process at least five times during our sponsorship period.
-The readers should be aware of these quotas and limits before scaling up workloads on Azure Batch.
+Readers should be aware of these quotas and limits before scaling up workloads on Azure Batch.
 

### 2019-04-15 tex/MesnardoBarba2019.tex
edit new conclusion paragraph

@@
 
-\IEEEPARstart{L}{ooking} for an alternative solution to university-managed HPC clusters to run CFD simulations with our in-house software, we leveraged the public cloud provider Microsoft Azure to generate reproducible computational results.
-Our reproducible workflow makes use of Docker containers to faithfully port the runtime environment our CFD application to Azure.
-We used the command-line utilities Azure-CLI and Batch Shipyard to run multi-instance tasks within Docker containers on the Azure Batch platform.
-Our CFD simulations ran on instances of the NC-series that feature NVDIDA K80 GPU devices and enable access to InfiniBand network.
-The benchmarks showed that we could get comparable runtimes between our university-managed HPC system and Microsoft Azure.
-Thanks to Microsoft Azure sponsorship, we have been able to run dozens of CFD simulations of a gliding snake's model.
-The study of the three-dimensional flow around a cylinder with an anatomically accurate cross-section of the flying snake is currently ongoing; output data from these runs are being analyzed and will be published in a later paper.
+\IEEEPARstart{E}{xploring} public cloud services as an alternative (or complementary) solution to university-managed HPC clusters to run CFD simulations with our in-house software, we used Microsoft Azure to generate reproducible computational results.
+Our reproducible workflow makes use of Docker containers to faithfully port the runtime environment of our CFD application to Azure,
+and the command-line utilities Azure-CLI and Batch Shipyard to run multi-instance tasks within Docker containers on the Azure Batch platform.
+We ran CFD simulations on instances of the NC-series that feature NVIDIA K80 GPU devices and have access to InfiniBand network.
+Latency and bandwidth micro-benchmarks show that our university-managed HPC system and Microsoft Azure can produce comparable runtimes.
+Thanks to a Microsoft Azure sponsorship, we were able to run dozens of CFD simulations of a gliding snake's model.
+Our study of the three-dimensional flow around a cylinder with an anatomically accurate cross-section of the flying snake is currently ongoing. 
+We plan to analyze the output data from these runs to be published in a later paper.
 

### 2019-04-16 tex/MesnardoBarba2019.tex
Remove hyphen in Azure CLI

@@
 We push to DockerHub a Docker image of our CFD application with all its dependencies.
-Azure-CLI is use to configure accounts on Microsoft Azure and to upload/download data to/from an Azure Storage account.
+Azure CLI is use to configure accounts on Microsoft Azure and to upload/download data to/from an Azure Storage account.
 With Batch Shipyard, we can create pool on Azure Batch and run container-based simulation using our Docker image.}
@@
 
-Command-line utilities such as Azure-CLI and Batch Shipyard were of great help to create and manage resources on Microsoft Azure for executing our reproducible research workflow.
+Command-line utilities such as Azure CLI and Batch Shipyard were of great help to create and manage resources on Microsoft Azure for executing our reproducible research workflow.
 (In our lab, we tend to avoid interacting directly with graphical-user interfaces to keep a trace of the commands run and make the workflow more reproducible.)
-Azure-CLI helped us set up the Azure Batch and Storage accounts as well as moving data between the cloud platform and our local machines.
+Azure CLI helped us set up the Azure Batch and Storage accounts as well as moving data between the cloud platform and our local machines.
 Thanks to Batch Shipyard, we did not have to dig into the software development kit of Azure Batch to use the service.
@@
 Our reproducible workflow makes use of Docker containers to faithfully port the runtime environment of our CFD application to Azure,
-and the command-line utilities Azure-CLI and Batch Shipyard to run multi-instance tasks within Docker containers on the Azure Batch platform.
+and the command-line utilities Azure CLI and Batch Shipyard to run multi-instance tasks within Docker containers on the Azure Batch platform.
 We ran CFD simulations on instances of the NC-series that feature NVIDIA K80 GPU devices and have access to InfiniBand network.

### 2019-04-16 tex/MesnardoBarba2019.tex
Fix typos and use correct words

@@
 It uses Docker containers to create an image of the application software stack.
-We also adopt several tools that facilitate creating and managing virtual machines with compute nodes and submitting jobs to these nodes.
+We also adopt several tools that facilitate creating and managing virtual machines on compute nodes and submitting jobs to these nodes.
 The configuration files for these tools are part of an expanded "reproducibility package" that includes workflow definitions for cloud computing, in addition to input files and instructions.
@@
 Containers allow re-creating the same runtime environment of an application (including all its dependencies) from one machine to another. 
-They empower researchers to share pre-built images of their software stack, ameliorating one of the biggest pain points for reproducible research: building the software in a different machine. 
+They empower researchers to share pre-built images of their software stack, ameliorating one of the biggest pain points for reproducible research: building the software on a different machine. 
 The majority of enterprise developers today are familiar with Docker container technology (first released six years ago). 
@@
 Azure CLI is use to configure accounts on Microsoft Azure and to upload/download data to/from an Azure Storage account.
-With Batch Shipyard, we can create pool on Azure Batch and run container-based simulation using our Docker image.}
+With Batch Shipyard, we create a pool on Azure Batch and run container-based simulation using our Docker image.}
     \label{fig:cloud_workflow}
@@
 
-To run computational jobs on Microsoft Azure, we use several tools that facilitate creating and managing virtual machines with compute nodes, and submitting jobs to those nodes.
+To run computational jobs on Microsoft Azure, we use several tools that facilitate creating and managing virtual machines on compute nodes, and submitting jobs to those nodes.
 We use a service called Azure Batch that leverages Microsoft Azure at no extra cost, relieving the user from manually creating, configuring, and managing an HPC-capable cluster of cloud nodes, including virtual machines, virtual networks, job and task scheduling infrastructure.
-Azure Batch works with both embarrassingly parallel workloads and tightly-coupled MPI jobs (the latter being the case of our CFD software).
+Azure Batch works with both embarrassingly parallel workloads and tightly coupled MPI jobs (the latter being the case of our CFD software).
 To use Azure Batch, we first need to configure a workspace on Microsoft Azure.
@@
 The folder \texttt{examples/snake2d2k35/config\_shipyard} in the repository accompanying this paper contains an example YAML files to create a pool of two \texttt{NC24r} compute nodes (featuring K80 GPUs and using InfiniBand network).
-Listing \ref{lst:shipyard_run} shows the commands to run from your local terminal to create a pool of compute nodes on Azure Batch and submit jobs to it.
+Listing \ref{lst:shipyard_run} shows the commands to run in your local terminal to create a pool of compute nodes on Azure Batch and submit jobs to it.
 During the pool creation (\texttt{shipyard pool add}), the Docker image of our CFD application is pulled from the registry to the virtual machines.
@@
 CFD algorithms often require solving linear systems with iterative methods.
-For example, the projection Navier-Stokes solver implemented in our software requires the solution of a Poisson system on every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
+For example, the projection Navier-Stokes solver implemented in our software requires the solution of a Poisson system at every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
 We investigated the time-to-solution for a three-dimensional Poisson system (obtained with a 7-point stencil central-difference scheme) on different nodes of Microsoft Azure and Colonial One.
@@
 We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
-The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) iwassolved on a single compute node using $12$ MPI processes and $2$ GPU devices; we then doubled the mesh size as we doubled the number of nodes (keeping the same number of MPI processes and GPUs per node).
+The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) was solved on a single compute node using $12$ MPI processes and $2$ GPU devices; we then doubled the mesh size as we doubled the number of nodes (keeping the same number of MPI processes and GPUs per node).
 The number of iterations to reach convergence increases with the size of the system, so we normalize the runtimes by the number of iterations.
@@
 To study the flow around the flying snake, we developed a CFD software called PetIBM\cite{chuang_et_al_2018}, an open-source toolbox that solves the two- and three-dimensional incompressible Navier-Stokes equations using a projection method (seen as an approximate block-LU decomposition of the fully discretized equations\cite{perot_1993}) and an immersed-boundary method (IBM).
-Within this framework, the fluid equations are solved over a extended grid that does not conform to the surface of the immersed body.
+Within this framework, the fluid equations are solved over an extended grid that does not conform to the surface of the immersed body.
 To model the presence of the body, the momentum equation is augmented with a forcing term that is activated in the vicinity of the immersed boundary.
 This technique allows the use of simple fixed structured Cartesian grids to solve the equations.
-PetIBM also implements immersed boundary methods (IBMs) that fit into the projection method; in the present study, we use the IBM scheme proposed in \cite{li_et_al_2016}.
+PetIBM implements immersed boundary methods (IBMs) that fit into the projection method; in the present study, we use the IBM scheme proposed in \cite{li_et_al_2016}.
 PetIBM runs on distributed-memory architectures using the efficient data structures and parallel routines from the PETSc library.
@@
 Although the two-dimensional simulations can give us some insights into to flow dynamics happening in the wake behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional structures will develop in the wake.
-We submitted jobs on Azure Batch to perform direct numerical simulation of the three-dimensional flow around a snake model: a cylinder with the an anatomically accurate cross-section.
+We submitted jobs on Azure Batch to perform direct numerical simulation of the three-dimensional flow around a snake model: a cylinder with the same anatomically accurate cross-section.
 The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (with a uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
@@
 Fig. \ref{fig:wz_avg_3d} shows the instantaneous spanwise vorticity averaged along the $z$-direction after $80$ and $100$ time units.
-Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von Karman street exhibits a narrower wake than in the two-dimensional simulations.
+Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von K\'{a}rm\'{a}n street exhibits a narrower wake than in the two-dimensional simulations.
 We also note the presence of an unsteady recirculation region just behind the snake cylinder, and alternating regions of positive and negative cross-flow velocity showing the presence of von Karman vortices (Fig.
@@
     \includegraphics[width=8cm]{figures/wz_avg_multi_contourf.png}
-    \caption{Filled contour of the spanwise-averaged z-component of the vorticity ($-5 \leq w_z c / U_\infty \leq 5$) field after $80$ and $100$ time units of three-dimensional flow simulation with PetIBM for the snake cylinder with a cross-section at a $35$-degree angle of attack and Reynolds number $2000$.}
+    \caption{Filled contour of the spanwise-averaged z-component of the vorticity ($-5 \leq w_z c / U_\infty \leq 5$) field after $80$ and $100$ time units of a three-dimensional flow simulation with PetIBM for the snake cylinder with a cross-section at a $35$-degree angle of attack and Reynolds number $2000$.}
     \label{fig:wz_avg_3d}
@@
 These files contain details about all the libraries needed to create the computational runtime environment.
-We even included a Dockerfile to reproduce the local environment with the visualization tools needed for post-processing.
+We even include a Dockerfile to reproduce the local environment with the visualization tools needed for post-processing.
 In addition, we have also deposited in the Zenodo service all secondary data required to reproduce the figures of the paper without running the simulations again.

### 2019-04-16 tex/MesnardoBarba2019.tex
Add paragraph about low-priority VMs
Also:

* Add low-priority pricing for the NC-series to the table.

@@
     \centering
-    \begin{tabular}{cccccccc}
-        Instance & cores & RAM & disk sizes & GPU & pay-as-you-go & 1-year reserved & 3-year reserved \\
-        && (GiB) & (Gib) && (\$/hr) & (\$/hr) & (\$/hr) \\
+    \begin{tabular}{ccccccccc}
+        Instance & cores & \begin{tabular}{@{}c@{}}RAM \\ (GiB) \end{tabular} & \begin{tabular}{@{}c@{}}disk sizes \\ (GiB) \end{tabular} & GPU & \begin{tabular}{@{}c@{}c@{}}pay-as-you-go \\ (dedicated) \\ (\$/hr) \end{tabular} & \begin{tabular}{@{}c@{}c@{}}pay-as-you-go \\ (low-priority) \\ (\$/hr) \end{tabular} & \begin{tabular}{@{}c@{}}1-year reserved \\ (\$/hr) \end{tabular} & \begin{tabular}{@{}c@{}}3-year reserved \\ (\$/hr) \end{tabular} \\
         \hline
-        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.5733 & 0.3996 \\
-        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 1.1466 & 0.7991 \\
-        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.2932 & 1.5981 \\
-        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.5224 & 1.7578 \\
+        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.18 & 0.5733 & 0.3996 \\
+        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 0.36 & 1.1466 & 0.7991 \\
+        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 0.72 & 2.2932 & 1.5981 \\
+        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 0.792 & 2.5224 & 1.7578 \\
         \hline
@@
 As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.
+
+Microsoft Azure offers the possibility to take advantage of surplus capacity with ``low-priority'' virtual machines that are significantly cheaper than ``dedicated'' ones (\ref{tab:nc_series}).
+For example, the low-priority \texttt{NC24r} instance has an hourly cost of $0.792$ USD, $5$ times cheaper than its dedicated counterpart.
+However, the reader should keep in mind that low-priority may not be available for allocation or may be preempted at any time.
+In fact, low-priority instances should be avoided for long-running MPI jobs in pools where inter-node communication is enabled.
+We only used dedicated virtual machines to run our CFD software.
+Moreover, our job tasks used a shared filesystems (GlusterFS on compute nodes) for I/O operations and Batch Shipyard will fail to create the pool if low-priority nodes are requested.
 

### 2019-04-16 tex/MesnardoBarba2019.tex
Add edits with @labarba

@@
 The configuration files for these tools are part of an expanded "reproducibility package" that includes workflow definitions for cloud computing, in addition to input files and instructions.
-This facilitates re-creating the cloud environment to re-un the simulations under the same conditions.
+This facilitates re-creating the cloud environment to re-run the computations under the same conditions.
 \end{abstract}
@@
 This promises to greatly facilitate code development, debugging, and testing. Resources allocated on the cloud are released as soon as the job is done, avoiding paying for idle time.
-On a public-cloud platform with a "pay-as-you-go" type of subscription---such as Microsoft Azure, Google Cloud, Amazon AWS---a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters.
+On a public-cloud platform---such as Microsoft Azure, Google Cloud, Amazon AWS---with a "pay-as-you-go" type of subscription, a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters.
 Cost models that make sense for researchers, labs, and universities are still unclear. 
 Yet, this information is key when making a decision to adopt a cloud workflow for research. 
-We report here what we have learned from nearly two years of using cloud computing for our simulation-based workflow, with the hope that it will shed some light on the costs and benefits, and help others considering using cloud computing for their research.
+We report here what we have learned from nearly two years of using cloud computing for our computational fluid dynamics (CFD) simulations, with the hope that it will shed some light on the costs and benefits, and help others considering using cloud computing for their research.
 
@@
 Scientific publications reporting computational results often lack sufficient details to reproduce the researcher's computational environment; e.g., they may miss to mention external libraries used along with the main computational code.
-We have learned the hard way how even different versions of the same external library can alter the numerical results and even the scientific findings of a computational study\cite{mesnard_barba_2017}.
-This section presents an overview and mini-tutorial of the workflow we developed to guarantee the highest level of reproducibility of our computational research, with the best available technology solutions.
+We have learned the hard way how different versions of the same external library can alter the numerical results and even the scientific findings of a computational study\cite{mesnard_barba_2017}.
+This section presents an overview and mini-tutorial of the workflow we developed to aim for the highest level of reproducibility of our computational research, with the best available technology solutions.
 In the process of creating this reproducible workflow, we also evaluated the suitability of public cloud offerings by Microsoft Azure for our research computing needs. 
@@
 
-\begin{figure*}[b]
+\begin{figure*}[t]
     \centering
@@
 This can be done either via the Azure Portal in a web browser or from a local terminal using the open-source tool Azure CLI.\footnote{Azure CLI (version 2.0.57): \url{https://github.com/Azure/azure-cli}}
-We prefer to use the command-line solution (program \texttt{az}), as it allows us to keep track of the steps taken to configure the Azure workspace (see Listing \ref{lst:az_configure}).
+We prefer to use the command-line solution (program \texttt{az}), as it allows us to keep track of the steps taken to configure the cloud workspace (see Listing \ref{lst:az_configure}).
 First, we set the Azure subscription we want to use (let's call it \texttt{reprosubscription}).
-Next, we create a resource group, \texttt{reprorg}, located in this case in the East US region, which will contain all the Azure resources.
-We create an Azure Storage account, \texttt{reprostorage}, in the resource group, as well as an Azure Batch account, \texttt{reprobatch}, associated to the storage account.
+Next, we create a resource group (\texttt{reprorg}) located in this case in the East US region, which will contain all the Azure resources.
+We create an Azure Storage account (\texttt{reprostorage}) in the resource group, as well as an Azure Batch account (\texttt{reprobatch}) associated to the storage account.
 Finally, we create a fileshare (in this case of size $100$ GB) in the storage.
@@
 Listing \ref{lst:shipyard_run} shows the commands to run in your local terminal to create a pool of compute nodes on Azure Batch and submit jobs to it.
-During the pool creation (\texttt{shipyard pool add}), the Docker image of our CFD application is pulled from the registry to the virtual machines.
-With \texttt{shipyard data ingress}, we can upload input files to the compute nodes.
-Once created, we submit jobs to the pool (\texttt{shipyard jobs add}); the tasks for a job will start automatically.
+The Docker image of our CFD application is pulled from the registry to the virtual machines during the pool creation (\texttt{shipyard pool add}).
+We then upload the input files to the compute nodes (\texttt{shipyard data ingress}) and submit jobs to the pool (\texttt{shipyard jobs add}).
+The tasks for a job will start automatically upon submission.
 
-\begin{lstlisting}[label=lst:shipyard_run,caption={Create a pool with Batch Shipyard and submit jobs to it.}]
+\begin{lstlisting}[label=lst:shipyard_run,caption={Create a pool and submit jobs to it.}]
 $ cd $CLOUDREPRO/examples/snake2d2k35
@@
     \renewcommand{\arraystretch}{1.5}
-    \caption{Hardware Specifications of Nodes Used on Microsoft Azure and Colonial One.
-On Both Platforms, MPI Applications Take Advantage of RDMA (Remote Direct Memory Access) Network with FDR InfiniBand.}
+    \caption{Hardware specifications of nodes used on Microsoft Azure and Colonial One.
+On both platforms, MPI applications take advantage of RDMA (Remote Direct Memory Access) network with FDR InfiniBand.}
     \label{tab:hw_specs}
@@
 For all message sizes, a higher bandwidth rate was achieved on Azure.
-Over the last few years, Microsoft Azure has improved its HPC solution to provide networking capabilities that are comparable or even better than our 6-year-old university-managed cluster.
+Over the last few years, Microsoft Azure has indeed improved its HPC solutions to provide networking capabilities that are comparable or even better than our 6-year-old university-managed cluster.
 
@@
 CFD algorithms often require solving linear systems with iterative methods.
-For example, the projection Navier-Stokes solver implemented in our software requires the solution of a Poisson system at every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
+For example, the Navier-Stokes solver implemented in our software requires the solution of a Poisson system at every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
 We investigated the time-to-solution for a three-dimensional Poisson system (obtained with a 7-point stencil central-difference scheme) on different nodes of Microsoft Azure and Colonial One.
@@
 In that regard, PetIBM is open source, version-controlled on GitHub,\footnote{PetIBM (version 0.4): \url{https://github.com/barbagroup/PetIBM}} and shared under the permissive (non copy-left) BSD-3 clause license.
+We also provide a Docker image of PetIBM on DockerHub and its Dockerfile is available in the GitHub repository of the software.
 
@@
 
-We submitted a job on Azure Batch (via Batch Shipyard,) to compute the two-dimensional flow around an anatomically accurate sectional shape of the gliding snake.
+We submitted a job on Azure Batch (with Batch Shipyard,) to compute the two-dimensional flow around an anatomically accurate sectional shape of the gliding snake.
 The cross-section has a chord-length $c=1$ and forms a $35$-degree angle of attack with the incoming freestream flow.
@@
 The immersed boundary is centered in a $30c \times 30c$ computational domain that contains just over $2.9$ million cells.
-The grid is kept uniform with the highest resolution in the vicinity of the body and stretched to the external boundaries with a constant ratio (see Table \ref{tab:grid_specs} for details about the grid).
-For the immersed boundary, the same grid resolution than the background fluid grid was applied.
+The grid is uniform with the highest resolution in the vicinity of the body and stretched to the external boundaries with a constant ratio (see Table \ref{tab:grid_specs} for details about the grid).
+The discretization of the immersed boundary has the same resolution as the background fluid grid.
 A convective condition was used at the outlet boundary while freestream conditions were enforced on the three other boundaries.
@@
     \caption{Filled contour of the vorticity field ($-5 \leq w_z c / U_\infty \leq 5$) after $20$, $44$, $45$, and $80$ time units of flow simulation with PetIBM for the snake cross-section at a $35$-degree angle of attack and Reynolds number $2000$.
-Vortex merging events are responsible for the change in the wake signature and the drop in the mean value of the lift coefficient.}
+Vortex merging events trigger a change in the wake signature causing the drop in the mean value of the lift coefficient.}
     \label{fig:wz_2d}
@@
 We submitted jobs on Azure Batch to perform direct numerical simulation of the three-dimensional flow around a snake model: a cylinder with the same anatomically accurate cross-section.
-The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (with a uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
-The grid is kept uniform in the $z$-direction with periodic boundary conditions.
-The simulation ran in a Docker container on Azure Batch using Batch Shipyard.
+The computational domain extends in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (with a uniform discretization in the $z$-direction and periodic boundary conditions; see Table \ref{tab:grid_specs}).
 The job was submitted to a pool of two \texttt{NC24r} nodes using $24$ MPI processes and $4$ GPU devices per node.
@@
     \includegraphics[width=18cm]{figures/qcrit_wx_wake3d_0020.png}
-    \caption{Lateral view of the isosurfaces of the Q-criterion ($Q = 1.0$) in the wake of the snake cylinder (with a $35$-degree angle of attack) at Reynolds number $2000$.
+    \caption{Lateral view of the isosurfaces of the Q-criterion ($Q = 1$) in the wake of the snake cylinder (with a $35$-degree angle of attack) at Reynolds number $2000$.
 The isosurfaces are colored with the streamwise vorticity ($-5 \leq w_x c / U_\infty \leq 5$).
@@
 
-For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
+For the year $2018$, Microsoft Azure granted our research lab a sponsorship (in terms of cloud credits) to run CFD simulations with our in-house software.
 With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
@@
 
-Microsoft Azure offers the possibility to take advantage of surplus capacity with ``low-priority'' virtual machines that are significantly cheaper than ``dedicated'' ones (\ref{tab:nc_series}).
-For example, the low-priority \texttt{NC24r} instance has an hourly cost of $0.792$ USD, $5$ times cheaper than its dedicated counterpart.
-However, the reader should keep in mind that low-priority may not be available for allocation or may be preempted at any time.
-In fact, low-priority instances should be avoided for long-running MPI jobs in pools where inter-node communication is enabled.
-We only used dedicated virtual machines to run our CFD software.
-Moreover, our job tasks used a shared filesystems (GlusterFS on compute nodes) for I/O operations and Batch Shipyard will fail to create the pool if low-priority nodes are requested.
+Microsoft Azure offers the possibility of taking advantage of surplus capacity with ``low-priority'' virtual machines that are substantially cheaper than ``dedicated'' ones (\ref{tab:nc_series}).
+For example, the low-priority \texttt{NC24r} instance costs $0.792$ USD per hour, $5$ times cheaper than its dedicated counterpart.
+The reader should keep in mind that low-priority virtual machines may not be available for allocation or may be preempted at any time.
+Thus, low-priority instances should be avoided for long-running MPI jobs in pools where inter-node communication is enabled.
+We only used dedicated virtual machines to run our CFD simulations.
+Moreover, our job tasks used a shared filesystem (GlusterFS on compute nodes) for I/O operations and Batch Shipyard would fail to create the pool if low-priority nodes were requested.
 
@@
 We ran CFD simulations on instances of the NC-series that feature NVIDIA K80 GPU devices and have access to InfiniBand network.
-Latency and bandwidth micro-benchmarks show that our university-managed HPC system and Microsoft Azure can produce comparable runtimes.
+Latency and bandwidth micro-benchmarks show that our university-managed HPC system and Microsoft Azure can deliver similar performances.
 Thanks to a Microsoft Azure sponsorship, we were able to run dozens of CFD simulations of a gliding snake's model.
 Our study of the three-dimensional flow around a cylinder with an anatomically accurate cross-section of the flying snake is currently ongoing. 
-We plan to analyze the output data from these runs to be published in a later paper.
+We plan to analyze the output data from these runs, and publish them in a later paper.
 
@@
 CCF-1747669.
+We would like to thank Kenji Takeda, Fred Park, and Joshua Poulson of Microsoft for their help.
 

### 2019-04-16 tex/MesnardoBarba2019.tex
new text mentioning F&A costs

@@
 Universities and national laboratories spend millions of dollars to deploy and maintain on-site high-performance computing (HPC) clusters.
-At the George Washington University, we have access to a university-managed HPC cluster called Colonial One.
+At the George Washington University, we have access to a cluster called Colonial One.
 The cluster is now $6$ years old and approaching its end-of-life.
@@
 
+In this work, we show that public cloud resources are today able to deliver similar performances to a university-managed cluster, and thus can be regarded as a suitable solution for research computing.
+But in addition to performance, researchers also worry about cost.
+We share the actual costs incurred to run two- and three-dimensional CFD simulations  using cloud services with a pay-as-you-go model, and report on reduced costs possible with reserved instances.
+Universities (and possibly funding agencies) may obtain even more favorable pricing through bids or medium-term contracts.
+Researchers thinking of adding cloud computing to proposal budgets might encounter other barriers, however.
+For example, some universities exempt large equipment purchases from indirect (facilities and administrative, F\&A)  costs, while they may add these overhead rates to cloud purchases. 
+Until these internal policies are adjusted, cloud computing may not be adopted widely.
+
 In a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.

### 2019-04-16 tex/MesnardoBarba2019.tex
Add Zenodo archive citation

@@
 We even include a Dockerfile to reproduce the local environment with the visualization tools needed for post-processing.
-In addition, we have also deposited in the Zenodo service all secondary data required to reproduce the figures of the paper without running the simulations again.
+In addition, we have also deposited in the Zenodo service all secondary data required to reproduce the figures of the paper without running the simulations again\cite{cloud_repro_2019}.
 

### 2019-04-16 misc/rsync4zenodo.sh
Add Zenodo DOI to README

@@ -11,7 +11,7 @@ destdir=$rootdir/zenodo
 
 mkdir -p $destdir
 
-rsync -av --files-from=$listpath $rootdir $destdir
+rsync -av --files-from=$listpath --delete $rootdir $destdir
 
 rm -f $listpath
 

### 2019-07-29 tex/MesnardoBarba2019.tex
Fix typo in URL in footnote

@@
 Listing \ref{lst:docker_build_push} provides the command lines to build (\texttt{docker build}) and push (\texttt{docker push}) an image of our CFD software (\texttt{barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu}) that we used to obtain some of the results presented in the next section.
-Here, \texttt{CLOUDREPRO} is an environment variable set to the local path of the GitHub repository for this paper, \texttt{cloud-repro},\footnote{\url{https://github.com/barbargroup/cloud-repro}} cloned on the user's machine.
+Here, \texttt{CLOUDREPRO} is an environment variable set to the local path of the GitHub repository for this paper, \texttt{cloud-repro},\footnote{\url{https://github.com/barbagroup/cloud-repro}} cloned on the user's machine.
 

### 2019-07-29 tex/MesnardoBarba2019.tex
Fix typo "relatively" -> "relative"

@@
     \caption{Time-averaged force coefficients on the snake model at Reynolds number $2000$ and angle of attack $35^o$ for the two- and three-dimensional configurations.
-(We average the force coefficients between $40$ and $80$ time units of flow simulation and report the relatively difference of the 2D values with respect to the 3D ones.)}
+(We average the force coefficients between $40$ and $80$ time units of flow simulation and report the relative difference of the 2D values with respect to the 3D ones.)}
     \label{tab:force_coefficients}

### 2019-08-02 tex/MesnardoBarba2019.tex
Properly reference Table 5 of the manuscript

@@
 
-Microsoft Azure offers the possibility of taking advantage of surplus capacity with ``low-priority'' virtual machines that are substantially cheaper than ``dedicated'' ones (\ref{tab:nc_series}).
+Microsoft Azure offers the possibility of taking advantage of surplus capacity with ``low-priority'' virtual machines that are substantially cheaper than ``dedicated'' ones (see Table \ref{tab:nc_series} for pricing options on the NC series with Linux-based virtual machines).
 For example, the low-priority \texttt{NC24r} instance costs $0.792$ USD per hour, $5$ times cheaper than its dedicated counterpart.

### 2019-08-06 tex/MesnardoBarba2019.tex
Remove ambiguous sentence; make intention more explicit

@@
 \noindent Anyone can now pull the application image from DockerHub, and create a Docker container to run the CFD application software in a faithfully reproduced local environment.
-The great advantage of container technology is that the same container that was built and tested on the developer's local machine can now run at scale in production mode on virtual machines, bare metal, or even cloud platforms.
-Our objective is to create and run containers on a public cloud provider such as Microsoft Azure.
+Our objective is to create and run containers on the public cloud provider Microsoft Azure, and make it possible for the readers to also run these containers to reproduce our results.
 Figure \ref{fig:cloud_workflow} shows a graphical representation of the workflow we developed using Docker and various tools for running CFD simulations on Microsoft Azure.

### 2019-08-06 tex/MesnardoBarba2019.tex
Mention Docker images built for Azure
Change "anyone" to "the reader"

@@
 
-\noindent Anyone can now pull the application image from DockerHub, and create a Docker container to run the CFD application software in a faithfully reproduced local environment.
+\noindent A reader interested in reproducing the computational results can now pull the application image from DockerHub, and create a Docker container to run the CFD application software in a faithfully reproduced local environment.
 Our objective is to create and run containers on the public cloud provider Microsoft Azure, and make it possible for the readers to also run these containers to reproduce our results.
@@
 Thus, we used Azure instances of the NC-series, which feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over InfiniBand network.
+The Docker images were specifically built to be able to run MPI applications on RDMA-capable virtual machines (such as the NC24r instance with a CentOS-based 7.3 HPC image) with multiple-instance tasks on Azure Batch service.
 As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.

### 2019-08-06 tex/MesnardoBarba2019.tex
Add ppn and num GPU per node for Poisson benchmark
Add information about the number of MPI processes and the number of GPU devices
used per node for the Poisson benchmark.

@@
     \includegraphics[width=8cm]{figures/poisson_time_vs_nodes.pdf}
-    \caption{Runtimes to solve a Poisson system on Colonial One and on Microsoft Azure.
-Benchmark was repeated 5 times and we report the mean runtimes as well as the extrema.
-Poisson system was solved on Azure using PETSc on \texttt{H16r} nodes and using AmgX on \texttt{NC24r} nodes.
-On Colonial One, we solved the system with PETSc on \texttt{Short} nodes and with AmgX on \texttt{Ivygpu} nodes.
+    \caption{Runtime to solve a Poisson system on Colonial One and on Microsoft Azure.
+Benchmark was repeated 5 times and we report the mean runtime as well as the extrema.
+Poisson system was solved on Azure using PETSc on \texttt{H16r} nodes ($16$ processes per node) and using AmgX on \texttt{NC24r} nodes ($12$ processes and $1$ NVIDIA K80 GPU per node).
+On Colonial One, we solved the system with PETSc on \texttt{Short} nodes ($16$ processes per node) and with AmgX on \texttt{Ivygpu} nodes ($12$ processes and $2$ NVIDIA K20 GPUs per node).
 The runs with PETSc solved a Poisson system on a mesh size of 50 million cells (top).

### 2019-08-06 tex/MesnardoBarba2019.tex
Add description about Singularity containers

@@
 Note that Batch Shipyard also supports Singularity containers.
+Singularity is an open source container platform designed for HPC workloads.
+Singularity containers can be used on traditional HPC clusters such as Colonial One; Docker containers usually cannot.
+Indeed, running a Docker container involves running a Docker daemon (a background process) which requires root privileges (that users do not and should not have on production clusters).
+The container technology from Singularity was designed from the ground up to prevent escalation in user privileges.
 

### 2019-08-08 tex/MesnardoBarba2019.tex
Add sentences to abstract and introduction
Abstract:

* Mention that our workflow is for Microsoft Azure.
* Mention we provide evidence to support cloud computing as an alternative to HPC clusters.

Introduction:

* Mention we build on the work of Boettiger.
* Add additional paragraph to highlight contributions.

@@
 \begin{abstract}
-In a new effort to make our research transparent and reproducible by others, we developed a workflow to run computational studies on a public cloud.
+In a new effort to make our research transparent and reproducible by others, we developed a workflow to run and share computational studies on the public cloud Microsoft Azure.
 It uses Docker containers to create an image of the application software stack.
@@
 This facilitates re-creating the cloud environment to re-run the computations under the same conditions.
+Although cloud providers have improved their offerings, many researchers using high-performance computing (HPC) are still skeptical about using cloud computing.
+Thus, we ran benchmarks for tightly coupled applications to confirm that the latest HPC nodes of Microsoft Azure are indeed a viable alternative to traditional on-site HPC clusters.
+We also show that cloud offerings are now adequate to complete computational fluid dynamics studies with in-house research software that uses parallel computing with GPUs.
+Finally, we share with the community what we have learned from nearly two years of using Azure cloud to enhance transparancy and reproducibility in our computational simulations.
 \end{abstract}
@@
 Container technology like Docker is a recent addition to the reproducibility toolbox \cite{boettiger_2015}. 
-In this work, we develop and assess a workflow for reproducible research on a public cloud, adopting Docker containers and several other tools to automate and fully document scientific computations.
+In this work, we develop and assess a workflow for reproducible research on the public cloud provider Microsoft Azure, adopting Docker containers and several other tools to automate and fully document scientific computations.
+The workflow follows the idea of using container technologies to enhance transparency and reproducibility, and to reduce the burden of installing our application software stack, for readers interested in re-doing the analysis under the same conditions.
+We go one step further by moving the computational work to Azure cloud resources using tools that programmatically capture the virtual environment configuration.
+The configuration files become part of expanded "reproducibility packages" for the study.
 
@@
 Yet, this information is key when making a decision to adopt a cloud workflow for research.
-We report here what we have learned from nearly two years of using cloud computing for our computational fluid dynamics (CFD) simulations, with the hope that it will shed some light on the costs and benefits, and help others considering using cloud computing for their research.
+
+Until recently, public cloud offerings were inadequate to the needs of computational scientists using HPC, mainly due to performance overhead of virtualization or lack of support for fast networking \cite{freniere_et_2016} and hardware accelerators.
+Freniere and co-authors (2016) used the OSU micro-benchmark suite to report performance degradation in networking with Amazon AWS, compared to their on-site local HPC cluster.
+We take the same approach with Microsoft Azure to verify that their improved services are now suitable for HPC applications.
+We also share what we have learned from nearly two years of using cloud computing for our computational fluid dynamics (CFD) simulations, with the hope that it will shed some light on the costs and benefits, and help others considering using cloud computing for their research.
 

### 2019-08-12 tex/MesnardoBarba2019.tex
[intro] add text on limitations re. portability

@@
 In this work, we develop and assess a workflow for reproducible research on the public cloud provider Microsoft Azure, adopting Docker containers and several other tools to automate and fully document scientific computations.
-The workflow follows the idea of using container technologies to enhance transparency and reproducibility, and to reduce the burden of installing our application software stack, for readers interested in re-doing the analysis under the same conditions.
+The workflow follows the idea of using container technology to enhance transparency and reproducibility, and to reduce the burden of installing our application software stack.
 We go one step further by moving the computational work to Azure cloud resources using tools that programmatically capture the virtual environment configuration.
 The configuration files become part of expanded "reproducibility packages" for the study.
+This work does not target portability of our software and workflow to diverse high-performance computing (HPC) environments. 
+Our goal is, rather, to publish our computational research with deep transparency. 
+The workflow we developed and document here is expressly designed for Azure  cloud offerings. 
+An interested reader could thus re-run our simulations under exactly the same conditions as we used, provided they are willing and able to create an Azure account.
 
-Universities and national laboratories spend millions of dollars to deploy and maintain on-site high-performance computing (HPC) clusters.
+Universities and national laboratories spend millions of dollars to deploy and maintain on-site HPC clusters.
 At the George Washington University, we have access to a cluster called Colonial One.

### 2019-08-14 tex/MesnardoBarba2019.tex
Re-arrange last paragraph (conclusion) and add NASEM citation
* Re-arrange last paragraph of the conclusion to mention limitation.
* Add reference to NASEM in introduction and last paragraph of the conclusion.

@@
 The term ``replication'' has been adopted to refer to an independent study generating new data which, when analyzed, lead to the same findings \cite{peng_2011}.
-We follow this convention, adopted also recently in a report from the National Academies of Sciences, Engineering, and Medicine \cite{nasa_oss_2018}.
+We follow this convention, adopted also recently in reports from the National Academies of Sciences, Engineering, and Medicine \cite{nasa_oss_2018,nasem_2019}.
 
@@
 
-In a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
-The repository is found at \url{https://github.com/barbagroup/cloud-repro}.
+In a heightened effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
+The repository is found at \url{https://github.com/barbagroup/cloud-repro} and is also permanently archived in Zenodo \cite{cloud_repro_2019}.
 Our expanded reproducibility packages contain input files, Batch Shipyard configuration files, command-line instructions to set up and submit jobs to Microsoft Azure, as well as the post-processing scripts to reproduce the figures of this paper.
+We included in the Zenodo archive all secondary data required to reproduce the figures without running the simulations again.
 Although they are not required to reproduce the computations, the Dockerfiles to build Docker images are also made available. 
+We even include a Dockerfile to reproduce the local environment with the visualization tools needed for post-processing.
 These files contain details about all the libraries needed to create the computational runtime environment. 
-We even include a Dockerfile to reproduce the local environment with the visualization tools needed for post-processing.
-In addition, we have also deposited in the Zenodo service all secondary data required to reproduce the figures of the paper without running the simulations again\cite{cloud_repro_2019}.
+Both the Dockerfiles and the workflow files may not execute as they were designed to do in a period of a few years, due to technology changes.
+Obsolescence of digital research objects, including software libraries and computational environments, is an acknowledged source of non-reproducibility, in the long run. 
+The recent report of the National Academies highlights this \cite[p.~57]{nasem_2019}. 
+Indeed, tools in our workflow that we have no control over (Azure CLI, Batch Shipyard) will likely change, and perhaps not be backwards compatible. 
+That is inevitable. 
+But when they do, our fully documented workflow (via human-readable configuration files) will continue to offer transparency of what we did and how we did it.
 

### 2019-08-14 tex/MesnardoBarba2019.tex
Add word "ideally" for reproducibility requirement

@@
 The software also implements the possibility to solve linear systems on multiple GPU devices distributed across the nodes with the NVIDIA AmgX library and our AmgXWrapper\cite{chuang_barba_2017}.
-One of the requirements for reproducible computational results is to make the code available under a public license (allowing reuse and modification by others).
+One of the requirements for reproducible computational results is to make the code available under a public license (ideally allowing reuse and modification by others).
 In that regard, PetIBM is open source, version-controlled on GitHub,\footnote{PetIBM (version 0.4): \url{https://github.com/barbagroup/PetIBM}} and shared under the permissive (non copy-left) BSD-3 clause license.

### 2019-08-14 tex/MesnardoBarba2019.tex
Add references to reviewers' comments
Mention ECC-enabled in caption of Table 1

@@
     \caption{Hardware specifications of nodes used on Microsoft Azure and Colonial One.
-On both platforms, MPI applications take advantage of RDMA (Remote Direct Memory Access) network with FDR InfiniBand.}
+On both platforms, MPI applications take advantage of RDMA (Remote Direct Memory Access) network with FDR InfiniBand and ECC is enabled for GPU computing.}
     \label{tab:hw_specs}
@@
 We would like to thank Kenji Takeda, Fred Park, and Joshua Poulson of Microsoft for their help.
+We are also immensely grateful to the reviewers, Patrick O'Leary \cite{oleary_2019} and Freddie Witherden \cite{witherden_2019}, for their suggestions.
 

### 2019-08-14 misc/listfiles4zenodo.py
Ignore ipynb_checkpoints for Zenodo files

@@ -6,7 +6,7 @@ import pathlib
 scriptdir = pathlib.Path(__file__).absolute().parent
 rootdir = scriptdir.parent
 
-excludes = ['.git', '.vscode', '__pycache__',
+excludes = ['.git', '.vscode', '__pycache__', '.ipynb_checkpoints',
             '.xmf', '.pyc',
             'credentials.yaml', 'id_rsa', 'l_mpi_2017.2.174.tgz']
 

### 2019-08-14 misc/independence/helper.py
Add Notebook with results on fine and coarse grids

@@ -1,0 +1,75 @@
+"""Module with functions for aerodynamic forces."""
+
+import pathlib
+import numpy
+
+
+def read_forces(*filepaths):
+    """Read PetIBM forces from given file(s).
+
+    If multiple files are provided, the histories are concatenated.
+    Parameters
+    ----------
+    filepaths : tuple of pathlib.Path objects or strings
+        Path of the files to load the history from.
+
+    Returns
+    -------
+    data : numpy.ndarray
+        Time followed by the forces in the x, y, and z directions.
+
+    """
+    if type(filepaths) in [str, pathlib.Path]:
+        filepaths = [filepaths]
+    for i, filepath in enumerate(filepaths):
+        with open(filepath, 'r') as infile:
+            subdata = numpy.loadtxt(infile, unpack=True)
+        if i == 0:
+            data = subdata
+        else:
+            data = numpy.concatenate((data, subdata), axis=1)
+        _, mask = numpy.unique(data[0], return_index=True)
+    return numpy.array([subdata[mask] for subdata in data])
+
+
+def get_force_coefficients(*forces, coeff=1.0):
+    """Convert forces to force coefficients.
+
+    Parameters
+    ----------
+    forces : tuple of numpy.ndarray objects
+        The forces.
+    coeff : float (optional)
+        The scaling coefficient; default: 1.0.
+
+    Returns
+    -------
+    force_coeffs : tuple of numpy.ndarray objects
+        The force coefficients.
+
+    """
+    force_coeffs = (coeff * f for f in forces)
+    return force_coeffs
+
+
+def get_time_averaged_values(t, *forces, limits=(-numpy.infty, numpy.infty)):
+    """Compute the time-averaged values.
+
+    Parameters
+    ----------
+    t : numpy.ndarray object
+        The time values.
+    forces : tuple of numpy.ndarray objects
+        The forces (or force coefficients).
+    limits : tuple of 2 floats (optional)
+        Time limits used to compute the mean; default: (-inf, +inf).
+
+    Returns
+    -------
+    means : tuple of floats
+        The time-averaged values.
+
+    """
+    mask = (t >= limits[0]) & (t <= limits[1])
+    means = (numpy.mean(f[mask]) for f in forces)
+    return means

### 2019-08-14 misc/independence/runs/snake3d2k35-coarse/config/deploynode.sh

@@ -1,0 +1,23 @@
+#!/bin/bash
+# Deploy one NC24 VM on Azure
+
+RESOURCE_GROUP="snakenc24-rg"
+VM_NAME="master"
+LOCATION="southcentralus"
+DNS_NAME="snakenc24"
+
+az group create \
+  --name ${RESOURCE_GROUP} \
+  --location ${LOCATION}
+
+az vm create \
+  --name ${VM_NAME} \
+  --resource-group ${RESOURCE_GROUP} \
+  --location ${LOCATION} \
+  --size Standard_NC24 \
+  --image Canonical:UbuntuServer:16.04-LTS:latest \
+  --admin-username mesnardo \
+  --authentication-type ssh \
+  --ssh-key-value ~/.ssh/id_rsa.pub \
+  --public-ip-address-dns-name ${DNS_NAME} \
+  --storage-sku Standard_LRS

### 2019-08-14 misc/independence/runs/snake3d2k35-coarse/config/installation/install-amgx.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+# setup AmgX
+
+AMGX_DIR=/opt/amgx
+mkdir -p ${AMGX_DIR}
+unzip 2014.12.22_amgx_redhat-6.5_cuda-6.5_openmpi-1.7.2.zip -d ${AMGX_DIR}
+cp "amgx_trial.lic" ${AMGX_DIR}

### 2019-08-14 misc/independence/runs/snake3d2k35-coarse/config/installation/install-amgxwrapper-1.0-beta2.sh

@@ -1,0 +1,32 @@
+#!/bin/bash
+
+AMGXWRAPPER_VERSION="1.0-beta2"
+AMGXWRAPPER_DIR="/opt/amgxwrapper/${AMGXWRAPPER_VERSION}"
+TARBALL="v${AMGXWRAPPER_VERSION}.tar.gz"
+
+mkdir -p ${AMGXWRAPPER_DIR}
+cd /tmp
+wget https://github.com/barbagroup/AmgXWrapper/archive/${TARBALL}
+tar -xzf ${TARBALL} -C ${AMGXWRAPPER_DIR} --strip-components=1
+
+AMGXWRAPPER_POISSON="${AMGXWRAPPER_DIR}/example/Poisson"
+cd ${AMGXWRAPPER_POISSON}
+
+export CC=mpicc
+export CXX=mpicxx
+
+export PETSC_DIR="/opt/petsc/3.7.4"
+export PETSC_ARCH="linux-gnu-opt"
+
+cmake . \
+  -DCUDA_TOOLKIT_ROOT_DIR="/usr/local/cuda-6.5" \
+  -DAMGX_DIR="/opt/amgx/examples" \
+  -DPETSC_DIR="/opt/petsc/3.7.4"
+cmake . \
+  -DCUDA_TOOLKIT_ROOT_DIR="/usr/local/cuda-6.5" \
+  -DAMGX_DIR="/opt/amgx" \
+  -DPETSC_DIR="/opt/petsc/3.7.4"
+
+make
+
+rm -f /tmp/${TARBALL}

### 2019-08-14 misc/independence/runs/snake3d2k35-coarse/config/installation/install-cuda-6.5.sh

@@ -1,0 +1,15 @@
+#!/bin/bash
+# install CUDA-6.5 toolkit
+
+CUDA_REPO_PKG=cuda-repo-ubuntu1404_6.5-14_amd64.deb
+wget -O /tmp/${CUDA_REPO_PKG} http://developer.download.nvidia.com/compute/cuda/repos/ubuntu1404/x86_64/${CUDA_REPO_PKG}
+dpkg -i /tmp/${CUDA_REPO_PKG}
+rm -f /tmp/${CUDA_REPO_PKG}
+apt-get update
+apt-get install cuda-drivers
+apt-get install cuda-6-5
+export PATH="/usr/local/cuda-6.5/bin:$PATH"
+export LD_LIBRARY_PATH="/usr/local/cuda-6.5/lib64:$LD_LIBRARY_PATH"
+cd /usr/local/cuda-6.5/samples/1_Utilities/deviceQuery
+make all
+./deviceQuery

### 2019-08-14 misc/independence/runs/snake3d2k35-coarse/config/installation/install-openmpi-1.8.8.sh

@@ -1,0 +1,20 @@
+#!/bin/bash
+# install OpenMPI-1.8.8
+
+cd /tmp
+OPENMPI_VERSION=1.8.8
+wget https://www.open-mpi.org/software/ompi/v1.8/downloads/openmpi-${OPENMPI_VERSION}.tar.gz
+OPENMPI_DIR=/opt/openmpi/${OPENMPI_VERSION}
+mkdir -p ${OPENMPI_DIR}
+tar -xzf /tmp/openmpi-${OPENMPI_VERSION}.tar.gz -C ${OPENMPI_DIR} --strip-components=1
+cd ${OPENMPI_DIR}
+./configure --prefix=/usr/local \
+	CC=gcc-5 \
+        CFLAGS="-O3" \
+        CXX=g++-5 \
+        CXXFLAGS="-O3" \
+        FC=gfortran-5 \
+        FCFLAGS="-O3"
+make -j"$(nproc)" install
+ldconfig /usr/local/lib
+rm -f /tmp/openmpi-${OPENMPI_VERSION}.tar.gz

### 2019-08-14 misc/independence/runs/snake3d2k35-coarse/config/installation/install-petibm-0.2.sh

@@ -1,0 +1,19 @@
+#!/bin/bash
+# install PetIBM-0.2
+
+cd /tmp
+PETIBM_VERSION=0.2
+PETIBM_DIR=/opt/petibm/${PETIBM_VERSION}
+mkdir -p ${PETIBM_DIR}
+wget https://github.com/barbagroup/PetIBM/archive/v${PETIBM_VERSION}.tar.gz
+tar -xzf v${PETIBM_VERSION}.tar.gz -C ${PETIBM_DIR} --strip-components=1
+cd ${PETIBM_DIR}
+./configure --prefix=/usr/local \
+	CXX=mpicxx \
+        CXXFLAGS="-O3 -w -std=c++11" \
+        --with-petsc-dir=/opt/petsc/3.7.4 \
+        --with-petsc-arch=linux-gnu-opt \
+        --with-cuda=/usr/local/cuda \
+        --with-amgx=/opt/amgx
+make -j4 clean all install
+rm -f /tmp/v${PETIBM_VERSION}.tar.gz

### 2019-08-14 misc/independence/runs/snake3d2k35-coarse/config/installation/install-petsc-3.7.4.sh

@@ -1,0 +1,27 @@
+#!/bin/bash
+# install PETSc-3.7.4
+
+cd /tmp
+PETSC_VERSION=3.7.4
+wget http://ftp.mcs.anl.gov/pub/petsc/release-snapshots/petsc-lite-${PETSC_VERSION}.tar.gz
+PETSC_DIR=/opt/petsc/${PETSC_VERSION}
+mkdir -p ${PETSC_DIR}
+tar -xzf /tmp/petsc-lite-${PETSC_VERSION}.tar.gz -C ${PETSC_DIR} --strip-components=1
+cd ${PETSC_DIR}
+PETSC_ARCH=linux-gnu-opt
+./configure --PETSC_DIR=${PETSC_DIR} --PETSC_ARCH=${PETSC_ARCH} \
+	--with-mpi-dir=/usr/local \
+        --COPTFLAGS="-O3" \
+        --CXXOPTFLAGS="-O3" \
+        --FOPTFLAGS="-O3" \
+        --with-debugging=0 \
+        --download-fblaslapack \
+        --download-hypre \
+        --download-hdf5 \
+        --download-ptscotch \
+        --download-metis \
+        --download-parmetis \
+        --download-superlu_dist
+make PETSC_DIR=${PETSC_DIR} PETSC_ARCH=${PETSC_ARCH} all
+make PETSC_DIR=${PETSC_DIR} PETSC_ARCH=${PETSC_ARCH} test
+rm -f /tmp/petsc-lite-${PETSC_VERSION}.tar.gz

### 2019-08-14 misc/independence/runs/snake3d2k35-coarse/config/installation/preinstall.sh

@@ -1,0 +1,15 @@
+# Pre-installation
+
+apt-get update
+apt-get upgrade
+apt-get install -y --no-install-recommends \
+	gcc-5 \
+	g++-5 \
+	gfortran-5 \
+	make \
+	cmake \
+	unzip \
+	bison \
+	flex
+
+

### 2019-08-14 misc/independence/runs/snake3d2k35-coarse/run-petibm.sh

@@ -1,0 +1,16 @@
+#!/bin/bash
+# Run PetIBM
+
+export CUDA_VISIBLE_DEVICES=0,1,2,3
+CUDA_DIR="/usr/local/cuda-6.5"
+export PATH="${CUDA_DIR}/bin:${PATH}"
+export LD_LIBRARY_PATH="${CUDA_DIR}/lib64:${LD_LIBRARY_PATH}"
+AMGX_DIR="/opt/amgx"
+export LD_LIBRARY_PATH="${AMGX_DIR}/lib:${LD_LIBRARY_PATH}"
+export LM_LICENSE_FILE="${AMGX_DIR}/amgx_trial.lic"
+
+mpiexec -np 24 petibm3d \
+	-log_view \
+	-malloc_log \
+	-memory_view \
+	-options_left

### 2019-08-14 misc/independence/runs/snake3d2k35-fine-restart2/run-petibm.sh

@@ -1,0 +1,41 @@
+#!/bin/bash
+
+SIMULATION_DIR=$1
+
+source /opt/intel/compilers_and_libraries/linux/mpi/intel64/bin/mpivars.sh
+
+# get number of nodes
+IFS=',' read -ra HOSTS <<< "$AZ_BATCH_HOST_LIST"
+nodes=${#HOSTS[@]}
+echo "Number of nodes: $nodes"
+echo "Hosts: $AZ_BATCH_HOST_LIST"
+# number of processes per node
+ppn=24
+echo "Number of processes per node to use: $ppn"
+# number of processes
+np=$(($nodes * $ppn))
+echo "Total number of processes: $np"
+
+# get number of GPUs on machine
+ngpusmax=`nvidia-smi -L | wc -l`
+echo "Number of GPU devices available on each node: $ngpusmax"
+# number of GPUs to use per node
+CUDA_VISIBLE_DEVICES=0,1,2,3
+IFS=',' read -ra GPUS <<< "$CUDA_VISIBLE_DEVICES"
+ngpus=${#GPUS[@]}
+echo "Number of GPU devices per node to use: $ngpus ($CUDA_VISIBLE_DEVICES)"
+
+echo "PATH: $PATH"
+echo "LD_LIBRARY_PATH: $LD_LIBRARY_PATH"
+
+mpirun -np $np -ppn $ppn -host $AZ_BATCH_HOST_LIST \
+  -genv I_MPI_FABRICS=dapl \
+  -genv I_MPI_DAPL_PROVIDER=ofa-v2-ib0 \
+  -genv I_MPI_DYNAMIC_CONNECTION=0 \
+  -genv CUDA_VISIBLE_DEVICES=$CUDA_VISIBLE_DEVICES \
+  petibm3d \
+  -directory $SIMULATION_DIR \
+  -log_view \
+  -malloc_log \
+  -memory_view \
+  -options_left

### 2019-08-14 tex/MesnardoBarba2019.tex
Add sentences about run on finer grid
* at the end of the paragrah about the history of the force coefficients with a footnote pointing to the Jupyter Notebook,
* at the end of the cost analysis

@@
 Two-dimensional computational simulations of fundamentally three-dimensional flows lead to incorrect estimation of the force coefficients, as is well known\cite{mittal_balachandar_1995}.
+The grid used for the three-dimensional simulation contains about $46$ million cells and is somewhat coarse for Direct Numerical Simulation (DNS) at Reynolds number $2,000$, but acceptable for our exploratory analysis.
+A finer grid would be preferable to capture the flow dynamics in details, but the purpose of this paper is not targeting the physics.
+We did however run a simulation on a finer grid (about $233$ million cells) resulting in a relative difference (with respect to the "coarse"-grid simulation) of $+6.5\%$ and $+3\%$ for the time-averaged drag and lift coefficients, respectively.
+We decided to continue this work with the coarser grid due to the cost difference (see Section \ref{sec:cost}).
+Details about this fine-grid simulation are available as supplementary material on the GitHub repository for this study.\footnote{\url{https://nbviewer.jupyter.org/github/barbagroup/cloud-repro/blob/master/misc/independence/grid.ipynb}}
 
@@
 (Note that with 3-year-reserved instances, the two- and three-dimensional snake simulations would have only cost $24.6$ and $478.1$ USD, respectively.)
+The three-dimensional simulation on the finer grid ($233$ million cells) ran on $6$ \texttt{NC24r} instances and cost about $7965$ USD to compute $100,000$ time steps (cost not included in \ref{tab:azure_charges}).
+This is more than $7$ times the cost we paid for the "coarse"-grid run!
+It would have been too expensive to run a batch of simulations on the finer grid for our exploratory analysis of the flow around the snake cylinder.
 

### 2019-08-14 tex/MesnardoBarba2019.tex
Update Colonial One benchmark results with Intel MPI library
Previous Colonial One results used OpenMPI.

@@
 Fig. \ref{fig:osu_benchmarks} reports the mean latencies and bandwidths obtained over $5$ repetitions on both platforms.
-For small message sizes, the average latencies on Colonial One and Azure are $1.75$ and $1.95 \mu $s, respectively.
-As the message size increases, the latency becomes smaller on Azure compared to Colonial One.
-The maximum sustained bandwidth rates for Colonial One and Azure are on average $4.5$ and $5.6$ GB/s, respectively.
-For all message sizes, a higher bandwidth rate was achieved on Azure.
+For small message sizes, the average latencies on Colonial One and Azure are $1.25$ and $1.95 \mu $s, respectively.
+For all message sizes, the latency reported on Azure is slightly higher than the value obtained on Colonial One.
+The maximum sustained bandwidth rates for Colonial One and Azure are on average $6.2$ and $5.2$ GB/s, respectively.
+For all message sizes, a similar bandwidth rate was achieved on Azure and Colonial One.
 Over the last few years, Microsoft Azure has indeed improved its HPC solutions to provide networking capabilities that are comparable or even better than our 6-year-old university-managed cluster.
@@
     \includegraphics[width=8cm]{figures/osu_latency_bandwidth.pdf}
-    \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One (\texttt{Ivygpu} nodes) and on Microsoft Azure (\texttt{NC24r} nodes).
+    \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One (\texttt{Ivygpu} nodes) and on Microsoft Azure (\texttt{NC24r} nodes) with the Intel MPI library.
 Benchmark results are averaged over $5$ repetitions.}
@@
 Fig.
-\ref{fig:poisson_benchmarks} (top) reports the mean runtimes (averaged over $5$ repetitions) to iteratively solve the system, on a uniform grid of $50$ million cells ($1000 \times 1000 \times 50$), as we increase the number of nodes in the pool.
+\ref{fig:poisson_benchmarks} (top) reports the mean runtimes (averaged over $5$ repetitions) to iteratively solve the system, on a uniform grid of $50$ million cells ($1000 \times 1000 \times 50$), as we increase the number of nodes in the pool (strong scaling).
+Runtimes between obtained on Colonial One and Azure are similar.
 We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
-The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) was solved on a single compute node using $12$ MPI processes and $2$ GPU devices; we then doubled the mesh size as we doubled the number of nodes (keeping the same number of MPI processes and GPUs per node).
+The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) was solved on a single compute node using $12$ MPI processes and $2$ GPU devices; we then doubled the mesh size as we doubled the number of nodes, keeping the same number of MPI processes and GPUs per node (weak scaling).
 The number of iterations to reach convergence increases with the size of the system, so we normalize the runtimes by the number of iterations.
@@
 The bottom-right panel of the figure reports the normalized mean runtimes obtained on Azure when we load the bandwidth with a larger problem; the base mesh now contains $25$ millions cells ($1000 \times 500 \times 50$).
-We observe larger variations in the time-to-solution for the Poisson system on Microsoft Azure; runtimes are more uniform on Colonial One.
+We observe larger variations in the time-to-solution for the Poisson system on Microsoft Azure with GPU computing; runtimes are more uniform on Colonial One.
 

### 2019-08-14 examples/osubenchmarks/colonialone-openmpi/run-osu.sh

@@ -1,0 +1,36 @@
+#!/bin/sh
+
+#SBATCH --job-name="osu"
+#SBATCH --output=log%j.out
+#SBATCH --error=log%j.err
+#SBATCH --partition=ivygpu
+#SBATCH --nodes=2
+#SBATCH --ntasks-per-node=1
+#SBATCH --time=01:00:00
+
+module load gcc/4.9.2
+module load cuda/toolkit/8.0
+module load openmpi/1.8/gcc/4.9.2
+
+bindir="/groups/barbalab/software/osu-micro-benchmarks/5.6/mpi/pt2pt"
+export PATH=$bindir:$PATH
+
+export CUDA_VISIBLE_DEVICES=0,1
+
+# number of runs
+nruns=5
+
+outdir="output"
+mkdir -p $outdir
+cd $outdir
+
+for (( i=0; i<$nruns; i++ ))
+do
+	echo "run $i"
+	time mpiexec -display-map -mca btl openib,self \
+		osu_bw -d cuda -x 100 -i 1000 H H \
+		> stdout_bandwidth_run$i.txt 2> stderr_bandwidth_run$i.txt
+	time mpiexec -display-map -mca btl openib,self \
+		osu_latency -d cuda -x 100 -i 1000 H H \
+		> stdout_latency_run$i.txt 2> stderr_latency_run$i.txt
+done

### 2019-08-14 examples/osubenchmarks/colonialone/run-osu.sh

@@ -1,4 +1,4 @@
-#!/bin/sh
+#!/usr/bin/env bash
 
 #SBATCH --job-name="osu"
 #SBATCH --output=log%j.out
@@ -6,31 +6,34 @@
 #SBATCH --partition=ivygpu
 #SBATCH --nodes=2
 #SBATCH --ntasks-per-node=1
-#SBATCH --time=01:00:00
+#SBATCH --time=00:20:00
 
-module load gcc/4.9.2
-module load cuda/toolkit/8.0
-module load openmpi/1.8/gcc/4.9.2
+source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
 
-bindir="/groups/barbalab/software/osu-micro-benchmarks/5.6/mpi/pt2pt"
+bindir="/groups/barbalab/software/osu-micro-benchmarks/5.6-intelmpi/mpi/pt2pt"
 export PATH=$bindir:$PATH
-
-export CUDA_VISIBLE_DEVICES=0,1
 
 # number of runs
 nruns=5
 
-outdir="output"
+outdir="/home/mesnardo/runs/osubenchmarks/colonialone-intelmpi/output"
 mkdir -p $outdir
 cd $outdir
 
-for (( i=0; i<$nruns; i++ ))
-do
-	echo "run $i"
-	time mpiexec -display-map -mca btl openib,self \
-		osu_bw -d cuda -x 100 -i 1000 H H \
-		> stdout_bandwidth_run$i.txt 2> stderr_bandwidth_run$i.txt
-	time mpiexec -display-map -mca btl openib,self \
-		osu_latency -d cuda -x 100 -i 1000 H H \
-		> stdout_latency_run$i.txt 2> stderr_latency_run$i.txt
+for i in `seq 1 5`; do
+	mpirun -n 2 --ppn 1 \
+		-env I_MPI_FABRICS=dapl \
+		-env I_MPI_DAPL_PROVIDER=ofa-v2-ib0 \
+		-env I_MPI_DYNAMIC_CONNECTION=0 \
+		osu_latency \
+		-x 100 -i 10000 H H \
+		>> $outdir/stdout_latency_run$i.txt 2> $outdir/stderr_latency_run$i.txt
+
+	mpirun -n 2 --ppn 1 \
+		-env I_MPI_FABRICS=dapl \
[…]

### 2019-08-14 examples/osubenchmarks/scripts/plot_latency_bandwidth_all.py

@@ -62,6 +62,7 @@ def get_latency_bandwidth_data(datadir, iterator, prefix='', suffix=''):
         data.append(subdata)
     # Average the measure over the runs.
     data = numpy.mean(data, axis=0)
+    print(data)
     return size, data
 
 
@@ -81,9 +82,11 @@ sizes, bandwidths = get_latency_bandwidth_data(datadir, range(1, 6),
                                                prefix='stdout_bandwidth_run',
                                                suffix='.txt')
 data[label]['bandwidth'] = {'sizes': sizes, 'values': bandwidths}
+data[label]['kwargs'] = dict(color='C0', linestyle='-',
+                             marker='o', markersize=6)
 
 # Get the latency and bandwidth results for Colonial One runs.
-label = 'Colonial One (Ivygpu)'
+label = 'Colonial One (Intel MPI)'
 data[label] = {}
 datadir = rootdir / 'colonialone' / 'output'
 sizes, latencies = get_latency_bandwidth_data(datadir, range(1, 6),
@@ -94,18 +97,35 @@ sizes, bandwidths = get_latency_bandwidth_data(datadir, range(1, 6),
                                                prefix='stdout_bandwidth_run',
                                                suffix='.txt')
 data[label]['bandwidth'] = {'sizes': sizes, 'values': bandwidths}
+data[label]['kwargs'] = dict(color='C1', linestyle='--',
+                             marker='o', markersize=6)
+
+# Get the latency and bandwidth results for Colonial One runs with Intel MPI.
+label = 'Colonial One (OpenMPI)'
+data[label] = {}
+datadir = rootdir / 'colonialone-openmpi' / 'output'
+sizes, latencies = get_latency_bandwidth_data(datadir, range(5),
+                                              prefix='stdout_latency_run',
+                                              suffix='.txt')
+data[label]['latency'] = {'sizes': sizes, 'values': latencies}
+sizes, bandwidths = get_latency_bandwidth_data(datadir, range(5),
+                                               prefix='stdout_bandwidth_run',
+                                               suffix='.txt')
+data[label]['bandwidth'] = {'sizes': sizes, 'values': bandwidths}
+data[label]['kwargs'] = dict(color='C2', linestyle='-',
[…]

### 2019-08-14 examples/poisson/colonialone-openmpi/amgx/01_ivygpu/run-poisson.sh

@@ -1,26 +1,23 @@
 #!/usr/bin/env bash
 
-#SBATCH --job-name="08amgx"
+#SBATCH --job-name="01amgx"
 #SBATCH --output=log%j.out
 #SBATCH --error=log%j.err
 #SBATCH --partition=ivygpu
-#SBATCH --nodes=8
+#SBATCH --nodes=1
 #SBATCH --ntasks-per-node=12
-#SBATCH --time=00:30:00
+#SBATCH --time=01:00:00
 
-n=8
-ppn=12
-np=$(($n * $ppn))
+nodes=1
 
 module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
-
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 export CUDA_VISIBLE_DEVICES=0,1
@@ -34,14 +31,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_amgx_${n}nodes_run${counter}"
-	mpirun -np $np -ppn $ppn poisson \
+	casename="poisson_amgx_${nodes}nodes_run${counter}"
+	mpiexec poisson \
 		-caseName $casename \
 		-mode AmgX_GPU \
 		-cfgFileName $configdir/poisson_solver.info \
-		-Nx 1000 -Ny 500 -Nz 100 \
+		-Nx 500 -Ny 500 -Nz 25 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
[…]

### 2019-08-14 examples/poisson/colonialone-openmpi/amgx/02_ivygpu/run-poisson.sh

@@ -1,26 +1,23 @@
 #!/usr/bin/env bash
 
-#SBATCH --job-name="08amgx"
+#SBATCH --job-name="02amgx"
 #SBATCH --output=log%j.out
 #SBATCH --error=log%j.err
 #SBATCH --partition=ivygpu
-#SBATCH --nodes=8
+#SBATCH --nodes=2
 #SBATCH --ntasks-per-node=12
-#SBATCH --time=00:30:00
+#SBATCH --time=01:00:00
 
-n=8
-ppn=12
-np=$(($n * $ppn))
+nodes=2
 
 module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
-
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 export CUDA_VISIBLE_DEVICES=0,1
@@ -34,14 +31,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_amgx_${n}nodes_run${counter}"
-	mpirun -np $np -ppn $ppn poisson \
+	casename="poisson_amgx_${nodes}nodes_run${counter}"
+	mpiexec poisson \
 		-caseName $casename \
 		-mode AmgX_GPU \
 		-cfgFileName $configdir/poisson_solver.info \
-		-Nx 1000 -Ny 500 -Nz 100 \
+		-Nx 500 -Ny 500 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
[…]

### 2019-08-14 examples/poisson/colonialone-openmpi/amgx/04_ivygpu/run-poisson.sh

@@ -1,26 +1,23 @@
 #!/usr/bin/env bash
 
-#SBATCH --job-name="08amgx"
+#SBATCH --job-name="04amgx"
 #SBATCH --output=log%j.out
 #SBATCH --error=log%j.err
 #SBATCH --partition=ivygpu
-#SBATCH --nodes=8
+#SBATCH --nodes=4
 #SBATCH --ntasks-per-node=12
 #SBATCH --time=00:30:00
 
-n=8
-ppn=12
-np=$(($n * $ppn))
+nodes=4
 
 module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
-
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 export CUDA_VISIBLE_DEVICES=0,1
@@ -34,14 +31,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_amgx_${n}nodes_run${counter}"
-	mpirun -np $np -ppn $ppn poisson \
+	casename="poisson_amgx_${nodes}nodes_run${counter}"
+	mpiexec poisson \
 		-caseName $casename \
 		-mode AmgX_GPU \
 		-cfgFileName $configdir/poisson_solver.info \
-		-Nx 1000 -Ny 500 -Nz 100 \
+		-Nx 1000 -Ny 500 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
[…]

### 2019-08-14 examples/poisson/colonialone-openmpi/amgx/08_ivygpu/run-poisson.sh

@@ -8,19 +8,16 @@
 #SBATCH --ntasks-per-node=12
 #SBATCH --time=00:30:00
 
-n=8
-ppn=12
-np=$(($n * $ppn))
+nodes=8
 
 module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
-
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 export CUDA_VISIBLE_DEVICES=0,1
@@ -34,14 +31,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_amgx_${n}nodes_run${counter}"
-	mpirun -np $np -ppn $ppn poisson \
+	casename="poisson_amgx_${nodes}nodes_run${counter}"
+	mpiexec poisson \
 		-caseName $casename \
 		-mode AmgX_GPU \
 		-cfgFileName $configdir/poisson_solver.info \
-		-Nx 1000 -Ny 500 -Nz 100 \
+		-Nx 1000 -Ny 1000 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
 	((counter++))
 done
 

### 2019-08-14 examples/poisson/colonialone-openmpi/petsc/01_short/run-poisson.sh

@@ -1,26 +1,23 @@
 #!/usr/bin/env bash
 
-#SBATCH --job-name="02petsc"
+#SBATCH --job-name="01petsc"
 #SBATCH --output=log%j.out
 #SBATCH --error=log%j.err
 #SBATCH --partition=short
-#SBATCH --nodes=2
+#SBATCH --nodes=1
 #SBATCH --ntasks-per-node=16
-#SBATCH --time=00:20:00
+#SBATCH --time=01:00:00
 
-n=2
-ppn=16
-np=$(($n * $ppn))
+nodes=1
 
 module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
-
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 configdir="../config"
@@ -32,14 +29,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_petsc_${n}nodes_run${counter}"
-	mpirun -np $np -ppn $ppn poisson \
+	casename="poisson_petsc_${nodes}nodes_run${counter}"
+	mpiexec poisson \
 		-caseName $casename \
 		-mode PETSc \
 		-cfgFileName $configdir/poisson_solver.info \
 		-Nx 1000 -Ny 1000 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
 	((counter++))
 done
 

### 2019-08-14 examples/poisson/colonialone-openmpi/petsc/02_short/run-poisson.sh

@@ -8,19 +8,16 @@
 #SBATCH --ntasks-per-node=16
 #SBATCH --time=00:20:00
 
-n=2
-ppn=16
-np=$(($n * $ppn))
+nodes=2
 
 module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
-
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 configdir="../config"
@@ -32,14 +29,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_petsc_${n}nodes_run${counter}"
-	mpirun -np $np -ppn $ppn poisson \
+	casename="poisson_petsc_${nodes}nodes_run${counter}"
+	mpiexec poisson \
 		-caseName $casename \
 		-mode PETSc \
 		-cfgFileName $configdir/poisson_solver.info \
 		-Nx 1000 -Ny 1000 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
 	((counter++))
 done
 

### 2019-08-14 examples/poisson/colonialone-openmpi/petsc/04_short/run-poisson.sh

@@ -1,26 +1,23 @@
 #!/usr/bin/env bash
 
-#SBATCH --job-name="02petsc"
+#SBATCH --job-name="04petsc"
 #SBATCH --output=log%j.out
 #SBATCH --error=log%j.err
 #SBATCH --partition=short
-#SBATCH --nodes=2
+#SBATCH --nodes=4
 #SBATCH --ntasks-per-node=16
 #SBATCH --time=00:20:00
 
-n=2
-ppn=16
-np=$(($n * $ppn))
+nodes=4
 
 module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
-
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 configdir="../config"
@@ -32,14 +29,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_petsc_${n}nodes_run${counter}"
-	mpirun -np $np -ppn $ppn poisson \
+	casename="poisson_petsc_${nodes}nodes_run${counter}"
+	mpiexec poisson \
 		-caseName $casename \
 		-mode PETSc \
 		-cfgFileName $configdir/poisson_solver.info \
 		-Nx 1000 -Ny 1000 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
 	((counter++))
 done
 

### 2019-08-14 examples/poisson/colonialone-openmpi/petsc/08_short/run-poisson.sh

@@ -1,26 +1,23 @@
 #!/usr/bin/env bash
 
-#SBATCH --job-name="02petsc"
+#SBATCH --job-name="08petsc"
 #SBATCH --output=log%j.out
 #SBATCH --error=log%j.err
 #SBATCH --partition=short
-#SBATCH --nodes=2
+#SBATCH --nodes=8
 #SBATCH --ntasks-per-node=16
 #SBATCH --time=00:20:00
 
-n=2
-ppn=16
-np=$(($n * $ppn))
+nodes=8
 
 module load gcc/4.9.2
+module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
-
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 configdir="../config"
@@ -32,14 +29,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_petsc_${n}nodes_run${counter}"
-	mpirun -np $np -ppn $ppn poisson \
+	casename="poisson_petsc_${nodes}nodes_run${counter}"
+	mpiexec poisson \
 		-caseName $casename \
 		-mode PETSc \
 		-cfgFileName $configdir/poisson_solver.info \
 		-Nx 1000 -Ny 1000 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
 	((counter++))
 done
 

### 2019-08-14 examples/poisson/colonialone/amgx/01_ivygpu/run-poisson.sh

@@ -8,16 +8,19 @@
 #SBATCH --ntasks-per-node=12
 #SBATCH --time=01:00:00
 
-nodes=1
+n=1
+ppn=12
+np=$(($n * $ppn))
 
 module load gcc/4.9.2
-module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 export CUDA_VISIBLE_DEVICES=0,1
@@ -31,14 +34,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_amgx_${nodes}nodes_run${counter}"
-	mpiexec poisson \
+	casename="poisson_amgx_${n}nodes_run${counter}"
+	mpirun -np $np -ppn $ppn poisson \
 		-caseName $casename \
 		-mode AmgX_GPU \
 		-cfgFileName $configdir/poisson_solver.info \
 		-Nx 500 -Ny 500 -Nz 25 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
 	((counter++))
 done
 

### 2019-08-14 examples/poisson/colonialone/amgx/02_ivygpu/run-poisson.sh

@@ -8,16 +8,19 @@
 #SBATCH --ntasks-per-node=12
 #SBATCH --time=01:00:00
 
-nodes=2
+n=2
+ppn=12
+np=$(($n * $ppn))
 
 module load gcc/4.9.2
-module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 export CUDA_VISIBLE_DEVICES=0,1
@@ -31,14 +34,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_amgx_${nodes}nodes_run${counter}"
-	mpiexec poisson \
+	casename="poisson_amgx_${n}nodes_run${counter}"
+	mpirun -np $np -ppn $ppn poisson \
 		-caseName $casename \
 		-mode AmgX_GPU \
 		-cfgFileName $configdir/poisson_solver.info \
 		-Nx 500 -Ny 500 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
 	((counter++))
 done
 

### 2019-08-14 examples/poisson/colonialone/amgx/04_ivygpu/run-poisson.sh

@@ -8,16 +8,19 @@
 #SBATCH --ntasks-per-node=12
 #SBATCH --time=00:30:00
 
-nodes=4
+n=4
+ppn=12
+np=$(($n * $ppn))
 
 module load gcc/4.9.2
-module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 export CUDA_VISIBLE_DEVICES=0,1
@@ -31,14 +34,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_amgx_${nodes}nodes_run${counter}"
-	mpiexec poisson \
+	casename="poisson_amgx_${n}nodes_run${counter}"
+	mpirun -np $np -ppn $ppn poisson \
 		-caseName $casename \
 		-mode AmgX_GPU \
 		-cfgFileName $configdir/poisson_solver.info \
 		-Nx 1000 -Ny 500 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
 	((counter++))
 done
 

### 2019-08-14 examples/poisson/colonialone/petsc/01_short/run-poisson.sh

@@ -8,16 +8,19 @@
 #SBATCH --ntasks-per-node=16
 #SBATCH --time=01:00:00
 
-nodes=1
+n=1
+ppn=16
+np=$(($n * $ppn))
 
 module load gcc/4.9.2
-module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 configdir="../config"
@@ -29,14 +32,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_petsc_${nodes}nodes_run${counter}"
-	mpiexec poisson \
+	casename="poisson_petsc_${n}nodes_run${counter}"
+	mpirun -np $np -ppn $ppn poisson \
 		-caseName $casename \
 		-mode PETSc \
 		-cfgFileName $configdir/poisson_solver.info \
 		-Nx 1000 -Ny 1000 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
 	((counter++))
 done
 

### 2019-08-14 examples/poisson/colonialone/petsc/04_short/run-poisson.sh

@@ -8,16 +8,19 @@
 #SBATCH --ntasks-per-node=16
 #SBATCH --time=00:20:00
 
-nodes=4
+n=4
+ppn=16
+np=$(($n * $ppn))
 
 module load gcc/4.9.2
-module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 configdir="../config"
@@ -29,14 +32,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_petsc_${nodes}nodes_run${counter}"
-	mpiexec poisson \
+	casename="poisson_petsc_${n}nodes_run${counter}"
+	mpirun -np $np -ppn $ppn poisson \
 		-caseName $casename \
 		-mode PETSc \
 		-cfgFileName $configdir/poisson_solver.info \
 		-Nx 1000 -Ny 1000 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
 	((counter++))
 done
 

### 2019-08-14 examples/poisson/colonialone/petsc/08_short/run-poisson.sh

@@ -8,16 +8,19 @@
 #SBATCH --ntasks-per-node=16
 #SBATCH --time=00:20:00
 
-nodes=8
+n=8
+ppn=16
+np=$(($n * $ppn))
 
 module load gcc/4.9.2
-module load openmpi/1.8/gcc/4.9.2
 module load cuda/toolkit/8.0
 
-AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-openmpi-opt"
+source /c1/apps/intel-cluster-studio/2017.4/compilers_and_libraries_2017.4.196/linux/mpi/intel64/bin/mpivars.sh
+
+AMGXWRAPPER_DIR="/groups/barbalab/software/amgxwrapper/1.4/linux-gnu-intelmpi-opt"
 export PATH="$AMGXWRAPPER_DIR/example/poisson/bin":$PATH
 
-AMGX_DIR="/groups/barbalab/software/amgx/git/master/linux-openmpi-opt"
+AMGX_DIR="/groups/barbalab/software/amgx-2.0/linux-gnu-intelmpi-opt"
 export LD_LIBRARY_PATH="$AMGX_DIR/lib":$LD_LIBRARY_PATH
 
 configdir="../config"
@@ -29,14 +32,14 @@ counter=1
 
 while [ $counter -le $niters ]
 do
-	casename="poisson_petsc_${nodes}nodes_run${counter}"
-	mpiexec poisson \
+	casename="poisson_petsc_${n}nodes_run${counter}"
+	mpirun -np $np -ppn $ppn poisson \
 		-caseName $casename \
 		-mode PETSc \
 		-cfgFileName $configdir/poisson_solver.info \
 		-Nx 1000 -Ny 1000 -Nz 50 \
 		-log_view ascii:${outdir}/view_run${counter}.log \
-		-options_left >> ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
+		-options_left > ${outdir}/stdout_run${counter}.txt 2> ${outdir}/stderr_run${counter}.txt
 	((counter++))
 done
 

### 2019-08-14 examples/poisson/scripts/plot_runtimes_all.py

@@ -1,0 +1,315 @@
+"""Plot the time-to-solution versus the number of nodes."""
+
+import pathlib
+from matplotlib import pyplot, gridspec
+import numpy
+
+
+def get_filepaths(casedir, prefix='stdout_run', suffix='.txt', niter=5):
+    """Get the file paths with data to read.
+
+    Parameters
+    ----------
+    casedir : pathlib.Path object
+        Directory that contains the files to read.
+    prefix : string (optional)
+        Common prefix of the file names; default: 'stdout_run'.
+    suffix : string (optional)
+        Common suffix of the file names; default: '.txt'.
+    niter : integer (optional)
+        Number of repeated runs (i.e., number of files to read).
+
+    Returns
+    -------
+    filepaths : list of pathlib.Path objects
+        The file paths.
+
+    """
+    filepaths = [casedir / (prefix + str(i + 1) + suffix)
+                 for i in range(niter)]
+    return filepaths
+
+
+def amgxwrapper_poisson_read_runtimes(*filepaths):
+    """Read the runtimes to solve the system for multiple runs.
+
+    Parameters
+    ----------
+    filepaths : tuple of strings or pathlib.Path objects
+        Path of the files to read.
+
+    Returns
+    -------
+    runtimes : list of floats
+        The runtimes.
+
+    """
+    runtimes = []
+    for filepath in filepaths:
+        with open(filepath, 'r') as infile:
+            prev_line = ''
+            for line in infile:
+                if 'Solve Time:' in line:
+                    if not prev_line.startswith('Warm-up'):
+                        runtime = float(line.split(' ')[-1])
+                        runtimes.append(runtime)
+                prev_line = line
+    return runtimes
+
+
+def amgxwrapper_poisson_read_iterations(filepath):
+    """Read the number of iterations to solve the system.
+
+    Parameters
+    ----------
+    filepath : string or pathlib.Path object
+        Path of the file to read.
+
+    Returns
+    -------
+    nites : integer
[…]

### 2019-08-15 tex/MesnardoBarba2019.tex
restructure caption fig. 3

@@
         \hline
-        \multirow{2}{*}{Azure} & \texttt{NC24r} & Dual 12-Core E5-2690v3 (2.60GHz) & 24 & 4 x K80 & 224 & 1440 \\
+        \multirow{2}{*}{Azure} & \texttt{NC24r} & Dual 12-Core E5-2690v3 (2.60GHz) & 24 & 2 x K80 & 224 & 1440 \\
         & \texttt{H16r} & Dual 8-Core E5-2667v3 (3.20GHz) & 16 & - & 112 & 2000 \\
@@
     \includegraphics[width=8cm]{figures/poisson_time_vs_nodes.pdf}
-    \caption{Runtime to solve a Poisson system on Colonial One and on Microsoft Azure.
-Benchmark was repeated 5 times and we report the mean runtime as well as the extrema.
-Poisson system was solved on Azure using PETSc on \texttt{H16r} nodes ($16$ processes per node) and using AmgX on \texttt{NC24r} nodes ($12$ processes and $1$ NVIDIA K80 GPU per node).
-On Colonial One, we solved the system with PETSc on \texttt{Short} nodes ($16$ processes per node) and with AmgX on \texttt{Ivygpu} nodes ($12$ processes and $2$ NVIDIA K20 GPUs per node).
-The runs with PETSc solved a Poisson system on a mesh size of 50 million cells (top).
-With AmgX (bottom left), the base mesh size contains 6.25 million cells and we scale it with the number of nodes.
-On Azure, we also ran the Poisson benchmark with a finer base mesh size of 25 million cells (bottom right).
+    \caption{Runtime to solve a Poisson system on Colonial One and Microsoft Azure.
+Benchmarks were repeated 5 times and we show the mean runtime and the extrema.
+\textbf{Top}: system solved on a fixed mesh size of 50 million cells (strong scaling) using PETSc on Azure \texttt{H16r} nodes ($16$ processes per node), and Colonial One \texttt{Short} nodes ($16$ processes per node).
+\textbf{Bottom-left}:  systems solved using AmgX on Azure \texttt{NC24r} nodes ($12$ processes and $2$ GPUs per node), and Colonial One \texttt{Ivygpu} nodes ($12$ processes and $2$ GPUs per node); the base mesh size contains 6.25 million cells and we scale it with the number of nodes (weak scaling).
+\textbf{Bottom-right:} systems solved with AmgX on Azure \texttt{NC24r} nodes ($24$ processes and $4$ GPUs per node), using a finer base mesh size of 25 million cells.
 Runtimes obtained with AmgX were normalized by the number of iterations required to reach a absolute tolerance of $10^{-12}$.}
@@
 Two-dimensional computational simulations of fundamentally three-dimensional flows lead to incorrect estimation of the force coefficients, as is well known\cite{mittal_balachandar_1995}.
-The grid used for the three-dimensional simulation contains about $46$ million cells and is somewhat coarse for Direct Numerical Simulation (DNS) at Reynolds number $2,000$, but acceptable for our exploratory analysis.
-A finer grid would be preferable to capture the flow dynamics in details, but the purpose of this paper is not targeting the physics.
+The grid used for the three-dimensional simulation contains about $46$ million cells and is somewhat coarse for direct numerical simulation at Reynolds number $2,000$, but acceptable for our exploratory analysis.
+A finer grid would be preferable to capture the flow dynamics in detail, but the purpose of this paper is not targeting the physics.
 We did however run a simulation on a finer grid (about $233$ million cells) resulting in a relative difference (with respect to the "coarse"-grid simulation) of $+6.5\%$ and $+3\%$ for the time-averaged drag and lift coefficients, respectively.
-We decided to continue this work with the coarser grid due to the cost difference (see Section \ref{sec:cost}).
+We decided to continue this work with the coarser grid due to the large cost difference (see Section \ref{sec:cost}).
 Details about this fine-grid simulation are available as supplementary material on the GitHub repository for this study.\footnote{\url{https://nbviewer.jupyter.org/github/barbagroup/cloud-repro/blob/master/misc/independence/grid.ipynb}}

### 2019-08-15 tex/MesnardoBarba2019.tex
add note on reviewer contributions

@@
 We would like to thank Kenji Takeda, Fred Park, and Joshua Poulson of Microsoft for their help.
-We are also immensely grateful to the reviewers, Patrick O'Leary \cite{oleary_2019} and Freddie Witherden \cite{witherden_2019}, for their suggestions.
+We are also immensely grateful to the reviewers, Patrick O'Leary \cite{oleary_2019} and Freddie Witherden \cite{witherden_2019}, for their contributions, which helped make the paper's audience and purpose more clear, in addition to other improvements.
+We include our detailed replies to the reviewer suggestions as a markdown file in the GitHub repository for this paper (exported from GitHub issues).
 

### 2019-08-15 tex/MesnardoBarba2019.tex
Add DOI for workflow diagram

@@
 Azure CLI is use to configure accounts on Microsoft Azure and to upload/download data to/from an Azure Storage account.
-With Batch Shipyard, we create a pool on Azure Batch and run container-based simulation using our Docker image.}
+With Batch Shipyard, we create a pool on Azure Batch and run container-based simulation using our Docker image.
+Figure available under CC BY 4.0 license (DOI: https://doi.org/10.6084/m9.figshare.9636722.v1).}
     \label{fig:cloud_workflow}

### 2019-08-15 response_to_reviewers.md
Add response to reviewers in Markdown

# Response to reviewers

## Reviewer 1

> Patrick O'Leary. Review: "Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics". Authorea. July 26, 2019. DOI: [https://doi.org/10.22541/au.156415458.85375575](https://doi.org/10.22541/au.156415458.85375575)

Portions of the review report quoted here by permissions granted on the original under a CC-BY license.

### Comment 1

* [x] Neither the introduction or the paper highlight the thesis or novel contributions. The reader is left to decide for themselves what aspect they believe are important. This needs to be improved. I found the following list to be reasonable possibilities:

1. Use of cloud computing as an alternative to onsite high-performance computing (HPC).
2. Improvement in public cloud offerings in last 2 to 4 years.
3. A proposed reproducible workflow.
4. The author's experiences.

**Reply**

* The main thesis of the paper is the idea of extending the set of open research objects created and shared for reproducibility (what we call "reproducibility packages"), to the automatic configuration of the computing environment on a cloud service. We explain our contribution in text added at the end of paragraph 3 of the Introduction. We also added a new paragraph at the end of the Introduction to emphasize the point that our paper updates the record with respect to the paper by Freniere and co-authors.
* Because many researchers in "traditional" computational fields (compared to data science) are still highly skeptical of using cloud for their work, we feel it's necessary to provide evidence that it's feasible today to complete CFD studies with cloud computing. Specifically, we need to show that cloud offerings today are practical for parallel computing with GPUs. We added a few sentences to the Abstract and to the last paragraph of the Introduction to emphasize this point.
* Another principal concern of researchers considering cloud resources is the cost. We can't address the issue in this paper in every detail. But we do want to communicate the cost of running the experiments we showcase, and share our ideas about how this concern may be addressed in the future (cost should come down, universities should tackle how to charge indirect costs, and maybe funding agencies could make bulk contracts with providers).

**Changes**

* Improve abstract and introduction to highlight present contributions ([8d998af](https://github.com/barbagroup/cloud-repro/commit/8d998af1c47dbaff37ac713472375bafad45678c)).

---

### Comment 2

* [x] the code snippets breakup the prose with generic, easy to find information such as how to instantiate or run a docker image

**Reply**

* We intend this paper to also serve as a mini-tutorial for researchers wanting to adopt more reproducible practices. (This is mentioned in the beginning of Section 2.) We understand that for this reviewer (an expert in cloud computing, and HPC) these things are obvious. We find among our colleagues and at CFD conferences that containers are still an esoteric technology for most applied computational researchers.

**Changes**

* No changes needed.

---

### Comment 3

* [x] Section One - Defines why reproducibility is essential for science and describes the related work but fails to differentiate their work from past contributions. The reader is left to speculate that it is merely an update to M. Schwab et al., C. Boettiger, C. Freniere et al. works.

**Reply**

* We are citing all of those works in the Introduction. With the new language introduced addressing comment 1, it should be clear now how we extend the work of the previous authors: we propose capturing the cloud environment programmatically and to share with readers the configuration files; we update the record on the observations made by Freniere et al. to the new cloud services introduced in the last two years.

**Changes**

* Improve abstract and introduction to highlight present contributions ([8d998af](https://github.com/barbagroup/cloud-repro/commit/8d998af1c47dbaff37ac713472375bafad45678c)).

---

### Comment 4

Section Two - Walks the reader through the authors' reproducibility workflow outlined in figure 1.

Notes:

* [x] The delete jobs and pool step is missing in figure 1, but presented (including a listing) in the text.
* [x] Do we need to see the content of listing 1 - 4? Why not add a script to the repository and point to it like the YAML config files in examples/snake2d2k35/config_shipyard? 
* [x] The docker build fails on the COPY ../ssh_config stage. Moreover, do the authors want someone to push their image to the authors' docker hub repository? Besides, the repository in footnote 1 contains a typo which highlights the far more significant issues in reproducibility of well-written error-free publications. This paper is a well-written paper, but errors happen.
* [x] The authors generalize that "same container ... can now run at scale." What about the MPI drivers? Does this effect where it can run and what hardware it can use?

**Reply**

* We added the step "Delete jobs and pool" to the workflow in Fig. 1.
* Do we need the listings? — From the reviewer's point of view, these may seem unnecessary, because the reviewer is already an expert in using containers and cloud resources. But we are aiming our paper for readers who are not experts, may have heard of containers as a new and interesting technology, but have never used them. These readers will see from these listings that adopting containers to make their computations more reproducible is not very complicated or time consuming. We want to include these listings as part of the narrative to encourage more researchers to adopt these tools.
* We updated the Dockerfiles to avoid the error message raised during the COPY instruction. We also fixed the typo in the URL of the GitHub repository.
* We do not expect the readers to build the Docker images locally. Indeed, we store the images on DockerHub, so that they can immediately use them. We provide the command-line instructions we used to build the images (as this is part of the workflow). If the readers want to re-build/modify the image locally, we do not expect them to push it to our DockerHub repository. We modified the last paragraph of sub-section 2.1 to reflect our intentions.
* The Docker images were specifically built (on our local workstation) to be able to run MPI applications on RDMA-capable VMs (such as the NC24r instance with a CentOS-based 7.3 HPC image) using multiple-instance tasks on Azure Batch service. The RDMA network on Azure supports MPI traffic for applications running with Intel MPI 5.x (or a later version). (In other words, to take advantage of RDMA on Linux compute nodes, we must use Intel MPI on the nodes.) We added a sentence  over the end of paragraph 4 of the section "Cost Analysis and User Experience" mentioning the Docker images was specifically crafted to be used with Azure Batch service. Thus, we also removed the sentence "same container ... run at scale."

**Changes**

* Fix typo in URL of footnote ([aac96cb](https://github.com/barbagroup/cloud-repro/commit/aac96cba56e532191e700802e250361068553a02)).
* Change directory of the build context so that Docker build does not fail ([67634d9](https://github.com/barbagroup/cloud-repro/commit/67634d915c3a5357dd363b8b8bdc1924e822a3d9)).
* Add step "Delete pool/jobs" to workflow diagram in Fig. 1 ([d612512](https://github.com/barbagroup/cloud-repro/commit/d61251290afc8e59fda135961d70d2804a5adcf8)).
* Remove sentence "same container ... run at scale" ([758e485](https://github.com/barbagroup/cloud-repro/commit/758e485de260cad01c72bdb38f93059593e4fe1b)).
* Mention Docker images were specifically built to run with Azure Batch service ([c908f53](https://github.com/barbagroup/cloud-repro/commit/c908f53bedb699e1ef0853a56ce4353cc21719de)).
* Change "Anyone" to "The reader interested..." ([a84844f](https://github.com/barbagroup/cloud-repro/commit/a84844fca16d25cdfa90d55c35778e2a20130796)).

---

### Comment 5

* [x] At its' core, this paper is describing the use of cloud computing as an alternative to onsite high-performance computing (HPC). At 'scale' is a loaded term in HPC. This paper examines performance improvements in public cloud offerings and compares small runs in the cloud versus a six-year-old onsite HPC system. However, an MPI performance test up to 8 nodes, a mini-application performance tests up to 8 nodes, and a computational fluid dynamics domain science examination of 2 nodes does not adequately explore scaling.

**Reply**

* The language "at scale" indeed can evoke a "leadership computing" scenario (large DOE machines, etc.), and the reviewer is right to protest its use. We rephrased, because we're in the "long tail" setting here, of researchers running in parallel, but moderate size simulations. The runs are still production size for our application, with mesh sizes in the order of 50 million cells, allowing for three-dimensional fluid dynamics studies in the regimes of interest for our research problem.

**Changes**

* Remove sentence "same container ... run at scale" ([758e485](https://github.com/barbagroup/cloud-repro/commit/758e485de260cad01c72bdb38f93059593e4fe1b)).

---

### Comment 6

Section Three - Provides the results in the form of an MPI benchmark and a Poisson mini-application performance analysis, and analysis associated with a standard set of computational science experiments involving flow around a flying snake.

Notes:

* [x] Both the cloud and the six-year old HPC system use FDR Infiniband. Is Azure superior performance a result of tuning, configuration, or age? The analysis provided by this section is that Azure interconnect is improving. Cloud offerings moving from 10 Gbps Ethernet to FDR Infiniband in the past four years makes this result visible without testing. Did we need the OSU benchmarks for verification?
* [x] For the Poisson mini-application, the results again verify Azure has newer hardware than the authors onsite HPC system. However, what was the cause of the variance? Job/Node placement?
* [x] The detailed description of the flying snake workflow is appreciated.

**Reply**

* Is Azure superior performance a result of tuning, configuration, or age? —We didn't apply any manual tuning: both machines are running the same code, but of course the compiler versions are different, and the hardware is different. We are not emphasizing in this paper that performance is "superior" on Azure: just that it is a viable alternative to on-premises HPC clusters (because many researchers continue to be skeptical of cloud). We noticed that the reviewer twice mentions that we're using a "six-year old HPC system." Even if this is an old machine, it is what we have at our university and it is probably the situation for the majority of university researchers that they don't have much choice in regards to the local machines they run on. We certainly are not attempting to do an "apples to oranges" comparison of performance. The point is to dispel the misconception that cloud is (still) inadequate.
* Do we need the OSU benchmark results? We want to showcase that public cloud offerings have improved in the last few years. Our benchmark results show comparable networking performances between our university-managed HPC cluster and Microsoft Azure. We believe it is important to highlight these results as it is still common wisdom that public clouds are inadequate for computational research using HPC. Moreover, Freniere et al. (2016; Computing in Science & Engineering, 18(5), 68) used the same benchmark to compare their local cluster with AWS EC2 and reported performance degradation in networking. With these results, we are updating the readers of CiSE on the improvements of a public cloud such as Microsoft Azure.
* We do not know the cause the variance in runtime for the Poisson benchmark. However, the benchmark was executed 5 times within a single job task (and thus, on the same physical node), so the variation is not due to Job/Node placement. We have updated the caption of Fig. 3 (Poisson benchmark), detailing the number of MPI processes and the number of GPU devices used per node.

**Changes**

* Add information about the number of MPI processes and the number of GPU devices used per node for the Poisson benchmark ([98fccec](https://github.com/barbagroup/cloud-repro/commit/98fccec0a5a0ba7c6d9b4859a20aa81866417f92)).

---

### Comment 7

Section Four - Explores the cost analysis for a typical set of computational science experiments and insights on the user experience.

Notes:

* [x] For the user experience, how much did free computing and augmented support from Microsoft influence the authors' determination to utilize this environment. If it cost 20K, would the authors have completed the project?
* [x] Pricing changes every month, every week, maybe every day. Will any of this analysis be relevant by publication?
* [x] Table 5 will be outdated by the time this article is published. It does not add value.
* [x] How does this cost compare to buying a 2 - 8 node equivalent cluster? 
* [x] Singularity containers appear out of the blue in this section with no description.
* [x] The reference for Table 5 in the text is just (5). Is this a cite, a figure, or a listing.

**Reply**

* We would not have attempted this work, were it not for the sponsored cloud credits. We were indeed curious about reproducibility benefits of cloud computing, and that's why we wrote the proposal to Azure Research. But without the sponsorship, we would not have had research budget for this work. In our opinion, this is one of the reasons to publish this paper: other researchers curious about using cloud need this kind of information before they will jump in. With regards to support, we used the standard channels (support tickets and GitHub issues), and it was not "augmented" support.
* Price will of course change. We feel it needs to go down. The relevancy of publishing the "snapshot" of today's pricing is precisely as back up that prices should drop. However, the cost of the NC24r instance we used in this study has been 3.96 USD per compute hour for the last two years and it's unlikely that it will change by a lot in the next 6 months.
* Table 5 will be outdated, yes, but it is today's situation, under which we operated. It's also the case that the patterns will continue (i.e., the ratio between the different pricing options).
* Cost compared to buying a cluster? We don't really know. We tried to get some helpful data from our IT department, but were denied the information.
* We added a short description about the Singularity container technology at the end of paragraph 3 of the section "Cost Analysis and User Experience."
* We fixed the reference to Table 5 in the manuscript.

**Changes**

* Properly reference Table 5 of the manuscript ([db21f03](https://github.com/barbagroup/cloud-repro/commit/db21f036e8ae47bb4b6ab61d555a28637542ad1a)).
* Add description about Singularity container technology ([df1e0d5](https://github.com/barbagroup/cloud-repro/commit/df1e0d5f009038b2057a3de8a914662972d80769)).

---

## Reviewer 2

> Witherden, Freddie (2019): Review of Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics. figshare. Online resource. DOI: [https://doi.org/10.6084/m9.figshare.9159740.v1](https://doi.org/10.6084/m9.figshare.9159740.v1)

Portions of the review report quoted here by permissions granted on the original under a CC-BY license.

### Comment 1

* [x] Whilst the manuscript is well written the narrative is somewhat muddled. It starts with an overview of reproducible computational research, then pivots to how containers can be employed within the context of cloud computing, then jumping to benchmarks of one particular cloud providers' hardware, and then -- finally -- pivots a final time to a cost analysis of the public cloud for simulations. These are all interesting topics. Indeed, many a conference proceeding has been dedicated to each of these areas. However, by combining them into a single 10 page document this present manuscript fails to do justice to any of these areas. Further, the high degree of specificity will likely have a negative impact the relevance of the manuscript going forwards; a consequence of it being a review of the current state of affairs of a rapidly evolving field. It would therefore be better if it focused on just one or two areas such as "benchmarking cloud computing platforms" or "reproducibility through containers."

**Reply**

* The main goal of this manuscript is to report how to conduct CFD research in a reproducible way on a public cloud, laying out all the tools we used and the steps we undertook. We intend this paper to also serve as a mini-tutorial for researchers wanting to adopt these reproducible practices (we have observed when giving seminars or domain-conference talks that containers haven't disseminated to the CFD community). We use Docker containers to capture the computational environment and Microsoft Azure tools to capture the run-time environment. The degree of specificity is, in part, the point: precisely reproducing our work presumes deploying the same computational environment.
* Right now, researchers using scientific computing are still concerned about cost and performances on public clouds, and this is why we provide benchmark results and are report how much it costs to run our CFD application. Freniere et al. (2016) reported performance degradation on AWS (compared to their local cluster). But in the last three years, cloud providers have improved their offerings for HPC solutions. Thus, another objective is to update the record on the observations made by Freniere et al. (in the same journal) to the new cloud services introduced in the last two years.
* Although cloud computing is a rapidly evolving field, we believe it is important to report on the current state of public cloud offerings for academic applications. 
* The reviewer is a top expert in HPC, and we understand from this point of view it seems the paper does not do justice to the various topics covered. But the intended audience of this paper is not, in fact, either of our reviewers (their expertise was needed, of course, to provide a quality review of the manuscript!). The audience is intended to be researchers using scientific computing (possibly on old and over-subscribed university clusters), who are curious about using cloud resources, and interested in reproducible practices, but need guidelines to adopt these.
* Neither benchmarking cloud computing, nor reproducibility with containers, were a central focus for our paper. We include some benchmark results to update the record with respect to the article by Freniere et al., appearing in the same journal. We use container technology for our reproducible workflow (as others have), but extend the reproducibility ideas to automatic configuration of cloud resources.

**Changes**

* We made several changes, responding to both reviewers, which make the aims of the paper more clear. In particular, the Abstract and Introduction prepare the reader better for the rest of the paper.

---

### Comment 2

* [x] The manuscript only appears to be concerned with reproducibility in the 'now' and pays no consideration to 'link rot' and if one will be able to build and run the proposed containers in 5, 10, or even 20 years. (C.f. Old F77 codes which are expected to remain viable long after the heat death of the universe.) This is one of the most serious issues affecting reproducible research today. 
* [x] Further, the manuscript also glosses over several of the issues regarding deploying containerised applications within an HPC context. One of the most important is with regards to MPI libraries and the fact that many HPC/Cloud environments depend on specific MPI library. For example, Cray machines require Cray MPI, IBM POWER 9 machines require Spectrum MPI, and so on. This results in a 'leaky abstraction' for the container must now concern itself with the idiosyncrasies of the hardware which it is running on.

**Reply**

* Obsolescence of digital research objects, including software libraries and computational environments, is an acknowledged source of non-reproducibility, in the long run. The recent report of the National Academies highlights it so [page?]. Indeed, tools in our workflow that we have no control over (Azure CLI, Batch Shipyard) will likely change, and perhaps not be backwards compatible. That is inevitable. But when they do, our fully documented workflow (via human-readable configuration files) will continue to offer transparency of what we did and how we did it. 
* "issues regarding deploying containerised applications within an HPC context" — Broad portability of our software and workflow is not our objective, and would (arguably) not be justified. Our software is currently only used in research projects within our lab: what reasons would call for the highly skilled and labor intensive software engineering required to deliver broadly portable software and workflow?The goal is, rather, to publish our computational research with deep transparency. The Docker images built for this study were specifically crafted to run on Microsoft Azure with Azure Batch service on RDMA-capable nodes with Linux-based virtual machines. Readers interested in reproducing our analysis should do it under the same conditions, which include the same cloud environment. We have added text in the introduction explaining the limitations of this work with respect to portability issues.

**Changes**

* Added language about limitations regarding portability issues ([97e0512](https://github.com/barbagroup/cloud-repro/commit/97e05126928bea4285c586bfd1f8edc50c0f10ad)).
* Re-arrange last paragraph of the conclusion to emphasize the limitation of the reproducibility, and add citation to the new NASEM report ([6f029e9](https://github.com/barbagroup/cloud-repro/commit/6f029e99103e38b1e4487b08f580a9c1904ba419)).

---

### Comment 3

As highlighted by the authors' in both the manuscript and the Dockerfiles it is necessary (on the Azure platform at least) to use the Intel MPI library. This is highly problematic.

* [x] (a) It explicitly ties the container to x86 based clusters which support the Intel MPI library (even when the underlying solver software and libraries are portable).
* [x] (b) The library itself has to be downloaded off a random URL on the Intel website (whose long term stability and availability is suspect).
* [x] (c) Downloading the library requires acceptance of a proprietary EULA whose terms could easily put an unsuspecting researcher who does not also possess a JD into serious legal trouble with the Intel Corporation -- especially when it comes to moving the container between systems which may be employed for commercial gain. (Aside: whilst in all of the Dockerfiles an rm -rf is performed at the end to remove the Intel components, due to the layered nature of Docker images the compilers are *100%* still present in the resulting images and thus may result in even more legal issues for an unsuspecting researcher.)
* [x] (d) It is also sub-optimal in the context of CUDA applications for the Intel MPI library is not (to the reviewers' knowledge) CUDA aware and thus parallel CUDA applications are likely to run substantially slower than on say OpenMPI or MVAPICH2 w/GDR.

The result is a highly fragile system which is coupled to the wonts of one particular cloud platform.

Similarly, with the CUDA containers there are also compatibility issues.  The most obvious is the container specifying a specific GPU architecture version which may not map onto the hardware of the host.  This is another 'leaky abstraction' issue.

**Reply**

* (a) As indicated in our reply to Comment 2, portability to other hardware is not our goal. We do, in fact, tie the reproducibility of our results to using the exact same computational environment.
* (b) We downloaded the MPI library from the Intel website just to build the Docker images locally. These images are now published on DockerHub and publicly available. Readers interested in reproducing our analysis under the same conditions (on Azure) do not need to dowload the Intel MPI library.
* (c) The Intel MPI library is under [Intel Simplified Software License](https://software.intel.com/en-us/license/intel-simplified-software-license), which allows for redistribution as long as the copyright note remains. On downloading the library, the LICENSE file is included with the source. There is no mention of commercial uses in the license, so they are not disallowed. Note that we are not using Intel compilers, just the MPI library. For greater transparency, we added a note in the README under the `docker` sub-folder saying the user who downloads the Docker image agrees to the Intel license terms. The same note was also added to the description of the Docker images on DockerHub.
* (d) We _need_ to use Intel MPI library, because the Azure nodes we are using require it. Our software is, indeed, using GPU computing with CUDA. Other MPI libraries may be more performant with CUDA,  but they are not available in the RDMA-capable Azure nodes used. Note that performance is not our highest priority, reproducibility is.

**Changes**

* Add note about Intel Simplified Software License ([d3c8543](https://github.com/barbagroup/cloud-repro/commit/d3c8543be25ff6b2d55947b6a3a118618878d7e3)).

---

### Comment 4

* [x] Table 1 contains performance data for the Azure cloud nodes and the Colonial One nodes. However, it makes no mention of the memory configuration of the nodes (# of channels and speed rating of the DDR memory). Different configurations here can result in substantial differences with regards to peak memory bandwidth. This is vital as all of the benchmarks fall into the category of 'memory bandwidth bound problems'. Along these lines it is also important to note if ECC was enabled or disabled for the NVIDIA GPUs as this can have a substantial impact on performance.

**Reply**

* We agree with the comments made by the reviewer. The memory configuration on Colonial One is 128GB of 1600MHz DDR3 ECC Register DRAM for `ivygpu` nodes and 128GB of 1866MHz DDR3 ECC Registered DRAM for `short` nodes. However, we do not have such information for Azure. We contacted Microsoft Azure about that and they told us there is no publicly released information regarding the speed and channels. Right now, only CPU information are publicly available (already included in Table 1 of the manuscript).
* All runs using GPU computing that are reported in the manuscript were done with ECC enabled for NVIDIA GPUs (on Azure and on Colonial One). As suggested by the reviewer, we added that information to the manuscript (in the caption of Table 1).

**Changes**

* Mention ECC was enabled for GPU computing in caption of Table 1 ([5ad8d81](https://github.com/barbagroup/cloud-repro/commit/5ad8d8100d59b60568cf067be82f6a63546179ea)).

---

### Comment 5

* [x] With regards to the benchmarks in Fig 2. could the authors explain why the lower latency for the Colonial One cluster at small message sizes does not translate into greater peak bandwidth at these sizes?

**Reply**

* We cannot explain that, because we don't know. We did, however, rerun the benchmarks on Colonial One, this time using Intel MPI (previous results used OpenMPI), and the results do get closer to those on Azure. In any case, the age of the system, the details of the hardware, or system software—we don't worry about the details, because the purpose of this figure is to update the reader on similar reports presented 3 years ago by Freniere et al.

**Changes**

* Update Figures 2 and 3 after re-running the benchmarks (MPI and Poisson) on Colonial One with the Intel MPI library; OpenMPI was used in the previous version of the manuscript ([38dd7d0](https://github.com/barbagroup/cloud-repro/commit/38dd7d074dc7bfa109d1c74b59f991d914fe204a)).

---

### Comment 6

* [x] Fig 3 is somewhat cluttered and amounts to three plots in one. The first appears to be strong scaling on CPUs whilst the second two correspond to weak scaling on GPUs (although it is not elucidated as such). This breakdown seems somewhat arbitrary.

**Reply**

* We added parenthetical remarks to the text and restructured the caption, emphasizing the type of scaling shown in each plot (strong, weak). We still like the three panels in one figure, rather than breaking it into three figures: they all deal with the Poisson benchmark on the local cluster and the cloud. It seems like a matter of preference on how to present the data, but it is clear what each plot is presenting.

**Changes**

* Mention "strong scaling" for CPUs and "weak scaling" for GPUs to the text ([38dd7d0](https://github.com/barbagroup/cloud-repro/commit/38dd7d074dc7bfa109d1c74b59f991d914fe204a)).
* Restructure the caption text ([a53ae04](https://github.com/barbagroup/cloud-repro/commit/a53ae040e58be7e3a1d6e2289ba84b97ae889133)).

---

### Comment 7

* [x] On line 45 of page 6 a remark is made around "One of the requirements for reproducible computational results is to make code available under a public license (allowing reuse and modification by others)." However this does not appear to follow; a piece of work whose code and data is made available for "reproducibility purposes only" would still appear to meet the requirements for facilitating reproducible computational results laid out in the introduction even though the license does not permit reuse or modification.

**Reply**

* Strictly speaking, the reviewer is correct. One _could_ make code available under a restrictive license that allows others to _only_ use it without modification to reproduce the results. That is certainly possible, but not good form, in our opinion. We added the word "ideally" in the parenthetical note, to be strictly accurate.

**Changes**

* Add word "ideally" in the parenthetical note ([56028ea](https://github.com/barbagroup/cloud-repro/commit/56028ead2f917bd5f30f0d781f8d5b253cfb7b07)).

---

### Comment 8

* [x] With regards to the CFD results there does not appear to be any kind of mesh/convergence study nor are any attempts made to quantify the uncertainties on the resulting C_L and C_D coefficients. As such it is difficult to know what to make of the results beyond "they look nice." Although the reviewer appreciates the focus of this paper is not the CFD results per-se it is nevertheless important when presenting numerical results to make a case that the method is resolving all relevant dynamics and that any time-averaged statistics are indeed converged.

**Reply**

* We do have results of a simulation with a mesh of doubled density in the near-body region, with the same stretching ratio moving away from it. It results in more than 230 million cells. The relative difference in time-averaged force coefficients was 6.5% for drag and 3% for lift. But the cost is about 7.4 times compared with the coarser-grid run shown in the paper. The purpose of this paper is not targeting the physics, but the reviewer is right to ask about the fidelity of the simulation shown, and other readers may have the same question. Therefore, we have added a passage at the end of section 3.3.2 with this very explanation, and added to the GitHub repository for this paper a Jupyter notebook with a comparison of the time-varying force coefficients between the coarser and finer meshes. The paper points to this notebook as supplementary material.

**Changes**

* Add a Jupyter Notebook with comparison of the force coefficients between the coarse and fine grids ([c1ed36e](https://github.com/barbagroup/cloud-repro/commit/c1ed36e143c226b3381898318d2ec0ab70e2994e)).
* Add sentences about the run on the finer grid ([201ef06](https://github.com/barbagroup/cloud-repro/commit/201ef066bd04a76cb715028f805d21da2f86e29b)).

---

### Comment 9

* [x] Although the cost analysis is interesting without any real basis of comparison it is difficult to glean much from it.

**Reply**

* We used the the cloud platform Microsoft Azure because we received a sponsorship from the program "Microsoft Azure for Research." We have not tried other cloud providers. We do not report any cost analysis for local HPC cluster as the University is not willing to disclose information related to the cost of operating the cluster.

**Changes**

* No changes needed.

### 2019-08-16 tex/MesnardoBarba2019.tex
Use LaTeX quotes and fix small typos

@@
 We also adopt several tools that facilitate creating and managing virtual machines on compute nodes and submitting jobs to these nodes.
-The configuration files for these tools are part of an expanded "reproducibility package" that includes workflow definitions for cloud computing, in addition to input files and instructions.
+The configuration files for these tools are part of an expanded ``reproducibility package'' that includes workflow definitions for cloud computing, in addition to input files and instructions.
 This facilitates re-creating the cloud environment to re-run the computations under the same conditions.
@@
 We go one step further by moving the computational work to Azure cloud resources using tools that programmatically capture the virtual environment configuration.
-The configuration files become part of expanded "reproducibility packages" for the study.
+The configuration files become part of expanded ``reproducibility packages'' for the study.
 This work does not target portability of our software and workflow to diverse high-performance computing (HPC) environments. 
@@
 This promises to greatly facilitate code development, debugging, and testing. Resources allocated on the cloud are released as soon as the job is done, avoiding paying for idle time.
-On a public-cloud platform---such as Microsoft Azure, Google Cloud, Amazon AWS---with a "pay-as-you-go" type of subscription, a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters.
+On a public-cloud platform---such as Microsoft Azure, Google Cloud, Amazon AWS---with a ``pay-as-you-go'' type of subscription, a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters.
 Cost models that make sense for researchers, labs, and universities are still unclear. 
@@
 Our research lab is interested in understanding the aerodynamics of flying animals via CFD simulations.
-One of our applications deals with the aerodynamics of a snake species, \textit{Chrysopelea Paradisi}, that lives in South-East Asia.
+One of our applications deals with the aerodynamics of a snake species, \textit{Chrysopelea paradisi}, that lives in South-East Asia.
 This arboreal reptile has the remarkable capacity to turn its entire body into a wing and glide over several meters\cite{socha_2011}.
@@
 
-We submitted a job on Azure Batch (with Batch Shipyard,) to compute the two-dimensional flow around an anatomically accurate sectional shape of the gliding snake.
+We submitted a job on Azure Batch (with Batch Shipyard) to compute the two-dimensional flow around an anatomically accurate sectional shape of the gliding snake.
 The cross-section has a chord-length $c=1$ and forms a $35$-degree angle of attack with the incoming freestream flow.
@@
 A finer grid would be preferable to capture the flow dynamics in detail, but the purpose of this paper is not targeting the physics.
-We did however run a simulation on a finer grid (about $233$ million cells) resulting in a relative difference (with respect to the "coarse"-grid simulation) of $+6.5\%$ and $+3\%$ for the time-averaged drag and lift coefficients, respectively.
+We did however run a simulation on a finer grid (about $233$ million cells) resulting in a relative difference (with respect to the ``coarse''-grid simulation) of $+6.5\%$ and $+3\%$ for the time-averaged drag and lift coefficients, respectively.
 We decided to continue this work with the coarser grid due to the large cost difference (see Section \ref{sec:cost}).
@@
 The three-dimensional simulation on the finer grid ($233$ million cells) ran on $6$ \texttt{NC24r} instances and cost about $7965$ USD to compute $100,000$ time steps (cost not included in \ref{tab:azure_charges}).
-This is more than $7$ times the cost we paid for the "coarse"-grid run!
+This is more than $7$ times the cost we paid for the ``coarse''-grid run!
 It would have been too expensive to run a batch of simulations on the finer grid for our exploratory analysis of the flow around the snake cylinder.

### 2019-08-16 tex/MesnardoBarba2019.tex
Add minor edits
List of modifications (ordered as they appear in the manuscript):

* Avoid repetition on "instruction" -> use "prefixed with the keyword".
* Use parenthesis for "program shipyard" for parallelism with "program az".
* Remove repetition of "network".
* Say explicitly what is an "immerse body".
* Remove unnecessary repetition of the Reynolds number value.
* Remove enumeration (as we are only enumerating two items).
* Remove negation and use "perhaps breaking backward compatibility".

@@
 For example, we start building a new image from a base image using the keyword \texttt{FROM}.
-We then write the different shell instructions (with the \texttt{RUN} instruction) to build a multi-layered runtime environment of the application that includes all its dependencies.
+We then write the different shell instructions (prefixed with the keyword \texttt{RUN}) to build a multi-layered runtime environment of the application that includes all its dependencies.
 Once we have built and tested the image on the local machine, we push it to a repository on the DockerHub registry: a place to store and retrieve Docker images.
@@
 
-Once the configuration files are written, we invoke Batch Shipyard through the \texttt{shipyard} program on our local machine.
+Once the configuration files are written, we invoke Batch Shipyard (program \texttt{shipyard}) on our local machine.
 The folder \texttt{examples/snake2d2k35/config\_shipyard} in the repository accompanying this paper contains an example YAML files to create a pool of two \texttt{NC24r} compute nodes (featuring K80 GPUs and using InfiniBand network).
@@
 The bandwidth test measures the maximum sustained rate that can be achieved on the network; the sender sends a fixed number of messages to a receiver that replies only after receiving all of them.
-The tests ran on \texttt{NC24r} nodes on Azure and \texttt{Ivygpu} nodes on Colonial One, all of them featuring a network interface for RDMA (Remote Direct Memory Access) connectivity to communicate over an InfiniBand network.
+The tests ran on \texttt{NC24r} nodes on Azure and \texttt{Ivygpu} nodes on Colonial One, all of them featuring a network interface for RDMA (Remote Direct Memory Access) connectivity to communicate over InfiniBand.
 (RDMA allows direct access to a remote's memory without involving the operating system of the host and remote.)
@@
 To study the flow around the flying snake, we developed a CFD software called PetIBM\cite{chuang_et_al_2018}, an open-source toolbox that solves the two- and three-dimensional incompressible Navier-Stokes equations using a projection method (seen as an approximate block-LU decomposition of the fully discretized equations\cite{perot_1993}) and an immersed-boundary method (IBM).
-Within this framework, the fluid equations are solved over an extended grid that does not conform to the surface of the immersed body.
+Within this framework, the fluid equations are solved over an extended grid that does not conform to the surface of the body immersed in the computational domain.
 To model the presence of the body, the momentum equation is augmented with a forcing term that is activated in the vicinity of the immersed boundary.
@@
 Two-dimensional computational simulations of fundamentally three-dimensional flows lead to incorrect estimation of the force coefficients, as is well known\cite{mittal_balachandar_1995}.
-The grid used for the three-dimensional simulation contains about $46$ million cells and is somewhat coarse for direct numerical simulation at Reynolds number $2,000$, but acceptable for our exploratory analysis.
+The grid used for the three-dimensional simulation contains about $46$ million cells and is somewhat coarse for direct numerical simulation at this Reynolds number, but acceptable for our exploratory analysis.
 A finer grid would be preferable to capture the flow dynamics in detail, but the purpose of this paper is not targeting the physics.
@@
 Fig. \ref{fig:wz_avg_3d} shows the instantaneous spanwise vorticity averaged along the $z$-direction after $80$ and $100$ time units.
-Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von K\'{a}rm\'{a}n street exhibits a narrower wake than in the two-dimensional simulations.
+Compared to the snapshots from the two-dimensional simulation, we observe that free-shear layers roll up into vortices further away from the snake body and that the von K\'{a}rm\'{a}n street exhibits a narrower wake than in the two-dimensional simulations.
 We also note the presence of an unsteady recirculation region just behind the snake cylinder, and alternating regions of positive and negative cross-flow velocity showing the presence of von Karman vortices (Fig.
@@
 The recent report of the National Academies highlights this \cite[p.~57]{nasem_2019}. 
-Indeed, tools in our workflow that we have no control over (Azure CLI, Batch Shipyard) will likely change, and perhaps not be backwards compatible. 
+Indeed, tools in our workflow that we have no control over (Azure CLI, Batch Shipyard) will likely change, perhaps breaking backward compatibility. 
 That is inevitable. 

### 2019-08-16 examples/snake3d2k35/scripts/plot_force_coefficients_compare_2d.py
Update legend of Matplotlib figure for forces
The info "(3D)" was missing in the legend.

@@ -45,14 +45,13 @@ pyplot.rc('font', family='serif', size=16)
 fig, ax = pyplot.subplots(figsize=(8.0, 4.0))
 ax.set_xlabel('Non-dimensional time')
 ax.set_ylabel('Force coefficients')
-ax.grid()
-ax.plot(t, cd, label='$C_D$')
-ax.plot(t, cl, label='$C_L$')
+ax.plot(t, cd, label='$C_D$ (3D)')
+ax.plot(t, cl, label='$C_L$ (3D)')
 ax.plot(t2, cd2, label='$C_D$ (2D)', 
         color='black', linewidth=0.75, linestyle='--')
 ax.plot(t2, cl2, label='$C_L$ (2D)',
         color='black', linewidth=0.75, linestyle='-')
-ax.legend(ncol=4)
+ax.legend(ncol=2, frameon=False, prop={'size': 14})
 ax.set_xlim(0.0, 80.0)
 ax.set_ylim(0.55, 3.5)
 fig.tight_layout()

### 2019-08-21 response_to_reviewers.md
light edit response reviewer 1

@@
 DOI: [https://doi.org/10.22541/au.156415458.85375575](https://doi.org/10.22541/au.156415458.85375575)
-
-Portions of the review report quoted here by permissions granted on the original under a CC-BY license.
+> (CC-BY)
 
@@
 The RDMA network on Azure supports MPI traffic for applications running with Intel MPI 5.x (or a later version).
-(In other words, to take advantage of RDMA on Linux compute nodes, we must use Intel MPI on the nodes.) We added a sentence  over the end of paragraph 4 of the section "Cost Analysis and User Experience" mentioning the Docker images was specifically crafted to be used with Azure Batch service.
+(In other words, to take advantage of RDMA on Linux compute nodes, we must use Intel MPI on the nodes.) We added a sentence  over the end of paragraph 4 of the section "Cost Analysis and User Experience" mentioning the Docker image was specifically crafted to be used with Azure Batch service.
 Thus, we also removed the sentence "same container ...
@@
 With these results, we are updating the readers of CiSE on the improvements of a public cloud such as Microsoft Azure.
-* We do not know the cause the variance in runtime for the Poisson benchmark.
+* We do not know the cause of the variance in runtime for the Poisson benchmark.
 However, the benchmark was executed 5 times within a single job task (and thus, on the same physical node), so the variation is not due to Job/Node placement.
@@
 With regards to support, we used the standard channels (support tickets and GitHub issues), and it was not "augmented" support.
+We edited the acknowledgement section, which vaguely used the verb "help," to avoid the impression that we received extra support.
 * Price will of course change.
@@
 * Add description about Singularity container technology ([df1e0d5](https://github.com/barbagroup/cloud-repro/commit/df1e0d5f009038b2057a3de8a914662972d80769)).
+* * Edit acknowledgements ([9772f42](https://github.com/barbagroup/cloud-repro/commit/9772f42a64d01b4aed7ee497a2f41ff88615cf73)).
 
@@
 DOI: [https://doi.org/10.6084/m9.figshare.9159740.v1](https://doi.org/10.6084/m9.figshare.9159740.v1)
-
-Portions of the review report quoted here by permissions granted on the original under a CC-BY license.
+> (CC-BY)
 

### 2019-08-21 response_to_reviewers.md
light edit response reviewer 2

@@
 The degree of specificity is, in part, the point: precisely reproducing our work presumes deploying the same computational environment.
-* Right now, researchers using scientific computing are still concerned about cost and performances on public clouds, and this is why we provide benchmark results and are report how much it costs to run our CFD application.
+* Right now, researchers using scientific computing are still concerned about cost and performance on public clouds, and this is why we provide benchmark results and report how much it costs to run our CFD application.
 Freniere et al.
@@
 * Obsolescence of digital research objects, including software libraries and computational environments, is an acknowledged source of non-reproducibility, in the long run.
-The recent report of the National Academies highlights it so [page?].
+The recent report of the National Academies highlights it so (page 57).
 Indeed, tools in our workflow that we have no control over (Azure CLI, Batch Shipyard) will likely change, and perhaps not be backwards compatible.
@@
 
-* [x] (a) It explicitly ties the container to x86 based clusters which support the Intel MPI library (even when the underlying solver software and libraries are portable).
-* [x] (b) The library itself has to be downloaded off a random URL on the Intel website (whose long term stability and availability is suspect).
-* [x] (c) Downloading the library requires acceptance of a proprietary EULA whose terms could easily put an unsuspecting researcher who does not also possess a JD into serious legal trouble with the Intel Corporation -- especially when it comes to moving the container between systems which may be employed for commercial gain.
+* [x] \(a) It explicitly ties the container to x86 based clusters which support the Intel MPI library (even when the underlying solver software and libraries are portable).
+* [x] \(b) The library itself has to be downloaded off a random URL on the Intel website (whose long term stability and availability is suspect).
+* [x] \(c) Downloading the library requires acceptance of a proprietary EULA whose terms could easily put an unsuspecting researcher who does not also possess a JD into serious legal trouble with the Intel Corporation -- especially when it comes to moving the container between systems which may be employed for commercial gain.
 (Aside: whilst in all of the Dockerfiles an rm -rf is performed at the end to remove the Intel components, due to the layered nature of Docker images the compilers are *100%* still present in the resulting images and thus may result in even more legal issues for an unsuspecting researcher.)
-* [x] (d) It is also sub-optimal in the context of CUDA applications for the Intel MPI library is not (to the reviewers' knowledge) CUDA aware and thus parallel CUDA applications are likely to run substantially slower than on say OpenMPI or MVAPICH2 w/GDR.
+* [x] \(d) It is also sub-optimal in the context of CUDA applications for the Intel MPI library is not (to the reviewers' knowledge) CUDA aware and thus parallel CUDA applications are likely to run substantially slower than on say OpenMPI or MVAPICH2 w/GDR.
 
@@
 
-* [x] With regards to the CFD results there does not appear to be any kind of mesh/convergence study nor are any attempts made to quantify the uncertainties on the resulting C_L and C_D coefficients.
+* [x] With regards to the CFD results there does not appear to be any kind of mesh/convergence study nor are any attempts made to quantify the uncertainties on the resulting C\_L and C\_D coefficients.
 As such it is difficult to know what to make of the results beyond "they look nice." Although the reviewer appreciates the focus of this paper is not the CFD results per-se it is nevertheless important when presenting numerical results to make a case that the method is resolving all relevant dynamics and that any time-averaged statistics are indeed converged.

### 2019-08-22 tex/MesnardoBarba2019.tex
Update legend of Matplotlib figure for forces
The info "(3D)" was missing in the legend.
refine acknowledgements
Fix typo

@@
 \ref{fig:poisson_benchmarks} (top) reports the mean runtimes (averaged over $5$ repetitions) to iteratively solve the system, on a uniform grid of $50$ million cells ($1000 \times 1000 \times 50$), as we increase the number of nodes in the pool (strong scaling).
-Runtimes between obtained on Colonial One and Azure are similar.
+Runtimes obtained on Colonial One and Azure are similar.
 We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
@@
     \centering
-    \includegraphics[width=8cm]{figures/forceCoefficientsCompare2D.pdf}
+    \includegraphics[width=8.5cm]{figures/forceCoefficientsCompare2D.pdf}
     \caption{History of the force coefficients obtained with two- and three-dimensional simulations at Reynolds number $2000$ for a snake cross-section with a $35$-degree angle of attack.
@@
 CCF-1747669.
-We would like to thank Kenji Takeda, Fred Park, and Joshua Poulson of Microsoft for their help.
+We would like to thank Kenji Takeda, Fred Park, and Joshua Poulson of Microsoft for constructive interactions and listening to our feedback about their products. 
 We are also immensely grateful to the reviewers, Patrick O'Leary \cite{oleary_2019} and Freddie Witherden \cite{witherden_2019}, for their contributions, which helped make the paper's audience and purpose more clear, in addition to other improvements.

### 2019-08-22 tex/MesnardoBarba2019.tex
fix typo

@@
 We also show that cloud offerings are now adequate to complete computational fluid dynamics studies with in-house research software that uses parallel computing with GPUs.
-Finally, we share with the community what we have learned from nearly two years of using Azure cloud to enhance transparancy and reproducibility in our computational simulations.
+Finally, we share with the community what we have learned from nearly two years of using Azure cloud to enhance transparency and reproducibility in our computational simulations.
 \end{abstract}

### 2019-09-10 tex/MesnardoBarba2019.tex
minor edit

@@
 This facilitates re-creating the cloud environment to re-run the computations under the same conditions.
-Although cloud providers have improved their offerings, many researchers using high-performance computing (HPC) are still skeptical about using cloud computing.
+Although cloud providers have improved their offerings, many researchers using high-performance computing (HPC) are still skeptical about cloud computing.
 Thus, we ran benchmarks for tightly coupled applications to confirm that the latest HPC nodes of Microsoft Azure are indeed a viable alternative to traditional on-site HPC clusters.
@@
 It is thus worth clarifying how we use these terms.
-``Reproducible research'' was used by geophysics professor Jon Claerbout in the 1990s to mean computational studies that can be reproduced by other scientists.
+``Reproducible research'' was used by geophysics professor Jon Claerbout in the 1990s to mean computational studies that are published with sufficient transparency so other scientists can re-create the results.
 His research group at Stanford created a reproducible-research environment\cite{schwab_et_al_2000} whose goal was complete documentation of scientific computations, in such a way that a reader could reproduce all the results and figures in a paper using the author-provided computer programs and raw data.

### 2019-09-10 tex/MesnardoBarba2019.tex
add note about portability

@@
 As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.
+Both the Docker image and the configurations files for deploying the cloud resources give an interested reader the opportunity to reproduce our computations in an identical environment.
+Even if this opportunity is not accompanied by portability---e.g., one may depend on a different MPI library to use a different system---the human-readable Docker files and configuration files do offer transparency.
 

### 2019-09-11 tex/MesnardoBarba2019.tex
fix typos in caption

@@
 We push to DockerHub a Docker image of our CFD application with all its dependencies.
-Azure CLI is use to configure accounts on Microsoft Azure and to upload/download data to/from an Azure Storage account.
-With Batch Shipyard, we create a pool on Azure Batch and run container-based simulation using our Docker image.
-Figure available under CC BY 4.0 license (DOI: https://doi.org/10.6084/m9.figshare.9636722.v1).}
+Azure CLI is used to configure accounts on Microsoft Azure and to upload/download data to/from an Azure Storage account.
+With Batch Shipyard, we create a pool on Azure Batch and run container-based simulations using our Docker image.
+Figure available under CC BY 4.0 license (https://doi.org/10.6084/m9.figshare.9636722.v1).}
     \label{fig:cloud_workflow}

### 2019-09-11 tex/MesnardoBarba2019.tex
remove hard-coded path to figures

@@
 \usepackage[pdftex]{graphicx}
-\graphicspath{{./figs}}
+\graphicspath{{figures/}}
 \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
@@
     \centering
-    \includegraphics[width=16cm]{figures/cloud_workflow.png}
+    \includegraphics[width=16cm]{cloud_workflow.png}
     \caption{Reproducible workflow on the public cloud provider Microsoft Azure.
@@
     \centering
-    \includegraphics[width=8cm]{figures/osu_latency_bandwidth.pdf}
+    \includegraphics[width=8cm]{osu_latency_bandwidth.pdf}
     \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One (\texttt{Ivygpu} nodes) and on Microsoft Azure (\texttt{NC24r} nodes) with the Intel MPI library.
@@
     \centering
-    \includegraphics[width=8cm]{figures/poisson_time_vs_nodes.pdf}
+    \includegraphics[width=8cm]{poisson_time_vs_nodes.pdf}
     \caption{Runtime to solve a Poisson system on Colonial One and Microsoft Azure.
@@
     \centering
-    \includegraphics[width=8cm]{figures/wz_multi_contourf.png}
+    \includegraphics[width=8cm]{wz_multi_contourf.png}
     \caption{Filled contour of the vorticity field ($-5 \leq w_z c / U_\infty \leq 5$) after $20$, $44$, $45$, and $80$ time units of flow simulation with PetIBM for the snake cross-section at a $35$-degree angle of attack and Reynolds number $2000$.
@@
     \centering
-    \includegraphics[width=8.5cm]{figures/forceCoefficientsCompare2D.pdf}
+    \includegraphics[width=8.5cm]{forceCoefficientsCompare2D.pdf}
     \caption{History of the force coefficients obtained with two- and three-dimensional simulations at Reynolds number $2000$ for a snake cross-section with a $35$-degree angle of attack.
@@
     \centering
-    \includegraphics[width=8cm]{figures/wz_avg_multi_contourf.png}
+    \includegraphics[width=8cm]{wz_avg_multi_contourf.png}
     \caption{Filled contour of the spanwise-averaged z-component of the vorticity ($-5 \leq w_z c / U_\infty \leq 5$) field after $80$ and $100$ time units of a three-dimensional flow simulation with PetIBM for the snake cylinder with a cross-section at a $35$-degree angle of attack and Reynolds number $2000$.}
@@
     \centering
-    \includegraphics[width=8cm]{figures/ux_uy_xz_plane.png}
+    \includegraphics[width=8cm]{ux_uy_xz_plane.png}
     \caption{Filled contour of the streamwise velocity (top) and cross-flow velocity (bottom) behind the snake cylinder in the $x/z$ plane at $y/c=-0.2$ in the wake of the snake cylinder with a $35$-degree angle of attack at Reynolds number $2000$ after $100$ time-units of flow simulations.
@@
     \centering
-    \includegraphics[width=18cm]{figures/qcrit_wx_wake3d_0020.png}
+    \includegraphics[width=18cm]{qcrit_wx_wake3d_0020.png}
     \caption{Lateral view of the isosurfaces of the Q-criterion ($Q = 1$) in the wake of the snake cylinder (with a $35$-degree angle of attack) at Reynolds number $2000$.

### 2019-09-11 tex/MesnardoBarba2019.tex
add author bios

@@
 
+\bigskip
+
+\textbf{Olivier Mesnard} is a doctoral student at the George Washington University.
+His research interests include computational fluid dynamics and immersed boundary methods with application to animal locomotion.
+Mesnard has an Engineering degree from Institut Sup{\'e}rieur de M{\'e}canique de Paris and an MS from Universit{\'e} Pierre et Marie Curie.
+Contact him at mesnardo@gwu.edu.
+
+\textbf{Lorena A.
+Barba} is a professor of mechanical and aerospace engineering at the George Washington University.
+Her research interests include computational fluid dynamics, biophysics, and high-performance computing.
+She is co-Editor of the CiSE Reproducible Research Track, Associate Editor for The ReScience Journal, Associate Editor-in-Chief of the Journal of Open Source Software, and Editor-in-Chief of the Journal of Open Source Education.
+Barba received a PhD in aeronautics from the California Institute of Technology.
+Contact her at labarba@gwu.edu.
+
 \bibliographystyle{IEEEtran}
